### 2021-10-05 main.tex
Initial Overleaf Import

\documentclass[a4paper]{article} 	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}  		% See geometry.pdf to learn the layout options. There are lots.
\geometry{left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm}   		
\usepackage{graphicx,subcaption}					
\usepackage{amssymb}
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{booktabs,multirow}
\usepackage{authblk}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{float}
\usepackage[flushleft]{threeparttable} % For adding footnotes to tables

\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newcommand{\E}{\mathrm{E}}
\newcommand{\D}{\mathcal{MD}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Corr}{\mathrm{Corr}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\R}{\texttt{R}}
\newcommand{\asreml}{\texttt{ASReml-R}}
\newcommand{\Matern}{Mat\'ern }
\newcommand{\N}{\mathcal{N}}
\newcommand{\AR}{\mathrm{AR1}}

%\newcommand{\brms}{\texttt{brms}}
%\newcommand{\rstan}{\texttt{rstan}}
%\newcommand{\elpd}{elpd\textsubscript{loo}}
%\newcommand{\psis}{elpd\textsubscript{psis-loo}}
%\newcommand{\ploo}{p\textsubscript{loo}}

\newcommand{\BigO}[1]{{\rm O}\left(#1\right)}
\newcommand{\eg}{e.g.\ }
\newcommand{\ie}{i.e.\ }
\newcommand{\iid}{\textrm{i.i.d.\ }}

\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100]{biblatex}
\addbibresource{BayesOFE.bib}

\title{Optimal design for on-farm strip trials --- systematic or randomised?}
%\author{Jerome}
\author[1]{Zhanglong Cao}
\author[1]{Andrew Grose}
\author[1]{Jordan Brown}
\author[1,2]{Suman Rakshit}

\affil[1]{SAGI West, School of Molecular and Life Sciences, Curtin University, Perth, Australia}
\affil[2]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}

\date{}							
% Activate to display a given date or no date

\linenumbers
%\doublespacing
\onehalfspacing

\begin{document}

\maketitle

\begin{abstract}
There is no doubt on the importance of randomisation in agricultural experiments by agronomists and biometricians. Even when agronomists extend the experimentation from small trials to large on-farm trials, randomised designs predominate over systematic designs. However, the situation may change depending on the objective of the on-farm experiments (OFE). If the goal of OFE is obtaining a smooth map showing the optimal level of a controllable input across a grid made by rows and columns covering the whole field, a systematic design should be preferred over a randomised design in terms of robustness and reliability. With the novel geographically weighted regression (GWR) for OFE and simulation studies, we conclude that, for large OFE strip trials, the difference between randomised designs and systematic designs are not significant if a linear model of treatments is fitted or if spatial variation is not taken into account. But for a quadratic model, systematic designs are superior to randomised designs. 
\end{abstract}

{\bf Keywords:} yield map, optimal treatment, spatially varying coefficients.

\section{Introduction}\label{Sec:Intro}

The principles of randomisation were first expounded in 1925, when \textcite{Fisher1934Statistical} analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in the rows and columns of a Latin square \parencite{Verdooren2020History}. The most straightforward, least restrictive experimental design is the completely randomised design (CRD). More complex designs are widely used in agricultural experiments \parencite{Petersen1994Agricultural}, which include randomised complete block, split-plot, strip-plot, and latin square designs.

% Old concluding sentence: With the increase in complexity, randomised block design, split-plot design, strip-plot design and Latin square design are all widely used in agricultural experiments \parencite{Petersen1994Agricultural}.

Following these principles, randomised designs are routinely used, from small on-site trials to large on-farm experiments (OFE), in contrast to systematic designs which are rarely used. OFE enables farmers the flexibility to implement large-scale experiments in order to test management practices on their farms \parencite{Evans2020Assessment}. The aim of OFE is to enable farmers to improve their competence of uncertainties and to take into account their existing strengths of handling translational and structural uncertainty \parencite{Cook2013Onfarm}. In the situation that the goal is to compare yield responses between management classes or to select individuals with the best performance as new market varieties, a randomised design is superior to a systematic design \parencite{Pringle2004FieldScale, Selle2019Flexible}.

%Like conventional agricultural experiments,

Randomisation has been considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, however this is not true when the goal of OFE shifts from what is desired from a conventional analysis. In the application of precision agriculture (PA), a prescription map from the experimental results is required by the variable-rate applicators (VRA) prior to the start of the operation \parencite{Pringle2004FieldScale}. Therefore, in this scenario, the goal of OFE becomes obtaining such a smooth map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made by rows and columns covering the whole field. For this objective, \textcite{Pringle2004FieldScale} stress that only a single level of the treatments can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated. If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary across the field. Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction \parencite{Piepho2011Statistical}. Hence, for this scenario a systematic design is preferable to a randomised design. Unfortunately, this standpoint has been ignored by researchers, meaning that randomised designs have been universal.

To analyse a systematic design for the creation of the optimal treatment map for OFE is statistically challenging. The truly localised estimation at each point on the grid is unknown and the optimum treatment response continuously varies spatially on the field. \textcite{Cao2021Bayesian} implemented a Bayesian approach of spatially correlated random parameters for large systematic OFE strip trials. They assumed a quadratic response in the model, consisting of a global component and a local spatially varying component. However, the Bayesian approach is time-consuming and requires preliminary knowledge of Bayesian statistics for farmers and agronomists. Alternatively, \textcite{Rakshit2020Novel} adapted a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE. Additionally, \textcite{Evans2020Assessment} conclude that, through simulation studies, GWR is a simple method for the analysis of OFE data and is able to accurately separate yield variation that is not due to the applied treatment from yield response due to treatment. The limitation in the study is that they used a randomised design and assumed a linear response to fertiliser treatment.

%The role of variable-rate applicators has a focus on the application of fertilizers or fungicides to target enable the most efficient yields.

\textcite{Piepho2018Tutorial} demonstrate an example that a linear model is lack of fit on the sugar beets data \parencite{Petersen1994Agricultural}. \textcite{Glynn2007} show that many curves exist beyond a linear trend for nutrient-response relationships. 
%However, when modelling this process it is still common to see linear approximations made \parencite{}. 
%While segments of nutrient-response relationships may be linear, they will generally exhibit inflection points which arise from processes such as sufficiency or toxicity. 
The curve depends on the current availability of other macro and micro nutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial. For this reason, it is important to consider models with degrees higher than 1, with a quadratic model found to be adequate relationships (\textcite{Piepho2018Tutorial, Liben2019}).

%Other relationships have been  with the potential for other more complex polynomials possible but can be prone to over-fitting. %\ref{Add a reference}.

% nature than linear curves. 
%

Our study uses a few simulation examples to demonstrate that randomisation is not a crucial prerequisite for large OFE strip trials, and, in the purpose of obtaining a treatment map, a systematic design is superior over a randomised design subject to appropriate restrictions. We also test the power of GWR, allowing us to know if it can successfully estimate spatially varying coefficients for both linear and quadratic responses to treatments. It shows that the optimal bandwidths found by AICc is not the best bandwidth for GWR, but a fixed bandwidth based on the experimental design is recommended.

The structure of the paper is organised as follows: in Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and the GWR model for fitting OFE data. In Section \ref{Sec:Simu}, we generate simulated data for the combination of the following scenarios: randomised and systematic designs; linear and quadratic response; low and high coefficient correlations; spatial variation among grids is identity (no spatial trend), $\AR\otimes\AR$ and \Matern form. Finally, in Sections \ref{Sec:Res} and \ref{Sec:Dis}, we illustrate the results and discuss their importance with respect to OFE, and how the findings should influence future trial designs.

\section{Methods}\label{Sec:Meth}

This section describes the statistical model used in the simulation study. It outlines the basic model (subsection \ref{sec:basic}) followed by the methodology for the spatially correlated treatment parameters (subsection \ref{sec:spatial}), and finally GWR (subsection \ref{sec:gwr}).

%and explains the statistical aspects of the models with spatially correlated coefficients.

\subsection{Basic statistical model}\label{sec:basic}

In a conventional agricultural study, a field experiment can be considered as a rectangular array, consisting of $r$ rows and $c$ columns, where the total number of the plots in the experiment is $n=r\times c$. The notation $s_i\in \mathcal{R}^2, i=1,\ldots,n$ is a two-cell vector of the Cartesian coordination of the plot centroids, located on a regular grid \parencite{Zimmerman1991Randoma}. Hence, $y(s_i)$ denotes the dependent variable at a query location/grid $i$.

With the assumption that $\bm{Y}$ is the vector of the plot data ordered as rows nested within ranges (columns), then the matrix notation of the model is 
\begin{equation}\label{eq:modelmatrix}
	\bm{Y} = \bm{X}\bm{b}+\bm{Z}\bm{u}+\bm{e},
\end{equation}
where $\bm{b}$ and $\bm{u}$ are vectors of fixed and random effects, respectively; $\bm{X}$ and $\bm{Z}$ are the associated design matrices; and $\bm{e}$ is the error vector. We further assume that $\bm{u}$ and $\bm{e}$ are pairwise independent and that their joint distribution is 
\begin{equation}\label{eq:covariance}
	\begin{bmatrix}
		\bm{u} \\ \bm{e}
	\end{bmatrix} \sim \N\left( \begin{bmatrix}
		0\\0 \end{bmatrix}, \begin{bmatrix}
		\Sigma_u & 0 \\ 0 & \Sigma_e
	\end{bmatrix}\right). 
\end{equation}

\subsection{Spatially correlated treatment parameters}\label{sec:spatial}

\textcite{Cao2021Bayesian} implemented the Bayesian hierarchical model with spatially correlated random parameters on large OFE strip trials. Here, for the simulation study, we use the same model to generate the simulated data.

With the same notation given in the reference and previous section, the underlying model is represented as 
\begin{equation}\label{eq:underlying}
	\begin{split}
		y(s_i)\mid \bm{u}_i,\theta_u,\sigma_e &\sim \N\left( \sum_{m=1}^{l}b_m x_m(s_i) + \sum_{j=1}^{k}u_j(s_i)z_j(s_i),~e(s_i)\right) \\
		\bm{u}_i \mid \theta_u &\sim \N(0,V_u(\theta_u))\\
		e(s_i) \mid \sigma_e &\sim \N(0,\sigma_e^2) 
	\end{split}
\end{equation}
where: $x_1,\ldots, x_l$ denote $l$ fixed effects and $z_1,\ldots, z_k$ denote $k$ random effects; $b_m$ and $u_j(s)$ are the coefficients for the fixed and random terms, respectively; $\bm{u}_i$ is a vector of all random effects at grid $s_i\in\mathcal{S}$, $i=1,\ldots,n$; $\theta_u$ is a set of parameters of the covariance matrix $V_u$; and $\sigma_e$ is a positive latent variable.

In \eqref{eq:underlying}, the structure of the covariance matrix $V_u(\theta_u)$ of $\bm{u}_i$ can be either diagonal, which means the treatments at grid $i$ are independent, or in general form, which means a correlation exists. \textcite{McElreath2015Statistical} suggest that the covariance of $\bm{u}_i$ can be $V_u = B(\sigma_u)R_uB(\sigma_u)$, where $B(\sigma_u)$ denotes the diagonal matrix of elements $\sigma_{u_j}$, $j=1,\ldots,k$, and $R_u \sim \mbox{LKJ}(\epsilon)$ is a correlation matrix controlled by a positive parameter $\epsilon$. As $\epsilon$ increases, a high correlation among parameters becomes less likely.

Furthermore, by incorporating a spatial correlation structure $V_s$, the complete form of the covariance matrix of $\bm{u}$ is presented as 
\begin{equation}\label{eq:varu}
	\Sigma_u = V_s \otimes V_u. 
\end{equation}
In fact, $V_s$ is the covariance matrix of all grids on the field. For example, if $V_s=I_{n\times n}$ is an identity matrix, each grid is independent even though the treatments within each grid are correlated. However, the correlation among grids is ubiquitous. Hence, we introduce a simple spatial covariance matrix such that 
\begin{equation}\label{eq:ar1cov}
	V_s = \AR(\rho_c)\otimes \AR(\rho_r),
\end{equation}
where AR1 is the separable first-order autoregressive model in the column and row direction which is controlled by the correlation parameters $\rho_c$ and $\rho_r$, respectively \parencite{Butler2017ASRemlR}.

Besides the above $\AR\otimes\AR$ covariance, the \Matern class covariance  
\begin{equation}\label{eq:matcov}
V_s(d) = \sigma^2 \frac{2^{1-\nu}}{\Gamma(\nu)} \left( \sqrt{2\nu} \frac{d}{r}\right)^\nu K_\nu\left( \sqrt{2\nu} \frac{d}{r}\right)
\end{equation}
is also used in spatial analysis \parencite{Cressie1999Classes} and in capturing spatial variation in OFE \parencite{Selle2019Flexible}. Here, $d$ is the space lag or distance; $r$ is a non-negative scaling parameter; $\nu> 0$ is a smoothness parameter determining the mean-square differentiability of the field; $\sigma_d^2$ is the variance of the process; $\Gamma$ is the Gamma function; and $K_\nu$ is the modified Bessel function of the second kind. If $\nu = r + \frac{1}{2}$, then the \Matern covariance can be expressed as a product of an exponential and a polynomial of order $r$ \parencite{Pandit2019Comparative, Abramowitz1974Handbook}, which simplifies the model and the computation process. The \Matern class $\nu=\frac{3}{2}$ and $\nu =\frac{5}{2}$ are common in application.

Model \eqref{eq:underlying} has the advantage of reproducibility in simulation study and robustness in estimation. It is possible even though only a single treatment is directly observed at each plot, and the responses of the other levels need to be estimated by interpolation because the spatial model allows using information from neighbouring plots with other treatments \parencite{Panten2010Enhancing, Piepho2011Statistical}.

\subsection{Geographically weighted regression (GWR)}\label{sec:gwr}

Geographically weighted regression (GWR) is a local regression approach and is adapted to obtain spatially-varying estimates of treatment effects for OFE \parencite{Rakshit2020Novel}.  It is seen as a locally weighted regression method that operates by assigning a weight to each observation $i$ depending on its distance from the query grid on the field \parencite{Paez2002General}.

The underlying template model for the GWR, according to \textcite{Leung2000Statistical}, is given by 
\begin{equation}\label{eq:basicgwr}
	y(s_i) = \beta_0 + \sum_{j=1}^{k} \beta_jz_j(s_i)+\varepsilon_i, 
\end{equation}
where $\bm{\beta}$ and $\varepsilon\sim \N(0,\tau^2)$ are the model parameters for the $k$ levels treatments and error terms, respectively, at grid $i,\ i=1,\ldots,n$. The estimator of this model is given by the geographically weighted expression in 
\begin{eqnarray}\label{eq:betahat}
	\bm{\hat{\beta}}(s) = \left( Z^\top W(s) Z \right)^{-1}Z^\top W(s) Y,
\end{eqnarray}
where $W(s)$ is an $n\times n$ diagonal matrix of weights, $\bm{w}$. Then it can be found by maximising the local log-likelihood 
\begin{eqnarray}\label{eq:locallog}
	\log L(s;\beta) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_jz_j(s_i) \right)^2 
\end{eqnarray}
with a given kernel function $K(\cdot,\cdot)$, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}. In the simulation study, we use Gaussian kernel. In fact, kernel is not a crucial factor in GWR model fitting on OFE data. By contrast, the factor bandwidth has higher influence on the estimation.

The optimal bandwidth of a GWR model is usually given by the lowest AICc where 
\begin{equation}\label{eq:aicc}
	\mbox{AICc} = 2n\log (\tau^2) + n \log (2\pi) + n\frac{ n+\tr (S) }{n-2-\tr (S)},
\end{equation}
and $S$ is the matrix with the $i$-th row given by $Z_i\left( Z^\top W(s_i) Z \right)^{-1}Z^\top W(s_i)$ \parencite{Evans2020Assessment}. Alternatively, as suggested by \textcite{Rakshit2020Novel}, it can be based on the experimental design such that the local regressions capture data covering the full range of treatments.

The GWR model in this paper is implemented with the \R-package \texttt{GWmodel} \parencite{lu2014gwmodel, Gollini2015GWmodel}.

\section{Simulation study}\label{Sec:Simu}

To study the effect of randomised designs and systematic designs and to evaluate the power of GWR, we simulate spatially correlated large strip trials. The advantage of the simulation study is that the actual coefficients of the models are known, so adverse effects of model misspecification
can be ruled out \parencite{Piepho2013Why}.

We investigate the combination of the following factors: types of designs with two levels: randomised and systematic; response relationship with two levels: linear and quadratic; correlation of coefficients with two levels: low and high; spatial variation with three levels: identity (no spatial trend), $\AR\otimes\AR$ and \Matern form; bandwidth of GWR with three levels: 5, 9 and optimum given by AICc. The fixed bandwidth 5 in the simulation study covers all treatment levels (five nitrogen levels) in a systematic design, where the information is adequate in the inference of a quadratic curve. Similarly, the fixed bandwidth 9 covers all possible treatment levels in a randomised design. This is because if all treatments are randomly allocated in the strips, there is a chance that the information of one treatment level is missing if the bandwidth is less than 9.

With model \eqref{eq:underlying}, we generate the yield as a response to the nitrogen treatment in two scenarios which cover whether the yield has a linear or quadratic relationship with nitrogen rate. The nitrogen rates are treated as continuous observations with five levels: 0, 35, 75, 105 and 140 kg/ha. A strip plot structure was used to allocate the five nitrogen levels where each level is assigned to one strip. Then we assume that the experimental design of the trial consists of four replicates, each containing 5 ranges (columns) by 93 rows. The nitrogen rates are allocated either randomly or systematically on the whole field. The overall layout of the trial is 20 ranges by 93 rows. Examples of a randomly and systematically allocated treatment map are presented in Figure \ref{fig:Nitrogen}.

\begin{figure}[!htp]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/RandNitro.pdf}
		\caption{Treatments are randomly allocated into large strips.}
	\end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/SystNitro.pdf}
		\caption{Treatments are systematically allocated into large strips.}
	\end{subfigure}
	\caption{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (a) and systematically (b) allocated into strips.}\label{fig:Nitrogen}
\end{figure}

With model \eqref{eq:underlying}, the nitrogen rates are treated as continuous observations with five levels. For a linear relationship, we assume that the true global intercept is $b_0 = 65$ and the slope is $b_1=0.05$. The parameters are chosen according to the estimates by \textcite{Rakshit2020Novel} on the Las Rosas corn field data from the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}. The variances of $\bm{u}_i$ are $\sigma_{u_0} = 5$ and $\sigma_{u_1}=0.01$. For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters for column and row are $\rho_c = 0.15$ and $\rho_r=0.5$. We have assumed a higher correlation in the rows due to the fact that the crop are traditionally sown and harvested along ranges where the correlation is higher in perpendicular to the travel direction \parencite{Marchant2019Establishinga}. For the \Matern covariance matrix \eqref{eq:matcov}, we set $\sigma_d^2=1$, $r=1$ and $\nu = \frac{3}{2}$. After drawing samples of $\bm{u}$ from $\N(0,\Sigma_u)$, the true spatially varying coefficients are $\bm{\beta}_0 = b_0 + \bm{u}_0$ and $\bm{\beta}_1 = b_1 + \bm{u}_1$.

Similarly, for the quadratic relationship, we have the true global intercept $b_0 = 65$, coefficients $b_1 = 0.05$ and $b_2 = -0.0003$, 
%where the curve is in a frown shape. 
making the curve concave down. We keep $\sigma_{u_0} = 5$, $\sigma_{u_1}=0.01$ and add $\sigma_{u_2}=0.0001$ because the true values are small. The remaining parameters stay unchanged. Therefore, the true spatially varying coefficients are $\bm{\beta}_0 = b_0 + \bm{u}_0$, $\bm{\beta}_1 = b_1 + \bm{u}_1$ and $\bm{\beta}_2 = b_2 + \bm{u}_2$.

To summarise, with the true spatially varying coefficients of the treatments, the simulated yield is obtained by 
\begin{equation}
\begin{cases}
	% \text{Linear}  &y_i = b_0 + b_1N_i + u_{0i} + u_{1i}N_i + e_i \\
	\text{Linear}  &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + e_i \\
	% \text{Quadratic} &y_i = b_0 + b_1N_i + b_2N_i^2 + u_{0i} + u_{1i}N_i  + u_{2i}N_i^2 + e_i
	\text{Quadratic} &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + (b_2 + u_{2i})N_i^2 + e_i
\end{cases},
\end{equation}
where $N_i$ is the nitrogen rate, $e_i\sim \N(0,1)$ is the error term at grid $i$, $i = 1, \ldots, n$. Figure \ref{fig:Lines} illustrates how these curves behave for the linear and quadratic relationships.

\begin{figure}[H]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/Linlines.pdf}
		\caption{Linear relationship of yield to nitrogen level.}
	\end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/Qualines.pdf}
		\caption{Quadratic relationship of yield to nitrogen level.}
	\end{subfigure}
	\caption{Noise-free linear and quadratic response to fertiliser treatment.}\label{fig:Lines}
\end{figure}

% Examples of the yield maps with true $\AR\otimes\AR$ spatially varying coefficients are in Figures \ref{fig:LinearYieldMap} and \ref{fig:QuadYieldMap}. 
% \begin{figure}[!htp]
% 	\centering
% 	\begin{subfigure}[t]{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\linewidth]{Expt/LinearRandYield01.pdf}
% 		\caption{Yield map of the linear response of the randomised design. }
% 	\end{subfigure}
% 	\begin{subfigure}[t]{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\linewidth]{Expt/LinearSystYield01.pdf}
% 		\caption{Yield map of the linear response of the systematic design. }
% 	\end{subfigure}
% 	\caption{Yield maps of linear response of randomly and systematically allocated nitrogen rates.}\label{fig:LinearYieldMap}
% \end{figure}

% \begin{figure}[!htp]
% 	\centering
% 	\begin{subfigure}[t]{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\linewidth]{Expt/QuadRandYield01.pdf}
% 		\caption{Yield map of the quadratic response of the randomised design. }
% 	\end{subfigure}
% 	\begin{subfigure}[t]{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\linewidth]{Expt/QuadSystYield01.pdf}
% 		\caption{Yield map of the quadratic response of the systematic design. }
% 	\end{subfigure}
% 	\caption{Yield maps of quadratic response of randomly and systematically allocated nitrogen rates.}\label{fig:QuadYieldMap}
% \end{figure}

%% To fit the data, we use basic GWR with Gaussian kernels.

The purpose of the simulation study is to test the effect of different types of designs in coefficients estimation by GWR. Identical coefficients were used in one comparison process for two types of designs, and the yield reflects the effect of nitrogen rates.

\section{Results}\label{Sec:Res}

By running the simulation 100 times, we assessed the performance of the randomised and systematic designs for linear and quadratic responses. In subsection \ref{Sec:MSE} the mean squared errors are compared between the two designs for different bandwidths, parameter correlations and spatial covariance matrices. Subsection \ref{Sec:anova} uses an analysis of variance (ANOVA) test to explore the significance of the factors in the simulation, while subsection \ref{Sec:bandselect} states the performance of bandwidth selection using AICc.

%By running the simulation 100 times,

\subsection{Mean squared error}\label{Sec:MSE}

We assessed the true mean squared error (MSE) of estimated coefficients differences. This was calculated by the difference of true coefficients, $\bm{\beta} = b + \bm{u}$, and estimated spatially varying coefficients, $\bm{\hat{\beta}} = \hat{b}+\bm{\hat{u}}$, for each grid, and then squared the discrepancy and averaged across the field for comparison. The results are shown in Figures \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE} where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$), ``AR1'' is for $\AR(0.15)\otimes \AR(0.5)$ and ``Matern'' is the \Matern covariance with $\nu=\frac{3}{2}$. Since the MSE of $\beta_0$, $\beta_1$ and $\beta_2$ are small, we take the natural logarithm for better visualisation.

% Paragraph about Figure 3 and the performance for a linear response
With the assumption of a linear response, both randomised and systematic designs performed similarly, meaning GWR is able to partition the local varying intercept and treatment coefficient. Figure \ref{fig:LinBetaMSE} shows that if the response is linear, the MSE of $\hat{\beta}_0$ and $\hat{\beta}_1$ estimated by GWR
%with bandwidth 5, 9 and the optimal bandwidth found by AICc
, for all bandwidths,
is not distinguishing between randomised and systematic designs. This is true regardless of the type of spatial covariance matrix when the correlation within grids is small ($\epsilon=1$), or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}. The GWR with bandwidth selected by AICc had a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{Expt/LinCombMSE_newpar.pdf}
	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response. The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation between the parameters ($\epsilon=1$).}\label{fig:LinBetaMSE}
\end{figure}

% Paragraph about Figure 4 and the performance for a linear response
However, if the assumption is a quadratic response, Figure \ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show that the GWR with a fixed bandwidth of a systematic design outperforms a randomised design if the spatial correlation is taken into account. With the optimal bandwidth, GWR successfully estimates the global intercepts $\beta_0$, but failed in estimating local varying coefficients $\beta_1$ and $\beta_2$, where the MSE is relatively larger than with fixed bandwidth. However, if we only compare across two types of designs, it still proves that GWR is robust to fit a systematic design rather than a randomised design if the assumption is quadratic response, regardless the intensity of the correlation within grids.

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{Expt/QuaCombMSE_newpar.pdf}
	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response. The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation amongst the parameters ($\epsilon=1$).} \label{fig:QuadBetaMSE}
\end{figure}

% Bandwidth MSE Result

The relative MSE for each bandwidth was found to change according to the spatial covariance matrix as well as the coefficient. When no spatial variation was simulated for $\beta_1$ and $\beta_2$, the bandwidth selected by AICc had the lowest MSE, followed by the bandwidths 9 and then 5. When there was spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ had lowest MSE when using bandwidth 9, followed by 5 and then bandwidth from AICc. The intercept ($\beta_0$) showed only significant changes in MSE amongst the bandwidths when the \Matern spatial covariance was considered. In this case, the bandwidth selected by AICc produced the smallest MSE.

Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} are the median MSE of linear response for two scenarios: correlation is low and correlation is high.

\begin{table}[H]
	\centering
\begin{threeparttable}
	\caption{Median MSE of GWR coefficient estimates for a linear response when the correlation between the parameters is low ($\epsilon=1$).}\label{tb:MSElinear}
	\begin{tabular}{llcccccc}
		\toprule
		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
   		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
		\multirow{2}{*}{NS}   & $\hat{\beta}_0$ & 24.903 &	24.924 &	24.983&	24.886\tnote{$\dagger$} &	24.911 &	24.965 \\ 
		& $\hat{\beta}_1 (\times 10^3)$ & 0.147&	0.118&	0.105&	0.147&	0.117&	0.104\tnote{$\dagger$}  \\  \midrule
		\multirow{2}{*}{AR1}  & $\hat{\beta}_0$ & 24.308&	24.617&	24.126&	24.319&	24.617&	23.246\tnote{$\dagger$}  \\ 
		& $\hat{\beta}_1 (\times 10^3)$ & 0.215	&0.147	&1.208&	0.214&	0.146\tnote{$\dagger$}	&1.143 \\ \midrule
		\multirow{2}{*}{\Matern} & $\hat{\beta}_0$ & 21.303	&23.566	&9.647&	21.164&	23.526&	9.239\tnote{$\dagger$} \\ 
		& $\hat{\beta}_1 (\times 10^3)$ & 0.157	&0.121&	0.845&	0.138&	0.115\tnote{$\dagger$} &	0.749 \\
		\bottomrule
	\end{tabular}
	\begin{tablenotes}
	\item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
	\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]
	\centering
\begin{threeparttable}
	\caption{Median MSE of GWR coefficient estimates of linear response when the correlation between the parameters is high ($\epsilon=0.1$).}\label{tb:MSElinearHigh}
	\begin{tabular}{llcccccc}
		\toprule
		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
		& Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
		\multirow{2}{*}{NS}   & $\hat{\beta}_0$  & 24.961	&24.991	&24.958	&24.934\tnote{$\dagger$}	&24.992	&25.020 \\
		& $\hat{\beta}_1 (\times 10^3)$ & 0.144&	0.115&	0.103\tnote{$\dagger$} &	0.145&	0.116&	0.104 \\ \midrule
		\multirow{2}{*}{AR1$\otimes$AR1}  & $\hat{\beta}_0$  & 24.234&	24.518&	23.696&	24.171	&24.497&	23.421\tnote{$\dagger$}  \\
		& $\hat{\beta}_1 (\times 10^3)$   & 0.216	&0.144\tnote{$\dagger$} &	1.024&	0.211&	0.146&	1.027 \\ \midrule
		\multirow{2}{*}{\Matern} & $\hat{\beta}_0$  & 20.882&	22.811&	9.823&	20.770	&22.789	&9.257\tnote{$\dagger$}  \\
		& $\hat{\beta}_1 (\times 10^3)$  & 0.152&	0.120&	0.939&	0.140&	0.112\tnote{$\dagger$} &	0.815 \\ 
		\bottomrule
	\end{tabular}
		\begin{tablenotes}
	\item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
	\end{tablenotes}
\end{threeparttable}
\end{table}

\vspace{12pt}

Tables \ref{tb:MSEquadratic} and \ref{tb:MSEquadraticHigh} are the median MSE of quadratic response for two scenarios: correlation is low and correlation is high. Despite the correlation intensity, the data fitted by GWR from systematical designs are superior to randomised designs, having a smaller MSE.

\begin{table}[H]
	\centering
\begin{threeparttable}
	\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is low ($\epsilon=1$).}\label{tb:MSEquadratic}
	\begin{tabular}{llcccccc} \toprule
		 &  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
		  & Coefficient & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
		\multirow{3}{*}{NS}   & $\hat{\beta}_0$ & 25.218 & 25.150 & 25.152  & 25.263 & 25.179 & 25.138\tnote{$\dagger$}  \\
		& $\hat{\beta}_1 (\times 10^4)$ & 7.417  & 3.823  & 1.625 & 7.233  & 3.529  & 1.516\tnote{$\dagger$}  \\
		& $\hat{\beta}_2 (\times 10^8)$  & 4.157  & 2.168  & 1.242\tnote{$\dagger$} & 4.135  & 2.269  & 1.269   \\ \midrule 
		\multirow{3}{*}{AR1$\otimes$AR1}  & $\hat{\beta}_0$  & 25.185 & 25.092\tnote{$\dagger$} & 30.315  & 25.166 & 25.230 & 27.831  \\
		&$\hat{\beta}_1 (\times 10^4)$  & 18.395 & 7.414  & 151.595 & 16.243 & 7.124\tnote{$\dagger$}  & 123.181  \\
		& $\hat{\beta}_2 (\times 10^8)$ & 9.491  & 4.244  & 74.420  & 8.305  & 3.777\tnote{$\dagger$}  & 61.619 \\ \midrule
		\multirow{3}{*}{\Matern} & $\hat{\beta}_0$  & 21.532 & 23.502 & 17.680  & 21.384 & 23.319 & 15.631\tnote{$\dagger$} \\
		&$\hat{\beta}_1 (\times 10^4)$  & 9.502  & 4.326  & 112.914 & 6.121  & 2.901\tnote{$\dagger$}  & 96.829  \\
		& $\hat{\beta}_2 (\times 10^8)$  & 5.071  & 2.537  & 56.789  & 3.324  & 1.889\tnote{$\dagger$}  & 44.707 \\ \bottomrule
	\end{tabular}
	    \begin{tablenotes}
	        \item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
	    \end{tablenotes}
\end{threeparttable}
\end{table}

\begin{table}[H]
	\centering
\begin{threeparttable}
	\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is high ($\epsilon=0.1$).}\label{tb:MSEquadraticHigh}
	\begin{tabular}{llcccccc} \toprule
		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
		$\epsilon=0.1$  & Coefficients & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
		\multirow{3}{*}{NS} & $\hat{\beta}_0$  & 25.075 & 25.067 & 25.015  & 25.082 & 25.060 & 25.012\tnote{$\dagger$} \\
		&$\hat{\beta}_1 (\times 10^4)$  & 6.683  & 3.466  & 1.478\tnote{$\dagger$} & 7.353  & 3.472  & 1.506 \\
		&$\hat{\beta}_2 (\times 10^8)$  & 3.779  & 2.101  & 1.222\tnote{$\dagger$} & 3.806  & 2.124  & 1.284 \\  \midrule
		\multirow{3}{*}{AR1$\otimes$AR1} & $\hat{\beta}_0$  & 25.103 & 25.223 & 29.266  & 25.033 & 25.032\tnote{$\dagger$} & 27.378 \\
		& $\hat{\beta}_1 (\times 10^4)$ & 16.260 & 6.845  & 130.335 & 16.228 & 6.314\tnote{$\dagger$}  & 112.599  \\
		& $\hat{\beta}_2 (\times 10^8)$  & 8.488  & 3.931  & 61.765  & 7.915  & 3.533\tnote{$\dagger$}  & 54.866  \\  \midrule
		\multirow{3}{*}{\Matern} & $\hat{\beta}_0$ & 21.780 & 23.622 & 18.832  & 21.409 & 23.296 & 15.728\tnote{$\dagger$}  \\
		& $\hat{\beta}_1 (\times 10^4)$ & 11.367 & 5.085  & 122.638 & 6.205  & 2.892\tnote{$\dagger$}  & 88.256 \\
		& $\hat{\beta}_2 (\times 10^8)$  & 5.979  & 2.981  & 60.298  & 3.025  & 1.803\tnote{$\dagger$}  & 43.156  \\ \bottomrule
	\end{tabular}
		    \begin{tablenotes}
	        \item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
	    \end{tablenotes}
\end{threeparttable}
\end{table}

\subsection{ANOVA}\label{Sec:anova}

Furthermore, ANOVA techniques were used for the analyses of the above results. The analyses were performed for two scenarios of different responses separately. For each response, the coefficients were also accounted for in the model. The objective of the analysis was to investigate the five main factors: two types of design, three bandwidths, three covariance matrices, coefficients $\bm{\beta}$ and the correlation $\epsilon$. The significance patterns of the second order interactions was also of interest. The results are listed in Table \ref{tb:LMMoutput}.

The results are consistent with what was observed in the subsection above in that, for the linear response, the difference between randomised and systematic designs was not significant. However, for the quadratic response, the design and its interactions with bandwidth and the coefficients were significant. For both scenarios, the correlation intensity and all of its interactions were not significant (Table \ref{tb:LMMoutput}). Hence, GWR performs similarly with either low or high correlation between coefficients. Also of note was that the Bandwidth, and its second order interactions with the variables other than the correlation, was found to be significant for both response types.

\begin{table}[H]
	\centering
	\caption{ANOVA analyses were conducted on the main factors and their second order interactions. The table lists degrees of freedom (Df), sum of squared errors (Sum Sq) and p-values of F tests (Pr($>$F)). }\label{tb:LMMoutput}
	\begin{tabular}{r | lll | lll}
		\toprule
		 & \multicolumn{3}{c|}{Linear}  & \multicolumn{3}{c}{Quadratic}  \\
    & Df & Sum Sq  & Pr(\textgreater{}F) & Df & Sum Sq  & Pr(\textgreater{}F) \\ \midrule 
Design & 1  & 8.46  & 0.0935  & 1  & 74.03 & \textless{}0.001  \\
Bandwidth & 2  & 7453.09 & \textless{}0.001  & 2  & 90.29  & \textless{}0.001  \\
Covariance ($V_s$)  & 2  & 16958.42  & \textless{}0.001  & 2  & 6122.84 & \textless{}0.001 \\
Coefficients ($\beta$)  & 1  & 903705.52 & \textless{}0.001  & 2  & 1419372.21 & \textless{}0.001  \\
Correlation  ($\epsilon$)  & 1  & 5.63  & 0.171   & 1  & 0.07  & 0.8976  \\
Design:Bandwidth  & 2  & 9.21 & 0.216  & 2  & 113.48   & \textless{}0.001  \\
Design:Covariance & 2  & 3.91 & 0.5217  & 2  & 37.55  & 0.0134 \\
Design:Coefficients  & 1  & 8.45 & 0.0935  & 2  & 147.55 & \textless{}0.001  \\
Design:Correlation  & 1  & 0  & 0.9832  & 1  & 0.01  & 0.9541  \\
Bandwidth:Covariance   & 4  & 12283.13  & \textless{}0.001  & 4  & 3135.47  & \textless{}0.001  \\
Bandwidth:Coefficients & 2  & 7456.81 & \textless{}0.001  & 4  & 179.38 & \textless{}0.001  \\
Bandwidth:Correlation  & 2  & 5.95  & 0.3716  & 2  & 0.85  & 0.9073  \\
Covariance:Coefficients  & 2  & 16959.68  & \textless{}0.001  & 4  & 12248.74 & \textless{}0.001  \\
Covariance:Correlation & 2  & 0.26  & 0.9572  & 2  & 11.57  & 0.2649  \\
Coefficients:Correlation & 1  & 5.63  & 0.171   & 2  & 0.15  & 0.9834  \\ \bottomrule  
	\end{tabular}
\end{table}

% For linear response, the type of design is not a key factor that the design and its interactions with other factors are not significant. On the contrary, if the response is quadratic, design becomes a key factor and the interactions are significant as well. For both scenarios, the correlation intensity and most of its interactions are not significant. Hence, either low or high correlation between coefficients works well with GWR. Moreover, bandwidth selection should be based on the design rather than optimality criteria. The results are consistent with the above boxplots.

\subsection{AICc Bandwidth selection}\label{Sec:bandselect}

From the simulation study, we found that the bandwidth given by AICc skewed to 1 if spatial covariance was included in the model, for all types of the design and nature of the response. If spatial covariance was not introduced, the GWR tended to use all data in one row (Figure \ref{fig:histband}).

\begin{figure}[H]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/BandwidthLinear.pdf}
		\caption{Histogram of optimal bandwidth for linear response.}
	\end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/BandwidthQuadra.pdf}
		\caption{Histogram of optimal bandwidth for quadratic response.}
	\end{subfigure}
	\caption{Histogram of optimal bandwidth found by AICc for linear and quadratic response. }\label{fig:histband}
\end{figure}

\section{Discussion}\label{Sec:Dis}

%1. Summary of Main Findings
Agronomists and biometricians generally prefer randomised designs for OFE trials. According to the performance metrics used, our simulation study shows a systematic design performed either preferably or similarly to a randomised design for the purposes of creating a varying treatment map. The differentiating factors included primarily the response type and the spatial covariance model, while the correlation amongst the treatment coefficients was not found to be important. These are factors which can be assessed by the farmer beforehand, and this should dictate which design should be used. However, given that a systematic design is easier to implement in the field, and shows little downside for the purposes of creating a varying treatment map, we will advocate for the use of systematic designs.

%2. How response type affected the performance, and what this means
The response type was the main differentiating factor between randomised and systematic designs. When the response was quadratic, the systematic design performed favourably which contrasted the result for the linear design which saw low differentiation between the designs. Given this, if a farmer expects an approximately linear response in the field, then the selection of the design may not be important. However, given the variable nature of the relationship between response and treatment over a large field (see i.e \textcite{Rakshit2020Novel}), it may be wise to implement a systematic design for the potential outcome of a quadratic relationship. 
%For other more complex response types (i.e polynomials of order greater than 2) it is predicted that a systematic design will also perform favourably. \textcolor{red}{?ref}
%(\textcolor{red}{Might not need a reference)}.

%2. Discussing Spatial Covariance Structures
%- Some Questions that might be interesting to answer
%- Is a \Matern class more realistic and what are its limitations? %- 
Another consideration for farmers as to which design to use is the expected spatial covariance structure in the field. When no spatial structure was simulated, the differences between the prediction from the systematic and random design were minimal. This result should be expected given if there are no spatial autocorrelations, then the individual query grids are independent observations and therefore the design is not important. However, when a first-order autoregressive structure was simulated the differences were noticeable when a quadratic response was used, showing systematic designs to be preferential. The largest difference between the two designs came when considering the \Matern spatial covariance structure, which showed a clear preference for systematic designs when a quadratic response was considered, and also a small preference for systematic designs for a linear response. Therefore, only if spatial variability was predicted to be negligible in the field would using a randomised design be reasonable given a quadratic response. This assumption of negligible spatial variability would be tough to reason with given the large fields used in on-farm experimentation (add reference), meaning that in application a systematic design should be used.

% Spatial stationarity is seldom the case in small plot research trials even in highly controlled environments.

%3. Bandwidth selection and why that is important [good]
There was found to be significant deficiencies in using AICc for bandwidth selection. The AICc-minimising bandwidths skewed to 1 and, in a few cases, ended in 93 (number of rows). Even though the bandwidth was optimal according to AICc, the MSE was higher than when using a fixed bandwidth. Therefore, we recommended using the fixed bandwidth based on the experimental design (5 or 9 in this case), rather than the recommended bandwidth from AICc which is prone to either over-fitting or being too generalised. Selecting the bandwidth based on the experimental design is also theoretically better since only a single measurement is observed in each grid, all levels of the treatment factor should be included in a GWR window at the same time to interpolate the %quadratic curve
relationship. Otherwise, the interpolation is incomplete if more than one level is missing.

% ... AICc-minimising bandwidth were skewed towards the upper ($sqrt(19^2+92^2)=93.94147$) or lower (1) bounds; two characteristics which are suggestive of underlying stationary or random processes  respectively \textcite{}.  
% In this paper, the simulated data is fitted by GWR, which has been proven to accurately separate treatment from non-treatment influence of yield response. One crucial factor of GWR is bandwidth selection. The AICc-minimising bandwidths skew to 1 and, in a few cases, end in 93 (number of rows). Thus, even though the bandwidth is optimal, the MSE is higher than when using a fixed bandwidth. Therefore, we would use the fixed bandwidth of 5 and 9 based on the experimental design, rather than the recommended bandwidth from AICc. Selecting the bandwidth based on the experimental design is also theoretically better. Since only a single measurement is observed in each grid, all levels of the treatment factor should be included in a GWR window at the same time to interpolate the quadratic curve. Otherwise, the interpolation is incomplete if more than one level is missing.

%4. Paragraph on Coefficient importance (or the lack thereof)
%The level of correlation between the coefficients as governed by $\epsilon$ was found to no be significant (Table \ref{tb:LMMoutput}). This indicates that GWR performs similarly with either low or high correlation between coefficients. %This is an unexpected/expected result...

%5. Recommendation of design variations
Given the scope of the paper, some designs and factors were not considered. Designs such as chequerboard or wave designs have been suggested for on-farm experiments \parencite{bramley1999designing}, however weren't able to be considered here. Topographical factors (spatial zones) were also not entertained in our study. Since GWR estimates a global template model and then adjusts it at a local scale across the study region, the variation between zones is ``flushed out'' by the spatial covariance.

%However, this is not practical for farmers as the complex layout of the treatments will increase the cost of sowing and harvesting. Therefore, unless the objective is for variety selection, we do not recommend such designs to agronomists.

%6. Recommendation of other spatial factors to consider, and why those were ignored. 
%Topographical factors (spatial zones) were also not considered in our study. Since GWR estimates a global template model and then adjusts it at a local scale across the study region, the variation between zones is ``flushed out'' by the spatial covariance.

\section{Conclusion}\label{Sec:Conclusion}

Agronomists and biometricians generally prefer randomised designs for OFE trials. With the purpose of creating a varying treatment map, our simulation study proves that a systematic design produces better performance metrics, under particular circumstances, than a randomised design for large on-farm trials in terms of robustness and smaller MSE on coefficients. On the other hand, if the spatial variation is not considered, or if researchers believe in linear response, either a systematic or a randomised design could be implemented because the difference is not significant. We recommend that, for a large OFE trial with the goal to create a varying treatment map, a systemic design should be used as it has more flexibility in post-experiment statistical modelling.

% Perhaps we add a comment along the lines - "Further research is needed in the case of OFE (and GWR?) when it comes to more complex designs such as chequerboard, donut etc."

\section{Acknowledgements}

SAGI West gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).

\appendix

\section{Figures}

\begin{figure}[!htp]
	\centering
	\includegraphics[width=\linewidth]{Expt/LinCombMSE_newpar_eta01.pdf}
	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response. The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation between the parameters ($\epsilon=0.1$).}\label{fig:LinBetaMSEeta01}
\end{figure}

\begin{figure}[!htp]
	\centering
	\includegraphics[width=\linewidth]{Expt/QuaCombMSE_newpar_eta01.pdf}
	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response. The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation amongst the parameters ($\epsilon=0.1$).} \label{fig:QuadBetaMSEeta01}
\end{figure}

\renewcommand\bibname{References}% change bibliography title to references
	%\addcontentsline{toc}{chapter}{Bibliography}
\addtocontents{toc}{Bibliography}
\printbibliography
\end{document}

### 2023-06-22 main.tex
abstract updated

@@
 \usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100]{biblatex}
+\DeclareNameAlias{sortname}{last-first}
 \addbibresource{BayesOFE.bib}
@@
 %\author{Jerome}
-\author[1]{Zhanglong Cao}
-\author[1]{Andrew Grose}
-\author[1]{Jordan Brown}
-\author[1,2]{Suman Rakshit}
+\author[1,2]{Zhanglong Cao}
+\author[1,2]{Andrew Grose}
+\author[1,2]{Jordan Brown}
+\author[1,3]{Suman Rakshit}
+\author[1,2,3]{XXXX}
 
-\affil[1]{SAGI West, School of Molecular and Life Sciences, Curtin University, Perth, Australia}
-\affil[2]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}
+\affil[1]{CBADA, School of Molecular and Life Sciences, Curtin University, Perth, Australia}
+\affil[2]{Centre for Crop and Disease Management, School of Molecular and Life Sciences, Curtin University, Perth, Australia}
+\affil[3]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}
 
@@
 \begin{abstract}
-There is no doubt on the importance of randomisation in agricultural experiments by agronomists and biometricians.
+% There is no doubt on the importance of randomisation in agricultural experiments by agronomists and biometricians.
 Even when agronomists extend the experimentation from small trials to large on-farm trials, randomised designs predominate over systematic designs.
@@
 If the goal of OFE is obtaining a smooth map showing the optimal level of a controllable input across a grid made by rows and columns covering the whole field, a systematic design should be preferred over a randomised design in terms of robustness and reliability.
-With the novel geographically weighted regression (GWR) for OFE and simulation studies, we conclude that, for large OFE strip trials, the difference between randomised designs and systematic designs are not significant if a linear model of treatments is fitted or if spatial variation is not taken into account.
+With the novel geographically weighted regression (GWR) for OFE and simulation studies, we conclude that, for large OFE strip trials, the difference between randomised designs and systematic designs is not significant if a linear model of treatments is fitted or if the spatial variation is not taken into account.
 But for a quadratic model, systematic designs are superior to randomised designs.
+Randomisation is a crucial aspect of agricultural experiments for both agronomists and biometricians.
+While randomised designs are predominantly used for small trials and large on-farm experiments (OFE), the choice between randomised and systematic designs may depend on the objective of the OFE.
+If the goal is to produce a smooth map of optimal input levels across a grid covering the entire field, a systematic design may be preferred for its robustness and reliability.
+Our study using geographically weighted regression (GWR) and simulation shows that for large OFE strip trials, the difference between randomised and systematic designs is insignificant when fitting a linear model or ignoring spatial variation.
+However, for quadratic models with the presence of spatial variation, systematic designs are superior to randomised designs.
 \end{abstract}
@@
 
-The principles of randomisation were first expounded in 1925, when \textcite{Fisher1934Statistical} analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in the rows and columns of a Latin square \parencite{Verdooren2020History}.
+The principles of randomisation were first expounded in 1925, when \textcite{Fisher1934Statistical} analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
 The most straightforward, least restrictive experimental design is the completely randomised design (CRD).
-More complex designs are widely used in agricultural experiments \parencite{Petersen1994Agricultural}, which include randomised complete block, split-plot, strip-plot, and latin square designs.
+More complex designs, such as randomised complete block design, split-plot design, strip-plot design and latin square design, are also widely used in agricultural experiments \parencite{Petersen1994Agricultural}, Following these principles, randomised designs are routinely used from small on-site trials to large on-farm experiments (OFE) in contrast to systematic designs, which are rarely used.
 
@@
 
-Following these principles, randomised designs are routinely used, from small on-site trials to large on-farm experiments (OFE), in contrast to systematic designs which are rarely used.
 OFE enables farmers the flexibility to implement large-scale experiments in order to test management practices on their farms \parencite{Evans2020Assessment}.
@@
 
-Randomisation has been considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, however this is not true when the goal of OFE shifts from what is desired from a conventional analysis.
+Randomisation has been considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, however, this is not true when the goal of OFE shifts from what is desired from the conventional analysis.
 In the application of precision agriculture (PA), a prescription map from the experimental results is required by the variable-rate applicators (VRA) prior to the start of the operation \parencite{Pringle2004FieldScale}.
-Therefore, in this scenario, the goal of OFE becomes obtaining such a smooth map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made by rows and columns covering the whole field.
-For this objective, \textcite{Pringle2004FieldScale} stress that only a single level of the treatments can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
+Therefore, in this scenario, the goal of OFE becomes obtaining a smooth map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
+For this objective, \textcite{Pringle2004FieldScale} stresses that only a single level of the treatments can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
 If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary across the field.
 Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction \parencite{Piepho2011Statistical}.
-Hence, for this scenario a systematic design is preferable to a randomised design.
+Hence, for this scenario, a systematic design is preferable to a randomised design.
 Unfortunately, this standpoint has been ignored by researchers, meaning that randomised designs have been universal.
@@
 The truly localised estimation at each point on the grid is unknown and the optimum treatment response continuously varies spatially on the field.
-\textcite{Cao2021Bayesian} implemented a Bayesian approach of spatially correlated random parameters for large systematic OFE strip trials.
+\textcite{Cao2022Bayesian} implemented a Bayesian approach of spatially correlated random parameters for large systematic OFE strip trials.
 They assumed a quadratic response in the model, consisting of a global component and a local spatially varying component.
@@
 %While segments of nutrient-response relationships may be linear, they will generally exhibit inflection points which arise from processes such as sufficiency or toxicity. 
-The curve depends on the current availability of other macro and micro nutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial.
+The curve depends on the current availability of other macro and micronutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial.
 For this reason, it is important to consider models with degrees higher than 1, with a quadratic model found to be adequate relationships (\textcite{Piepho2018Tutorial, Liben2019}).
@@
 
-Our study uses a few simulation examples to demonstrate that randomisation is not a crucial prerequisite for large OFE strip trials, and, in the purpose of obtaining a treatment map, a systematic design is superior over a randomised design subject to appropriate restrictions.
-We also test the power of GWR, allowing us to know if it can successfully estimate spatially varying coefficients for both linear and quadratic responses to treatments.
-It shows that the optimal bandwidths found by AICc is not the best bandwidth for GWR, but a fixed bandwidth based on the experimental design is recommended.
+Our study uses a few simulation examples to demonstrate that randomisation is not a crucial prerequisite for large strip trials, and, in the purpose of obtaining a treatment map, a systematic design is superior over a randomised design subject to appropriate restrictions.
+We also test the power of GWR, allowing us to know if it can successfully estimate spatially varying treatment effects for both linear and quadratic responses to treatments.
+It shows that the optimal bandwidth found by AICc is not the best bandwidth for GWR, but a fixed bandwidth based on the experimental design is recommended.
 
@@
 
-\textcite{Cao2021Bayesian} implemented the Bayesian hierarchical model with spatially correlated random parameters on large OFE strip trials.
+\textcite{Cao2022Bayesian} implemented the Bayesian hierarchical model with spatially correlated random parameters on large OFE strip trials.
 Here, for the simulation study, we use the same model to generate the simulated data.
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Linlines.pdf}
+		\includegraphics[width=\linewidth]{Expt/LinlinesV2.pdf}
 		\caption{Linear relationship of yield to nitrogen level.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Qualines.pdf}
+		\includegraphics[width=\linewidth]{Expt/QualinesV2.pdf}
 		\caption{Quadratic relationship of yield to nitrogen level.}
@@
 
-We assessed the true mean squared error (MSE) of estimated coefficients differences.
+We assessed the true mean squared error (MSE) of estimated coefficient differences.
 This was calculated by the difference of true coefficients, $\bm{\beta} = b + \bm{u}$, and estimated spatially varying coefficients, $\bm{\hat{\beta}} = \hat{b}+\bm{\hat{u}}$, for each grid, and then squared the discrepancy and averaged across the field for comparison.
@@
 When no spatial variation was simulated for $\beta_1$ and $\beta_2$, the bandwidth selected by AICc had the lowest MSE, followed by the bandwidths 9 and then 5.
-When there was spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ had lowest MSE when using bandwidth 9, followed by 5 and then bandwidth from AICc.
+When there was spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ had the lowest MSE when using bandwidth 9, followed by 5 and then bandwidth from AICc.
 The intercept ($\beta_0$) showed only significant changes in MSE amongst the bandwidths when the \Matern spatial covariance was considered.
@@
 The objective of the analysis was to investigate the five main factors: two types of design, three bandwidths, three covariance matrices, coefficients $\bm{\beta}$ and the correlation $\epsilon$.
-The significance patterns of the second order interactions was also of interest.
+The significance patterns of the second-order interactions was also of interest.
 The results are listed in Table \ref{tb:LMMoutput}.
@@
 For both scenarios, the correlation intensity and all of its interactions were not significant (Table \ref{tb:LMMoutput}).
-Hence, GWR performs similarly with either low or high correlation between coefficients.
-Also of note was that the Bandwidth, and its second order interactions with the variables other than the correlation, was found to be significant for both response types.
+Hence, GWR performs similarly with either a low or high correlation between coefficients.
+Also of note was that the Bandwidth, and its second-order interactions with the variables other than the correlation, was found to be significant for both response types.
 
@@
 
-From the simulation study, we found that the bandwidth given by AICc skewed to 1 if spatial covariance was included in the model, for all types of the design and nature of the response.
+From the simulation study, we found that the bandwidth given by AICc skewed to 1 if spatial covariance was included in the model, for all types of the design and the nature of the response.
 If spatial covariance was not introduced, the GWR tended to use all data in one row (Figure \ref{fig:histband}).
@@
 The differentiating factors included primarily the response type and the spatial covariance model, while the correlation amongst the treatment coefficients was not found to be important.
-These are factors which can be assessed by the farmer beforehand, and this should dictate which design should be used.
+These are factors that can be assessed by the farmer beforehand, and this should dictate which design should be used.
 However, given that a systematic design is easier to implement in the field, and shows little downside for the purposes of creating a varying treatment map, we will advocate for the use of systematic designs.
@@
 Therefore, only if spatial variability was predicted to be negligible in the field would using a randomised design be reasonable given a quadratic response.
-This assumption of negligible spatial variability would be tough to reason with given the large fields used in on-farm experimentation (add reference), meaning that in application a systematic design should be used.
+This assumption of negligible spatial variability would be tough to reason with given the large fields used in on-farm experimentation (add reference), meaning that in the application a systematic design should be used.
 
@@
 Given the scope of the paper, some designs and factors were not considered.
-Designs such as chequerboard or wave designs have been suggested for on-farm experiments \parencite{bramley1999designing}, however weren't able to be considered here.
+Designs such as chequerboard or wave designs have been suggested for on-farm experiments \parencite{bramley1999designing}, however, were not able to be considered here.
 Topographical factors (spatial zones) were also not entertained in our study.

### 2023-07-17 main.tex
new colour plots

@@
 
-%\newcommand{\brms}{\texttt{brms}}
-%\newcommand{\rstan}{\texttt{rstan}}
-%\newcommand{\elpd}{elpd\textsubscript{loo}}
-%\newcommand{\psis}{elpd\textsubscript{psis-loo}}
-%\newcommand{\ploo}{p\textsubscript{loo}}
+\newcommand{\zc}[1]{\textcolor{red}{#1}}
 
@@
 \usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100]{biblatex}
-\DeclareNameAlias{sortname}{last-first}
+\DeclareNameAlias{sortname}{family-given}
 \addbibresource{BayesOFE.bib}
@@
 %\author{Jerome}
-\author[1,2]{Zhanglong Cao}
+\author[1]{Zhanglong Cao}
+\author[1]{Jordan Brown}
 \author[1,2]{Andrew Grose}
-\author[1,2]{Jordan Brown}
-\author[1,3]{Suman Rakshit}
-\author[1,2,3]{XXXX}
+\author[1]{Mark Gibberd}
+\author[1,3]{Julia Easton}
+\author[1,2]{Suman Rakshit}
 
-\affil[1]{CBADA, School of Molecular and Life Sciences, Curtin University, Perth, Australia}
-\affil[2]{Centre for Crop and Disease Management, School of Molecular and Life Sciences, Curtin University, Perth, Australia}
-\affil[3]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}
+\affil[1]{Curtin Biometry and Data Analytic, Centre for Crop and Disease Management, Curtin University, Perth, Australia}
+\affil[2]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}
+\affil[3]{Curtin 4 Agribusiness Profitability Initiative, Centre for Crop and Disease Management, Curtin University, Perth, Australia}
 
@@
 While randomised designs are predominantly used for small trials and large on-farm experiments (OFE), the choice between randomised and systematic designs may depend on the objective of the OFE.
-If the goal is to produce a smooth map of optimal input levels across a grid covering the entire field, a systematic design may be preferred for its robustness and reliability.
-Our study using geographically weighted regression (GWR) and simulation shows that for large OFE strip trials, the difference between randomised and systematic designs is insignificant when fitting a linear model or ignoring spatial variation.
-However, for quadratic models with the presence of spatial variation, systematic designs are superior to randomised designs.
+Suppose the goal is to produce a smooth map of optimal input levels across a grid covering the entire field, in that case, a systematic design may be preferred for its robustness and reliability.
+Our simulation study using the Bayesian hierarchical model and geographically weighted regression (GWR) shows that, for large OFE strip trials, the difference between randomised and systematic designs is insignificant when fitting a linear model or ignoring spatial variation.
+However, for quadratic models, particularly with the presence of spatial variation, systematic designs are superior to randomised designs in terms of smaller true mean squared errors (MSE) of coefficients.
 \end{abstract}
@@
 
-The principles of randomisation were first expounded in 1925, when \textcite{Fisher1934Statistical} analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
+The principles of randomisation were first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
 The most straightforward, least restrictive experimental design is the completely randomised design (CRD).
-More complex designs, such as randomised complete block design, split-plot design, strip-plot design and latin square design, are also widely used in agricultural experiments \parencite{Petersen1994Agricultural}, Following these principles, randomised designs are routinely used from small on-site trials to large on-farm experiments (OFE) in contrast to systematic designs, which are rarely used.
+More complex designs, such as randomised complete block design (RCBD), split-plot design, strip-plot design and Latin square design, are also widely used in agricultural experiments \parencite{Petersen1994Agricultural}.
+Following these principles, randomised designs are routinely used from small on-site trials to large on-farm experiments (OFE), while systematic designs are rarely used.
 
@@
 OFE enables farmers the flexibility to implement large-scale experiments in order to test management practices on their farms \parencite{Evans2020Assessment}.
-The aim of OFE is to enable farmers to improve their competence of uncertainties and to take into account their existing strengths of handling translational and structural uncertainty \parencite{Cook2013Onfarm}.
+The goal of OFE is to help farmers better understand uncertainties and leverage their existing strengths in managing translational and structural uncertainty \parencite{Cook2013Onfarm}.
 In the situation that the goal is to compare yield responses between management classes or to select individuals with the best performance as new market varieties, a randomised design is superior to a systematic design \parencite{Pringle2004FieldScale, Selle2019Flexible}.
@@
 %Like conventional agricultural experiments, 
-
-Randomisation has been considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, however, this is not true when the goal of OFE shifts from what is desired from the conventional analysis.
+While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of on-farm experiments (OFE) shifts from the conventional analysis.
 In the application of precision agriculture (PA), a prescription map from the experimental results is required by the variable-rate applicators (VRA) prior to the start of the operation \parencite{Pringle2004FieldScale}.
 Therefore, in this scenario, the goal of OFE becomes obtaining a smooth map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
-For this objective, \textcite{Pringle2004FieldScale} stresses that only a single level of the treatments can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
+For this objective, \textcite{Piepho2011Statistical} stresses that only a single level of the treatments can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
 If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary across the field.
-Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction \parencite{Piepho2011Statistical}.
-Hence, for this scenario, a systematic design is preferable to a randomised design.
-Unfortunately, this standpoint has been ignored by researchers, meaning that randomised designs have been universal.
+Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction.
+As a result, a systematic design is preferable to a randomised design in this scenario.
+Unfortunately, this perspective has often been overlooked by researchers, leading to the widespread use of randomised designs.
 
-To analyse a systematic design for the creation of the optimal treatment map for OFE is statistically challenging.
-The truly localised estimation at each point on the grid is unknown and the optimum treatment response continuously varies spatially on the field.
-\textcite{Cao2022Bayesian} implemented a Bayesian approach of spatially correlated random parameters for large systematic OFE strip trials.
-They assumed a quadratic response in the model, consisting of a global component and a local spatially varying component.
+Analyzing a systematic design for the creation of an optimal treatment map for on-farm experiments (OFE) is statistically challenging.
+The truly localized estimation at each point on the grid is unknown, and the optimum treatment response varies continuously across the field.
+\textcite{Cao2022Bayesian} implemented a Bayesian approach using spatially correlated random parameters for large systematic OFE strip trials, assuming a quadratic response model with both global and local spatially varying components.
 However, the Bayesian approach is time-consuming and requires preliminary knowledge of Bayesian statistics for farmers and agronomists.
-Alternatively, \textcite{Rakshit2020Novel} adapted a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE.
-Additionally, \textcite{Evans2020Assessment} conclude that, through simulation studies, GWR is a simple method for the analysis of OFE data and is able to accurately separate yield variation that is not due to the applied treatment from yield response due to treatment.
-The limitation in the study is that they used a randomised design and assumed a linear response to fertiliser treatment.
+Alternatively, \textcite{Rakshit2020Novel} adopt a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE.
+Additionally, \textcite{Evans2020Assessment} conclude through simulation studies that GWR is a simple method for the analysis of OFE data and is able to accurately separate yield variation that is not due to the applied treatment from yield response due to treatment.
+However, their study was limited by the use of a randomised design and the assumption of a linear response to fertilizer treatment.
+\textcite{Alesso2021Design} simulated corn yield with four levels of nitrogen assigned systematically and randomly into chessboard designs and fitted the true coefficients using GWR.
+They concluded that systematic designs achieved the best results in most cases.
+However, in these simulation studies, the use of chessboard design presents a problem: harvesters can smooth over abrupt treatment changes between plots, potentially leading to misleading results unless there are constraints on the field \parencite{Pringle2004FieldScale}.
+Additionally, the quadratic or plateau feature was not considered as a factor in the simulations.
 
@@
 
-\textcite{Piepho2018Tutorial} demonstrate an example that a linear model is lack of fit on the sugar beets data \parencite{Petersen1994Agricultural}.
+\textcite{Piepho2018Tutorial} demonstrate an example that a linear model is lack fitting on the sugar beets data \parencite{Petersen1994Agricultural}.
 \textcite{Glynn2007} show that many curves exist beyond a linear trend for nutrient-response relationships.
+The curve depends on the current availability of other macro and micronutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial.
+For this reason, it is important to consider models with degrees higher than 1, with a quadratic model found to be adequate relationships (\textcite{Piepho2018Tutorial, Liben2019}).
 %However, when modelling this process it is still common to see linear approximations made \parencite{}. 
 %While segments of nutrient-response relationships may be linear, they will generally exhibit inflection points which arise from processes such as sufficiency or toxicity.
-The curve depends on the current availability of other macro and micronutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial.
-For this reason, it is important to consider models with degrees higher than 1, with a quadratic model found to be adequate relationships (\textcite{Piepho2018Tutorial, Liben2019}).
 
@@
 
-Our study uses a few simulation examples to demonstrate that randomisation is not a crucial prerequisite for large strip trials, and, in the purpose of obtaining a treatment map, a systematic design is superior over a randomised design subject to appropriate restrictions.
-We also test the power of GWR, allowing us to know if it can successfully estimate spatially varying treatment effects for both linear and quadratic responses to treatments.
-It shows that the optimal bandwidth found by AICc is not the best bandwidth for GWR, but a fixed bandwidth based on the experimental design is recommended.
+Our study uses simulation examples to demonstrate that randomisation is not essential for large strip trials.
+For the purpose of obtaining a treatment map, a systematic design is superior to a randomised design, subject to appropriate restrictions.
+We also test the power of GWR to determine if it can successfully estimate spatially varying treatment effects for both linear and quadratic responses.
+Our results show that the optimal bandwidth found by AICc is not the best for GWR.
+Instead, a fixed bandwidth based on the experimental design is recommended.
 
@@
 
-In \eqref{eq:underlying}, the structure of the covariance matrix $V_u(\theta_u)$ of $\bm{u}_i$ can be either diagonal, which means the treatments at grid $i$ are independent, or in general form, which means a correlation exists.
-\textcite{McElreath2015Statistical} suggest that the covariance of $\bm{u}_i$ can be $V_u = B(\sigma_u)R_uB(\sigma_u)$, where $B(\sigma_u)$ denotes the diagonal matrix of elements $\sigma_{u_j}$, $j=1,\ldots,k$, and $R_u \sim \mbox{LKJ}(\epsilon)$ is a correlation matrix controlled by a positive parameter $\epsilon$.
+In model \eqref{eq:underlying}, the structure of the covariance matrix $V_u(\theta_u)$ of $\bm{u}_i$ can be either diagonal, which implies the treatments at grid $i$ are independent, or in general form, which means a correlation exists.
+\textcite{McElreath2015Statistical} suggest that the covariance of $\bm{u}_i$ can be $V_u = B(\sigma_u)R_uB(\sigma_u)$, where $B(\sigma_u)$ denotes the diagonal matrix of elements $\sigma_{u_j}$, $j=1,\ldots,k$.
+For the matrix $R_u$ with correlation coefficients, we specify the Lewandowski-Kurowicka-Joe (LKJ) distribution \parencite{Lewandowski2009Generating}, which is given by
+\begin{equation}\label{eq:RPrior}
+    R_u \sim \text{LKJcorr}(\epsilon),
+\end{equation}
+where $\text{LKJcorr}(\epsilon)$ is a positive definite correlation matrix sampled from the LKJ distribution controlled by a positive parameter $\epsilon$.
 As $\epsilon$ increases, a high correlation among parameters becomes less likely.
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/RandNitro.pdf}
-		\caption{Treatments are randomly allocated into large strips.}
+		\includegraphics[width=\linewidth]{Expt/Col_RandNitro.pdf}
+		\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/SystNitro.pdf}
-		\caption{Treatments are systematically allocated into large strips.}
+		\includegraphics[width=\linewidth]{Expt/Col_SystNitro.pdf}
+		\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
 	\end{subfigure}
-	\caption{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (a) and systematically (b) allocated into strips.}\label{fig:Nitrogen}
+	\caption{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly \eqref{fig:RandNitrogen} and systematically \eqref{fig:SystNitrogen} allocated into strips in each replicate block.}\label{fig:Nitrogen}
 \end{figure}
@@
 For a linear relationship, we assume that the true global intercept is $b_0 = 65$ and the slope is $b_1=0.05$.
-The parameters are chosen according to the estimates by \textcite{Rakshit2020Novel} on the Las Rosas corn field data from the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
+The parameters are chosen according to the estimates by \textcite{Rakshit2020Novel, Cao2022Bayesian} on the Las Rosas corn field data, which is initially provided by \textcite{Luc2004ASpatial} and embedded in the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
+The unit of yield is quintals per hectare.
 The variances of $\bm{u}_i$ are $\sigma_{u_0} = 5$ and $\sigma_{u_1}=0.01$.
 For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters for column and row are $\rho_c = 0.15$ and $\rho_r=0.5$.
-We have assumed a higher correlation in the rows due to the fact that the crop are traditionally sown and harvested along ranges where the correlation is higher in perpendicular to the travel direction \parencite{Marchant2019Establishinga}.
+We have assumed a higher correlation in the rows due to the fact that the crop is traditionally sown and harvested along ranges where the correlation is higher in perpendicular to the travel direction \parencite{Marchant2019Establishinga}.
 For the \Matern covariance matrix \eqref{eq:matcov}, we set $\sigma_d^2=1$, $r=1$ and $\nu = \frac{3}{2}$.
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/LinCombMSE_newpar.pdf}
-	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
+	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
 The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation between the parameters ($\epsilon=1$).}\label{fig:LinBetaMSE}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/QuaCombMSE_newpar.pdf}
-	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
+	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
 The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation amongst the parameters ($\epsilon=1$).} \label{fig:QuadBetaMSE}
@@
 
-SAGI West gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
+CBADA (Curtin Biometry and Data Analytic) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/LinCombMSE_newpar_eta01.pdf}
-	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
+	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_eta01.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
 The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation between the parameters ($\epsilon=0.1$).}\label{fig:LinBetaMSEeta01}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/QuaCombMSE_newpar_eta01.pdf}
-	\caption{Boxplots of $\ln$(MSE) for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
+	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_eta01.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
 The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation amongst the parameters ($\epsilon=0.1$).} \label{fig:QuadBetaMSEeta01}

### 2023-07-26 main.tex
updated figures

@@
 \author[1]{Mark Gibberd}
-\author[1,3]{Julia Easton}
+\author[1]{Julia Easton}
 \author[1,2]{Suman Rakshit}
 
-\affil[1]{Curtin Biometry and Data Analytic, Centre for Crop and Disease Management, Curtin University, Perth, Australia}
+\affil[1]{Curtin Biometry and Agricultural Data Analytics, Centre for Crop and Disease Management, Curtin University, Perth, Australia}
 \affil[2]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}
-\affil[3]{Curtin 4 Agribusiness Profitability Initiative, Centre for Crop and Disease Management, Curtin University, Perth, Australia}
 
@@
 \linenumbers
-%\doublespacing
-\onehalfspacing
+\doublespacing
+%\onehalfspacing
 
@@
 The principles of randomisation were first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
-The most straightforward, least restrictive experimental design is the completely randomised design (CRD).
-More complex designs, such as randomised complete block design (RCBD), split-plot design, strip-plot design and Latin square design, are also widely used in agricultural experiments \parencite{Petersen1994Agricultural}.
-Following these principles, randomised designs are routinely used from small on-site trials to large on-farm experiments (OFE), while systematic designs are rarely used.
+Traditionally, small-plot trials for agriculture are designed to accentuate treatment effects with the completely randomised design (CRD) as the most straight forward, least restrictive experimental design.
+More complex designs, such as a randomised complete block design (RCBD), a split-plot design, a strip-plot design and a Latin square design, are also widely used in agricultural experiments \parencite{Petersen1994Agricultural}.
+Following these principles, randomised designs are routinely used for on-farm strip trials, while systematic designs are rarely used.
 
@@
 While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of on-farm experiments (OFE) shifts from the conventional analysis.
-In the application of precision agriculture (PA), a prescription map from the experimental results is required by the variable-rate applicators (VRA) prior to the start of the operation \parencite{Pringle2004FieldScale}.
+In the application of precision agriculture (PA), the variable rate applicators (VRA) require a prescription map of the experiment before the start of the operation \parencite{Pringle2004FieldScale}.
 Therefore, in this scenario, the goal of OFE becomes obtaining a smooth map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
-For this objective, \textcite{Piepho2011Statistical} stresses that only a single level of the treatments can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
-If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary across the field.
+For this objective, \textcite{Piepho2011Statistical} stresses that only a single level of treatments can be directly observed at any one point on the grid and the response for other levels at the same grid must be interpolated.
+If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary throughout the field.
 Such heterogeneous distances increase the uncertainty in the analysis and reduce the efficiency of local prediction.
@@
 
-Analyzing a systematic design for the creation of an optimal treatment map for on-farm experiments (OFE) is statistically challenging.
-The truly localized estimation at each point on the grid is unknown, and the optimum treatment response varies continuously across the field.
+Analysing a systematic design for the creation of an optimal treatment map for on-farm experiments (OFE) is a statistically challenging task.
+The truly localised estimation at each point on the grid is unknown, and the optimum treatment response varies continuously across the field.
 \textcite{Cao2022Bayesian} implemented a Bayesian approach using spatially correlated random parameters for large systematic OFE strip trials, assuming a quadratic response model with both global and local spatially varying components.
@@
 Alternatively, \textcite{Rakshit2020Novel} adopt a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE.
-Additionally, \textcite{Evans2020Assessment} conclude through simulation studies that GWR is a simple method for the analysis of OFE data and is able to accurately separate yield variation that is not due to the applied treatment from yield response due to treatment.
-However, their study was limited by the use of a randomised design and the assumption of a linear response to fertilizer treatment.
-\textcite{Alesso2021Design} simulated corn yield with four levels of nitrogen assigned systematically and randomly into chessboard designs and fitted the true coefficients using GWR.
+Additionally, \textcite{Evans2020Assessment} conclude through simulation studies that GWR is a simple method for OFE data analysis and is capable of accurately separating yield variation that is not due to applied treatment from yield response due to treatment.
+However, their study was limited by the use of a randomised design and the assumption of a linear response to fertiliser treatment.
+\textcite{Alesso2021Design} simulated corn yield with four nitrogen levels assigned systematically and randomly in the chessboard designs and fitted the true coefficients using GWR.
 They concluded that systematic designs achieved the best results in most cases.
 However, in these simulation studies, the use of chessboard design presents a problem: harvesters can smooth over abrupt treatment changes between plots, potentially leading to misleading results unless there are constraints on the field \parencite{Pringle2004FieldScale}.
-Additionally, the quadratic or plateau feature was not considered as a factor in the simulations.
+Additionally, the quadratic or plateau feature was not considered a factor in the simulations.
 
@@
 
-\textcite{Piepho2018Tutorial} demonstrate an example that a linear model is lack fitting on the sugar beets data \parencite{Petersen1994Agricultural}.
+\textcite{Piepho2018Tutorial} demonstrate an example that a linear model is lacking in fitting to the sugar beet data \parencite{Petersen1994Agricultural}.
 \textcite{Glynn2007} show that many curves exist beyond a linear trend for nutrient-response relationships.
 The curve depends on the current availability of other macro and micronutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial.
-For this reason, it is important to consider models with degrees higher than 1, with a quadratic model found to be adequate relationships (\textcite{Piepho2018Tutorial, Liben2019}).
+For this reason, it is important to consider models with degrees higher than 1, which means a quadratic model was found to be suitable for relationships \parencite{Piepho2018Tutorial, Liben2019}.
 %However, when modelling this process it is still common to see linear approximations made \parencite{}. 
@@
 
-The structure of the paper is organised as follows: in Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and the GWR model for fitting OFE data.
+The structure of the paper is organised as follows: In Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and the GWR model to fit OFE data.
 In Section \ref{Sec:Simu}, we generate simulated data for the combination of the following scenarios: randomised and systematic designs; linear and quadratic response; low and high coefficient correlations; spatial variation among grids is identity (no spatial trend), $\AR\otimes\AR$ and \Matern form.
@@
 This section describes the statistical model used in the simulation study.
-It outlines the basic model (subsection \ref{sec:basic}) followed by the methodology for the spatially correlated treatment parameters (subsection \ref{sec:spatial}), and finally GWR (subsection \ref{sec:gwr}).
+It outlines the basic model (Subsection \ref{sec:basic}) followed by the methodology for the spatially correlated treatment parameters (Subsection \ref{sec:spatial}), and finally GWR (Subsection \ref{sec:gwr}).
 
@@
 
-In a conventional agricultural study, a field experiment can be considered as a rectangular array, consisting of $r$ rows and $c$ columns, where the total number of the plots in the experiment is $n=r\times c$.
+In a conventional agricultural study, a field experiment can be considered as a rectangular matrix consisting of $r$ rows and $c$ columns, where the total number of plots in the experiment is $n=r\times c$.
 The notation $s_i\in \mathcal{R}^2, i=1,\ldots,n$ is a two-cell vector of the Cartesian coordination of the plot centroids, located on a regular grid \parencite{Zimmerman1991Randoma}.
@@
 \textcite{Cao2022Bayesian} implemented the Bayesian hierarchical model with spatially correlated random parameters on large OFE strip trials.
-Here, for the simulation study, we use the same model to generate the simulated data.
+Here, for the simulation study, we use the same model to generate the synthetic data.
 
@@
 \end{equation}
-where AR1 is the separable first-order autoregressive model in the column and row direction which is controlled by the correlation parameters $\rho_c$ and $\rho_r$, respectively \parencite{Butler2017ASRemlR}.
+where AR1 is the separable first-order auto-regressive model in the column and row direction which is controlled by the correlation parameters $\rho_c$ and $\rho_r$, respectively \parencite{Butler2017ASRemlR}.
 
@@
 
-Model \eqref{eq:underlying} has the advantage of reproducibility in simulation study and robustness in estimation.
+Model \eqref{eq:underlying} has the advantage of reproducibility in the simulation study and robustness in estimation.
 It is possible even though only a single treatment is directly observed at each plot, and the responses of the other levels need to be estimated by interpolation because the spatial model allows using information from neighbouring plots with other treatments \parencite{Panten2010Enhancing, Piepho2011Statistical}.
@@
 with a given kernel function $K(\cdot,\cdot)$, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}.
-In the simulation study, we use Gaussian kernel.
-In fact, kernel is not a crucial factor in GWR model fitting on OFE data.
-By contrast, the factor bandwidth has higher influence on the estimation.
+In the simulation study, we use a Gaussian kernel.
+In fact, the kernel is not the crucial factor in the GWR model fitting on OFE data.
+By contrast, the factor bandwidth has a higher influence on the estimation.
 
@@
 
-We investigate the combination of the following factors: types of designs with two levels: randomised and systematic; response relationship with two levels: linear and quadratic; correlation of coefficients with two levels: low and high; spatial variation with three levels: identity (no spatial trend), $\AR\otimes\AR$ and \Matern form; bandwidth of GWR with three levels: 5, 9 and optimum given by AICc.
+We investigate the combination of the following factors: types of design with two levels: randomised and systematic; response relationship with two levels: linear and quadratic; correlation of coefficients with two levels: low and high; spatial variation with three levels: identity (no spatial trend), $\AR\otimes\AR$ and \Matern form; GWR bandwidth with three levels: 5, 9 and optimum given by AICc.
 The fixed bandwidth 5 in the simulation study covers all treatment levels (five nitrogen levels) in a systematic design, where the information is adequate in the inference of a quadratic curve.
@@
 
-With model \eqref{eq:underlying}, we generate the yield as a response to the nitrogen treatment in two scenarios which cover whether the yield has a linear or quadratic relationship with nitrogen rate.
+With model \eqref{eq:underlying}, we generate the yield as a response to nitrogen treatment in two scenarios that cover whether the yield has a linear or quadratic relationship with the nitrogen rate.
 The nitrogen rates are treated as continuous observations with five levels: 0, 35, 75, 105 and 140 kg/ha.
-A strip plot structure was used to allocate the five nitrogen levels where each level is assigned to one strip.
+A strip plot structure was used to allocate the five nitrogen levels, where each level is assigned to one strip.
 Then we assume that the experimental design of the trial consists of four replicates, each containing 5 ranges (columns) by 93 rows.
-The nitrogen rates are allocated either randomly or systematically on the whole field.
+The nitrogen rates are allocated randomly or systematically in the whole field.
 The overall layout of the trial is 20 ranges by 93 rows.
@@
 For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters for column and row are $\rho_c = 0.15$ and $\rho_r=0.5$.
-We have assumed a higher correlation in the rows due to the fact that the crop is traditionally sown and harvested along ranges where the correlation is higher in perpendicular to the travel direction \parencite{Marchant2019Establishinga}.
+We have assumed a higher correlation in the rows due to the fact that the crop is traditionally sown and harvested along ranges where the correlation is higher in the perpendicular direction than the travel direction \parencite{Marchant2019Establishinga}.
 For the \Matern covariance matrix \eqref{eq:matcov}, we set $\sigma_d^2=1$, $r=1$ and $\nu = \frac{3}{2}$.
@@
 We keep $\sigma_{u_0} = 5$, $\sigma_{u_1}=0.01$ and add $\sigma_{u_2}=0.0001$ because the true values are small.
-The remaining parameters stay unchanged.
+The rest of the parameters remain unchanged.
 Therefore, the true spatially varying coefficients are $\bm{\beta}_0 = b_0 + \bm{u}_0$, $\bm{\beta}_1 = b_1 + \bm{u}_1$ and $\bm{\beta}_2 = b_2 + \bm{u}_2$.
@@
 
-\begin{figure}[H]
+\begin{figure}[!htp]
 	\begin{subfigure}[t]{0.45\textwidth}
@@
 		\includegraphics[width=\linewidth]{Expt/LinlinesV2.pdf}
-		\caption{Linear relationship of yield to nitrogen level.}
+		\caption{Linear relationship between crop yield and nitrogen levels, where $y=65+0.05x$.}
 	\end{subfigure}
@@
 		\includegraphics[width=\linewidth]{Expt/QualinesV2.pdf}
-		\caption{Quadratic relationship of yield to nitrogen level.}
+		\caption{Quadratic relationship between crop yield and nitrogen levels, where $y=65+0.05x-0.003x^2$.}
 	\end{subfigure}
-	\caption{Noise-free linear and quadratic response to fertiliser treatment.}\label{fig:Lines}
+	\caption{Noise-free linear and quadratic relationships between crop yield and nitrogen levels.}\label{fig:Lines}
 \end{figure}
@@
 
-By running the simulation 100 times, we assessed the performance of the randomised and systematic designs for linear and quadratic responses.
+Running the simulation 100 times, we assessed the performance of the randomised and systematic designs for linear and quadratic responses.
 In subsection \ref{Sec:MSE} the mean squared errors are compared between the two designs for different bandwidths, parameter correlations and spatial covariance matrices.
@@
 
-We assessed the true mean squared error (MSE) of estimated coefficient differences.
+We evaluated the true mean squared error (MSE) of the estimated coefficient differences.
 This was calculated by the difference of true coefficients, $\bm{\beta} = b + \bm{u}$, and estimated spatially varying coefficients, $\bm{\hat{\beta}} = \hat{b}+\bm{\hat{u}}$, for each grid, and then squared the discrepancy and averaged across the field for comparison.
 The results are shown in Figures \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE} where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$), ``AR1'' is for $\AR(0.15)\otimes \AR(0.5)$ and ``Matern'' is the \Matern covariance with $\nu=\frac{3}{2}$.
-Since the MSE of $\beta_0$, $\beta_1$ and $\beta_2$ are small, we take the natural logarithm for better visualisation.
+Since the MSEs of $\beta_0$, $\beta_1$, and $\beta_2$ are small, we take the natural logarithm for better visualisation.
 
 % Paragraph about Figure 3 and the performance for a linear response
-With the assumption of a linear response, both randomised and systematic designs performed similarly, meaning GWR is able to partition the local varying intercept and treatment coefficient.
-Figure \ref{fig:LinBetaMSE} shows that if the response is linear, the MSE of $\hat{\beta}_0$ and $\hat{\beta}_1$ estimated by GWR
+With the assumption of a linear response, both randomised and systematic designs perform similarly, meaning GWR is able to partition the local varying intercept and treatment coefficient.
+Figure \ref{fig:LinBetaMSE} shows that if the response is linear, the MSEs of $\hat{\beta}_0$ and $\hat{\beta}_1$ estimated by GWR, for all bandwidths,
 %with bandwidth 5, 9 and the optimal bandwidth found by AICc
-, for all bandwidths,
 is not distinguishing between randomised and systematic designs.
 This is true regardless of the type of spatial covariance matrix when the correlation within grids is small ($\epsilon=1$), or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
-The GWR with bandwidth selected by AICc had a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).
+The GWR with bandwidth selected by AICc has a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).
 
-\begin{figure}[H]
+\begin{figure}[!htp]
 	\centering
@@
 % Paragraph about Figure 4 and the performance for a linear response
-However, if the assumption is a quadratic response, Figure \ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show that the GWR with a fixed bandwidth of a systematic design outperforms a randomised design if the spatial correlation is taken into account.
-With the optimal bandwidth, GWR successfully estimates the global intercepts $\beta_0$, but failed in estimating local varying coefficients $\beta_1$ and $\beta_2$, where the MSE is relatively larger than with fixed bandwidth.
-However, if we only compare across two types of designs, it still proves that GWR is robust to fit a systematic design rather than a randomised design if the assumption is quadratic response, regardless the intensity of the correlation within grids.
+However, if the assumption is a quadratic response, Figures \ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show that the GWR with a fixed bandwidth of a systematic design outperforms a randomised design if the spatial correlation is taken into account.
+With the optimal bandwidth, GWR successfully estimates the global intercepts $\beta_0$ but failed in estimating local varying coefficients $\beta_1$ and $\beta_2$, where the MSE is relatively larger than with fixed bandwidth.
+However, if we only compare across two types of designs, it still proves that GWR is robust to fit a systematic design rather than a randomised design if the assumption is a quadratic response, regardless of the intensity of the correlation within grids.
 
-\begin{figure}[H]
+\begin{figure}[!thp]
 	\centering
@@
 
-The relative MSE for each bandwidth was found to change according to the spatial covariance matrix as well as the coefficient.
-When no spatial variation was simulated for $\beta_1$ and $\beta_2$, the bandwidth selected by AICc had the lowest MSE, followed by the bandwidths 9 and then 5.
-When there was spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ had the lowest MSE when using bandwidth 9, followed by 5 and then bandwidth from AICc.
-The intercept ($\beta_0$) showed only significant changes in MSE amongst the bandwidths when the \Matern spatial covariance was considered.
-In this case, the bandwidth selected by AICc produced the smallest MSE.
+%%The relative MSE for each bandwidth was found to change according to the spatial covariance matrix as well as the coefficient.
+When no spatial variation was simulated for $\beta_1$ and $\beta_2$, the AICc-selected bandwidth has the lowest MSE, followed by the fixed bandwidths of 9 and then 5.
+When there is spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ has the lowest MSEs when using bandwidth 9, followed by 5 and then bandwidth from AICc.
+The intercept ($\beta_0$) shows only significant changes in MSE amongst the bandwidths when the \Matern spatial covariance was considered.
+In this case, the bandwidth selected by AICc produces the smallest MSE.
 
-Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} are the median MSE of linear response for two scenarios: correlation is low and correlation is high.
+MSE analyses revealed that the choice of bandwidth significantly influenced the relative performance based on both the spatial covariance matrix and the coefficient characteristics.
+In scenarios without spatial variation for $\beta_1$ and $\beta_2$, the AICc-selected bandwidth demonstrated the lowest MSE, followed by fixed bandwidths of 9 and 5, respectively.
+However, when the spatial variation was present (utilising either AR1$\otimes$AR1 or \Matern covariance structures), the bandwidth of 9 consistently produced the most accurate estimations for $\beta_1$ and $\beta_2$, outperforming the bandwidths of 5 and the one chosen by AICc.
+Notably, for the intercept ($\beta_0$), significant changes in MSE amongst the bandwidths were observed only in the context of the \Matern spatial covariance.
+Here, the bandwidth selected by AICc resulted in the smallest MSE, highlighting its efficacy when dealing with spatially correlated residuals following the \Matern covariance structure.
 
-\begin{table}[H]
+Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} are the median MSEs of the linear response for two scenarios: the correlation is low and the correlation is high.
+
+\begin{table}[!htp]
 	\centering
@@
 
-\begin{table}[H]
+\begin{table}[!htp]
 	\centering
@@
 
-\vspace{12pt}
+% \vspace{12pt}
 
-Tables \ref{tb:MSEquadratic} and \ref{tb:MSEquadraticHigh} are the median MSE of quadratic response for two scenarios: correlation is low and correlation is high.
-Despite the correlation intensity, the data fitted by GWR from systematical designs are superior to randomised designs, having a smaller MSE.
+Tables \ref{tb:MSEquadratic} and \ref{tb:MSEquadraticHigh} are the median MSE of the quadratic response for two scenarios: correlation is low and correlation is high.
+Despite the intensity of the correlation, the data fitted by GWR from systematic designs are superior to randomised designs, in terms of having a lower MSE.
 
-\begin{table}[H]
+\begin{table}[!htp]
 	\centering
@@
 The analyses were performed for two scenarios of different responses separately.
-For each response, the coefficients were also accounted for in the model.
-The objective of the analysis was to investigate the five main factors: two types of design, three bandwidths, three covariance matrices, coefficients $\bm{\beta}$ and the correlation $\epsilon$.
-The significance patterns of the second-order interactions was also of interest.
+For each response, the coefficients were also taken into account in the model.
+The objective of the analysis was to investigate the five main factors: two types of design, three bandwidths, three covariance matrices, coefficients $\bm{\beta}$ and correlation $\epsilon$.
+The significance patterns of the second-order interactions were also of interest.
 The results are listed in Table \ref{tb:LMMoutput}.
 
-The results are consistent with what was observed in the subsection above in that, for the linear response, the difference between randomised and systematic designs was not significant.
-However, for the quadratic response, the design and its interactions with bandwidth and the coefficients were significant.
-For both scenarios, the correlation intensity and all of its interactions were not significant (Table \ref{tb:LMMoutput}).
-Hence, GWR performs similarly with either a low or high correlation between coefficients.
-Also of note was that the Bandwidth, and its second-order interactions with the variables other than the correlation, was found to be significant for both response types.
+The results are consistent with what was observed in the previous subsection that, for the linear response, the difference between the randomised and systematic designs was not significant.
+However, for the quadratic response, the design and its interactions with the bandwidth and the coefficients were significant.
+For both scenarios, the intensity of the correlation and all its interactions were not significant (Table \ref{tb:LMMoutput}).
+Therefore, the GWR performs similarly with a low or high correlation between coefficients.
+Also of note was that bandwidth and its second-order interactions with variables other than correlation were found to be significant for both response types.
 
-\begin{table}[H]
+\begin{table}[!htp]
 	\centering
@@
 Agronomists and biometricians generally prefer randomised designs for OFE trials.
-According to the performance metrics used, our simulation study shows a systematic design performed either preferably or similarly to a randomised design for the purposes of creating a varying treatment map.
+According to the performance metrics used, our simulation study shows a systematic design performs either preferably or similarly to a randomised design for the purposes of creating a varying treatment map.
 The differentiating factors included primarily the response type and the spatial covariance model, while the correlation amongst the treatment coefficients was not found to be important.
@@
 The response type was the main differentiating factor between randomised and systematic designs.
-When the response was quadratic, the systematic design performed favourably which contrasted the result for the linear design which saw low differentiation between the designs.
+When the response was quadratic, the systematic design performed favourably, which contrasted the result for the linear design.
 Given this, if a farmer expects an approximately linear response in the field, then the selection of the design may not be important.
-However, given the variable nature of the relationship between response and treatment over a large field (see i.e \textcite{Rakshit2020Novel}), it may be wise to implement a systematic design for the potential outcome of a quadratic relationship.
+However, given the variable nature of the relationship between response and treatment over a large field (see \textcite{Rakshit2020Novel}), it may be wise to implement a systematic design for the potential outcome of a quadratic relationship.
 %For other more complex response types (i.e polynomials of order greater than 2) it is predicted that a systematic design will also perform favourably. \textcolor{red}{?ref}
@@
 When no spatial structure was simulated, the differences between the prediction from the systematic and random design were minimal.
-This result should be expected given if there are no spatial autocorrelations, then the individual query grids are independent observations and therefore the design is not important.
-However, when a first-order autoregressive structure was simulated the differences were noticeable when a quadratic response was used, showing systematic designs to be preferential.
-The largest difference between the two designs came when considering the \Matern spatial covariance structure, which showed a clear preference for systematic designs when a quadratic response was considered, and also a small preference for systematic designs for a linear response.
+This result should be expected given that if there are no spatial autocorrelations, then the individual query grids are independent observations, and therefore the design is not important.
+However, when a first-order auto-regressive structure was simulated, the differences were noticeable when a quadratic response was used, showing systematic designs to be preferential.
+The largest difference between the two designs occurred when considering the \Matern spatial covariance structure, which showed a clear preference for systematic designs when a quadratic response was considered, and also a small preference for systematic designs for a linear response.
 Therefore, only if spatial variability was predicted to be negligible in the field would using a randomised design be reasonable given a quadratic response.
-This assumption of negligible spatial variability would be tough to reason with given the large fields used in on-farm experimentation (add reference), meaning that in the application a systematic design should be used.
+This assumption of negligible spatial variability would be difficult to reason with given the large fields used in on-farm experimentation (add reference), meaning that in the application a systematic design should be used.
 
@@
 %3. Bandwidth selection and why that is important [good]
-There was found to be significant deficiencies in using AICc for bandwidth selection.
+There were found to be significant deficiencies in using AICc for bandwidth selection.
 The AICc-minimising bandwidths skewed to 1 and, in a few cases, ended in 93 (number of rows).
@@
 Given the scope of the paper, some designs and factors were not considered.
-Designs such as chequerboard or wave designs have been suggested for on-farm experiments \parencite{bramley1999designing}, however, were not able to be considered here.
+Designs such as chequerboard or wave designs have been suggested for on-farm experiments \parencite{bramley1999designing}, however, were not considered here.
 Topographical factors (spatial zones) were also not entertained in our study.
@@
 With the purpose of creating a varying treatment map, our simulation study proves that a systematic design produces better performance metrics, under particular circumstances, than a randomised design for large on-farm trials in terms of robustness and smaller MSE on coefficients.
-On the other hand, if the spatial variation is not considered, or if researchers believe in linear response, either a systematic or a randomised design could be implemented because the difference is not significant.
-We recommend that, for a large OFE trial with the goal to create a varying treatment map, a systemic design should be used as it has more flexibility in post-experiment statistical modelling.
+On the other hand, if spatial variation is not considered or if researchers believe in linear response, a systematic or a randomised design could be implemented because the difference is not significant.
+We recommend that, for a large OFE strip trial with the goal to create a varying treatment map, a systemic design should be used as it has more flexibility in post-experiment statistical modelling.
 

### 2023-07-27 main.tex

@@
 
-CBADA (Curtin Biometry and Data Analytic) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
+Curtin Biometry and Data Analytics (CBADA) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
 
@@
 
-\begin{figure}[!htp]
+\begin{figure}[H]
 	\centering

### 2024-02-08 mainV2_mark.tex
revised abstract and re-submit

--- 2023-07-27 main.tex
@@
 
-\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100]{biblatex}
+\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100, uniquename=init]{biblatex}
+%backend=bibtex
 \DeclareNameAlias{sortname}{family-given}
@@
 \author[1]{Jordan Brown}
-\author[1,2]{Andrew Grose}
+% \author[1,2]{Andrew Grose}
 \author[1]{Mark Gibberd}
@@
 
-\begin{abstract}
-% There is no doubt on the importance of randomisation in agricultural experiments by agronomists and biometricians.
-Even when agronomists extend the experimentation from small trials to large on-farm trials, randomised designs predominate over systematic designs.
-However, the situation may change depending on the objective of the on-farm experiments (OFE).
-If the goal of OFE is obtaining a smooth map showing the optimal level of a controllable input across a grid made by rows and columns covering the whole field, a systematic design should be preferred over a randomised design in terms of robustness and reliability.
-With the novel geographically weighted regression (GWR) for OFE and simulation studies, we conclude that, for large OFE strip trials, the difference between randomised designs and systematic designs is not significant if a linear model of treatments is fitted or if the spatial variation is not taken into account.
-But for a quadratic model, systematic designs are superior to randomised designs.
-Randomisation is a crucial aspect of agricultural experiments for both agronomists and biometricians.
+% \begin{abstract}
+% Randomisation is a crucial aspect for the estimation of unbiased treatment effects in agricultural experiments.
 While randomised designs are predominantly used for small trials and large on-farm experiments (OFE), the choice between randomised and systematic designs may depend on the objective of the OFE.
@@
 However, for quadratic models, particularly with the presence of spatial variation, systematic designs are superior to randomised designs in terms of smaller true mean squared errors (MSE) of coefficients.
+% \end{abstract}
+
+% Field Crops Research has recently altered the format of the Abstract to make it more readable.
+I request that you revise the Abstract of your manuscript using the following headings and guidelines and resubmit your manuscript:
+
+% A concise and factual abstract of no more than 400 words is required.
+It should report concisely the main findings of the research.
+To this end, the abstract is structured in five parts: 1.
+CONTEXT OR PROBLEM to present the background and issues; 2.
+OBJECTIVE OR RESEARCH QUESTION where the main hypothesis is presented; 3.
+METHODS to provide an overview of the materials and methods used; 4.
+RESULTS to present the main results using quantitative facts where possible; 5 CONCLUSIONS to present the main interpretation of the results; 6.
+IMPLICATIONS OR SIGNIFICANCE highlights the novelty of the results and their implications for field crops research and practice.
+An abstract is often presented separately from the article, so it must be able to stand alone.
+For this reason, references are not allowed.
+Also, non-standard or uncommon abbreviations should be avoided, but if essential they must be defined at their first mention in the Abstract.
+The headings must be used in the Abstract.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%% reviewers %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Matthew J. Pringle,  matthew.pringle@qld.gov.au
+%% Department of Environment and Science, GPO Box 2454, Brisbane, QLD 4001, Australia
+%% OFE trial, experimental design for OFE
+
+%% Prof. Dr. Hans-Peter Piepho, piepho@uni-hohenheim.de
+%% Biostatistics (340c) [Director], Institute of Crop Science (340) [Managing director]
+%% University of Hohenheim
+%% OFE trial and model
+
+%% Dr. Fiona Evans,  fiona@daa.com.au
+%% https://www.daa.com.au/our-people/fiona-evans
+%% GWR, simulation
+
+%% Maria Lie Selle, maria.selle@ntnu.no
+%% Department of Mathematical Sciences, Norwegian University of Science and Technology (NTNU), Trondheim, Norway
+%% Bayesian model
+
+%% Osval Antonio Montesinos-López, oamontes2@hotmail.com
+%% Facultad de Telemática, Univ. de Colima, Colima, Colima, 28040 México
+%% OFE trials experiments, Multivariate Bayesian Analysis of On-Farm Trials with Multiple-Trait and Multiple-Environment Data
+
+\begin{abstract}
+
+\zc{CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians.
+However, for on-farm trials, the choice may depend on the objective of the experiments.
+If the purpose is to create a prescription map of a continuous input for each plot of a grid covering a large strip trial, a systematic design may be a better choice, but it attracts less discussion and attention.
+}
+
+\zc{OBJECTIVE OR RESEARCH QUESTION: This study aims to evaluate the performance of systematic designs with geographically weighted regression (GWR) models in addressing spatial variation and estimating continuous treatment effects in large strip trials through numeric simulations.}
+
+\zc{METHODS: A Bayesian hierarchical model with spatially correlated random parameters is utilised to generate simulated data for various scenarios of large strip on-farm trials.
+The study employs GWR models to analyse the simulated data for two assumptions: a linear response and a quadratic response to the treatment effects.}
+
+\zc{RESULTS: With the assumption of linear response, the difference between a systematic design and a randomised design is not significant regardless of the presence of spatial variation.
+However, with the assumption of quadratic response, a systematic design is superior to a randomised design concerning the lower mean squared errors (MSE) by GWR.
+}
+
+\zc{CONCLUSIONS: The findings highlight the superiority of systematic designs for producing smooth maps of optimal input levels and the impact of spatial variation on the performance of quadratic models in strip trials.
+Additionally, the study recommends fixed bandwidths based on experimental designs for GWR models.
+For a large strip trial to create a varying treatment map, a systemic design should be used as it has more flexibility in post-experiment statistical modelling.}
+
+\zc{IMPLICATIONS OR SIGNIFICANCE: The findings offer practical recommendations for designing large strip trials.
+By drawing attention to the considerations, especially regarding the experiment's purpose, this research contributes valuable insights for improving the efficacy and planning of future large strip trials.}
+
 \end{abstract}
@@
 The fixed bandwidth 5 in the simulation study covers all treatment levels (five nitrogen levels) in a systematic design, where the information is adequate in the inference of a quadratic curve.
-Similarly, the fixed bandwidth 9 covers all possible treatment levels in a randomised design.
-This is because if all treatments are randomly allocated in the strips, there is a chance that the information of one treatment level is missing if the bandwidth is less than 9.
+Similarly, a fixed bandwidth of 9 is essential to cover all possible treatment levels in a randomised design.
+This necessity stems from situations where treatments are randomly distributed across strips.
+In particular, if identical treatments are positioned at the far left edge of the first replicate block and the far right edge of the second replicate block, a bandwidth smaller than 9 would lead to the GWR model capturing only the treatments between these boundaries, thereby missing the treatment level at the extremes.
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_RandNitro.pdf}
+		\includegraphics[width=\linewidth]{Col_RandNitro.pdf}
 		\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_SystNitro.pdf}
+		\includegraphics[width=\linewidth]{Col_SystNitro.pdf}
 		\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/LinlinesV2.pdf}
+		\includegraphics[width=\linewidth]{LinlinesV2.pdf}
 		\caption{Linear relationship between crop yield and nitrogen levels, where $y=65+0.05x$.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/QualinesV2.pdf}
+		\includegraphics[width=\linewidth]{QualinesV2.pdf}
 		\caption{Quadratic relationship between crop yield and nitrogen levels, where $y=65+0.05x-0.003x^2$.}
@@
 % 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/LinearRandYield01.pdf}
+% 		\includegraphics[width=\linewidth]{LinearRandYield01.pdf}
 % 		\caption{Yield map of the linear response of the randomised design. }
@@
 % 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/LinearSystYield01.pdf}
+% 		\includegraphics[width=\linewidth]{LinearSystYield01.pdf}
 % 		\caption{Yield map of the linear response of the systematic design. }
@@
 % 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/QuadRandYield01.pdf}
+% 		\includegraphics[width=\linewidth]{QuadRandYield01.pdf}
 % 		\caption{Yield map of the quadratic response of the randomised design. }
@@
 % 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/QuadSystYield01.pdf}
+% 		\includegraphics[width=\linewidth]{QuadSystYield01.pdf}
 % 		\caption{Yield map of the quadratic response of the systematic design. }
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar.pdf}
+	\includegraphics[width=\linewidth]{Col_LinCombMSE_newpar.pdf}
 	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar.pdf}
+	\includegraphics[width=\linewidth]{Col_QuaCombMSE_newpar.pdf}
 	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
@@
 
-\subsection{AICc Bandwidth selection}\label{Sec:bandselect}
+\subsection{AICc bandwidth selection}\label{Sec:bandselect}
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/BandwidthLinear.pdf}
+		\includegraphics[width=\linewidth]{BandwidthLinear.pdf}
 		\caption{Histogram of optimal bandwidth for linear response.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/BandwidthQuadra.pdf}
+		\includegraphics[width=\linewidth]{BandwidthQuadra.pdf}
 		\caption{Histogram of optimal bandwidth for quadratic response.}
@@
 
-\section{Acknowledgements}
+\section*{Acknowledgements}
 
 Curtin Biometry and Data Analytics (CBADA) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
+
+\section*{CRediT authorship contribution statement}
+
+\textbf{Zhanglong Cao}: Conceptualization; Formal analysis; Methodology; Software; Validation; Visualization; Roles/ Writing - original draft; and Writing - review \& editing.
+\textbf{Jordan Brown}: Investigation; Methodology; Visualization; Roles/Writing - original draft; and Writing - review \& editing.
+\textbf{Mark Gibberd}: Project administration; Roles/Writing - original draft; and Writing - review \& editing.
+\textbf{Julia Easton}: Roles/Writing - original draft; and Writing - review \& editing.
+\textbf{Suman Rakshit}: Conceptualization; Methodology; Supervision; Roles/Writing - original draft; and Writing - review \& editing.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_eta01.pdf}
+	\includegraphics[width=\linewidth]{Col_LinCombMSE_newpar_eta01.pdf}
 	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_eta01.pdf}
+	\includegraphics[width=\linewidth]{Col_QuaCombMSE_newpar_eta01.pdf}
 	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.

### 2024-07-18 main_revision_col.tex
revision V3, suman

--- 2023-07-27 main.tex
@@
 \usepackage[flushleft]{threeparttable} % For adding footnotes to tables
+\usepackage[normalem]{ulem}
+\usepackage{soul}
 
@@
 
-\newcommand{\zc}[1]{\textcolor{red}{#1}}
-
 \newcommand{\BigO}[1]{{\rm O}\left(#1\right)}
@@
 
-\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100]{biblatex}
+\newcommand{\revision}[1]{\textcolor{red}{#1}}
+\newcommand{\zc}[1]{\textcolor{blue}{#1}}
+
+\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=biber, maxcitenames=2, giveninits=true, maxbibnames=100, uniquename=init]{biblatex}
+%backend=bibtex
 \DeclareNameAlias{sortname}{family-given}
@@
 %\author{Jerome}
-\author[1]{Zhanglong Cao}
+\author[1,*]{Zhanglong Cao}
 \author[1]{Jordan Brown}
-\author[1,2]{Andrew Grose}
+% \author[1,2]{Andrew Grose}
 \author[1]{Mark Gibberd}
@@
 \affil[2]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}
+
+\affil[*]{Corresponding author: Zhanglong Cao, zhanglong.cao@curtin.edu.au}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%% reviewers %%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Matthew J. Pringle,  matthew.pringle@qld.gov.au
+%% Department of Environment and Science, GPO Box 2454, Brisbane, QLD 4001, Australia
+%% OFE trial, experimental design for OFE
+
+%% Prof. Dr. Hans-Peter Piepho, piepho@uni-hohenheim.de
+%% Biostatistics (340c) [Director], Institute of Crop Science (340) [Managing director]
+%% University of Hohenheim
+%% OFE trial and model
+
+%% Dr. Fiona Evans,  fiona@daa.com.au
+%% https://www.daa.com.au/our-people/fiona-evans
+%% GWR, simulation
+
+%% Maria Lie Selle, maria.selle@ntnu.no
+%% Department of Mathematical Sciences, Norwegian University of Science and Technology (NTNU), Trondheim, Norway
+%% Bayesian model
+
+%% Osval Antonio Montesinos-López, oamontes2@hotmail.com
+%% Facultad de Telemática, Univ. de Colima, Colima, Colima, 28040 México
+%% OFE trials experiments, Multivariate Bayesian Analysis of On-Farm Trials with Multiple-Trait and Multiple-Environment Data
+
 \begin{abstract}
-% There is no doubt on the importance of randomisation in agricultural experiments by agronomists and biometricians.
-Even when agronomists extend the experimentation from small trials to large on-farm trials, randomised designs predominate over systematic designs.
-However, the situation may change depending on the objective of the on-farm experiments (OFE).
-If the goal of OFE is obtaining a smooth map showing the optimal level of a controllable input across a grid made by rows and columns covering the whole field, a systematic design should be preferred over a randomised design in terms of robustness and reliability.
-With the novel geographically weighted regression (GWR) for OFE and simulation studies, we conclude that, for large OFE strip trials, the difference between randomised designs and systematic designs is not significant if a linear model of treatments is fitted or if the spatial variation is not taken into account.
-But for a quadratic model, systematic designs are superior to randomised designs.
-Randomisation is a crucial aspect of agricultural experiments for both agronomists and biometricians.
-While randomised designs are predominantly used for small trials and large on-farm experiments (OFE), the choice between randomised and systematic designs may depend on the objective of the OFE.
-Suppose the goal is to produce a smooth map of optimal input levels across a grid covering the entire field, in that case, a systematic design may be preferred for its robustness and reliability.
-Our simulation study using the Bayesian hierarchical model and geographically weighted regression (GWR) shows that, for large OFE strip trials, the difference between randomised and systematic designs is insignificant when fitting a linear model or ignoring spatial variation.
-However, for quadratic models, particularly with the presence of spatial variation, systematic designs are superior to randomised designs in terms of smaller true mean squared errors (MSE) of coefficients.
+CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians.
+However, for on-farm trials, the choice may depend on the objective of the experiments.
+If the purpose is to create a prescription map of a continuous input for each plot of a grid covering a large strip trial, a systematic design may be a better choice, but it attracts less discussion and attention.
+
+OBJECTIVE OR RESEARCH QUESTION: This study aims to evaluate the performance of systematic designs with geographically weighted regression (GWR) models in addressing spatial variation and estimating continuous treatment effects in large strip trials through numeric simulations.
+
+METHODS: A Bayesian hierarchical model with spatially correlated random parameters is utilised to generate simulated data for various scenarios of large strip on-farm trials.
+The study employs GWR models to analyse the simulated data for two assumptions: a linear response and a quadratic response to the treatment effects.
+
+RESULTS: With the assumption of \revision{a} quadratic response, a systematic design is superior to a randomised design \revision{in terms of achieving lower mean squared errors (MSE) with GWR}.
+However, with the assumption of \revision{a} linear response, the difference between a systematic design and a randomised design is not significant, regardless of the presence of spatial variation.
+
+CONCLUSIONS: The findings highlight the superiority of systematic designs in producing smooth \revision{spatial} maps of optimal input levels \revision{for quadratic response models in large strip trials, even when impacted by significant spatial variation.}.
+Additionally, \textcolor{red}{we recommend selecting} fixed bandwidths \revision{in GWR analysis} based on \revision{the plot configurations used in} experimental designs.
+For a large strip trial, to \revision{allocate continuously varying treatments in strips}, a systemic design should be used as it \revision{allows us to obtain accurate treatment effects} in post-experiment statistical modelling.
+
+IMPLICATIONS OR SIGNIFICANCE: The findings offer practical recommendations for designing large strip trials.
+By drawing attention to the experiment's \revision{main inferential} purpose, this research contributes valuable insights for improving the efficacy and planning of large strip trials.
 \end{abstract}
 
-{\bf Keywords:} yield map, optimal treatment, spatially varying coefficients.
+{\bf Keywords:} yield map, optimal treatment, spatially varying coefficients, \revision{geographically weighted regression}, \revision{precision agriculture}.
 
@@
 The principles of randomisation were first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
-Traditionally, small-plot trials for agriculture are designed to accentuate treatment effects with the completely randomised design (CRD) as the most straight forward, least restrictive experimental design.
-More complex designs, such as a randomised complete block design (RCBD), a split-plot design, a strip-plot design and a Latin square design, are also widely used in agricultural experiments \parencite{Petersen1994Agricultural}.
-Following these principles, randomised designs are routinely used for on-farm strip trials, while systematic designs are rarely used.
+Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design (CRD), as \revision{it is} the most straightforward \revision{and} least restrictive experimental design.
+More complex designs, such as the randomised complete block design (RCBD), the split-plot design, the strip-plot design and the Latin square design, are also widely used in agricultural experiments \revision{to improve the precision of treatment effect estimates} \parencite{Petersen1994Agricultural}.
+\revision{With the primary aim of obtaining unbiased estimates of global treatment effects}, randomised designs are routinely used for on-farm strip trials, \revision{whereas} systematic designs are rarely used.
 
@@
 
-OFE enables farmers the flexibility to implement large-scale experiments in order to test management practices on their farms \parencite{Evans2020Assessment}.
-The goal of OFE is to help farmers better understand uncertainties and leverage their existing strengths in managing translational and structural uncertainty \parencite{Cook2013Onfarm}.
-In the situation that the goal is to compare yield responses between management classes or to select individuals with the best performance as new market varieties, a randomised design is superior to a systematic design \parencite{Pringle2004FieldScale, Selle2019Flexible}.
+\revision{On-farm experiment (OFE)} enables farmers the flexibility to implement large-scale experiments in order to test management practices on their farms \parencite{Evans2020Assessment}.
+The \revision{main} goal of OFE is to help farmers better understand uncertainties \revision{around farm-related decisions} and leverage their existing strengths in managing translational and structural uncertainties \revision{in decision-making} \parencite{Cook2013Onfarm}.
+\revision{In situations where} the goal is to compare yield responses between management classes or to select \revision{best-performing crop varieties} as new market varieties, a randomised design \revision{may be} superior to a systematic design \parencite{Pringle2004FieldScale, Selle2019Flexible}.
 
 %Like conventional agricultural experiments, 
-While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of on-farm experiments (OFE) shifts from the conventional analysis.
-In the application of precision agriculture (PA), the variable rate applicators (VRA) require a prescription map of the experiment before the start of the operation \parencite{Pringle2004FieldScale}.
-Therefore, in this scenario, the goal of OFE becomes obtaining a smooth map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
-For this objective, \textcite{Piepho2011Statistical} stresses that only a single level of treatments can be directly observed at any one point on the grid and the response for other levels at the same grid must be interpolated.
+While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of OFE shifts from the conventional analysis.
+In the application of precision agriculture (PA) \revision{using} variable rate applicators (VRA) \revision{,} a prescription map of the experiment \st{before the start of the operation} \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}.
+Therefore, in this scenario, the goal of OFE becomes obtaining a smooth \revision{spatial} map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
+\revision{An important point to note here is} that only a single \revision{treatment level} can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
 If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary throughout the field.
@@
 
-Analysing a systematic design for the creation of an optimal treatment map for on-farm experiments (OFE) is a statistically challenging task.
-The truly localised estimation at each point on the grid is unknown, and the optimum treatment response varies continuously across the field.
-\textcite{Cao2022Bayesian} implemented a Bayesian approach using spatially correlated random parameters for large systematic OFE strip trials, assuming a quadratic response model with both global and local spatially varying components.
-However, the Bayesian approach is time-consuming and requires preliminary knowledge of Bayesian statistics for farmers and agronomists.
+Analysing a systematic design for the creation of an optimal treatment map for OFE is a statistically challenging task.
+\revision{The true responses} at each point on the grid \revision{corresponding to all the treatment rates are} unknown, and the treatment \revision{producing the optimum response} varies continuously across the field.
+\textcite{Cao2022Bayesian} implemented a Bayesian approach using spatially correlated random parameters for \revision{analysing} large systematic strip trials, assuming a quadratic response model with both global and local \revision{(}spatially-varying\revision{)} components.
+However, Bayesian \revision{analysis can be computationally expensive} and \revision{would require at least} preliminary knowledge of Bayesian \revision{inference to interpret the results, which can be extremely demanding} for farmers and agronomists.
 Alternatively, \textcite{Rakshit2020Novel} adopt a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE.
-Additionally, \textcite{Evans2020Assessment} conclude through simulation studies that GWR is a simple method for OFE data analysis and is capable of accurately separating yield variation that is not due to applied treatment from yield response due to treatment.
-However, their study was limited by the use of a randomised design and the assumption of a linear response to fertiliser treatment.
-\textcite{Alesso2021Design} simulated corn yield with four nitrogen levels assigned systematically and randomly in the chessboard designs and fitted the true coefficients using GWR.
+Additionally, \textcite{Evans2020Assessment} conclude through simulation studies that GWR is capable of accurately separating variation \revision{in yield response due to treatment from} \revision{the variation that} is not due to the applied treatment.
+However, their study was limited by the use of a randomised design and the assumption of a linear response \revision{model}.
+\textcite{Alesso2021Design} simulated corn yield with four nitrogen levels, assigned systematically and randomly in the chessboard designs, and \revision{estimated the regression} coefficients using GWR.
 They concluded that systematic designs achieved the best results in most cases.
-However, in these simulation studies, the use of chessboard design presents a problem: harvesters can smooth over abrupt treatment changes between plots, potentially leading to misleading results unless there are constraints on the field \parencite{Pringle2004FieldScale}.
-Additionally, the quadratic or plateau feature was not considered a factor in the simulations.
+However, the use of chessboard design presents a problem: harvesters can smooth over abrupt treatment changes between plots, potentially leading to misleading results unless there are constraints \revision{in} the field \parencite{Pringle2004FieldScale} \textcolor{green}{SR: This line does not make sense to me.
+We need to clarify}.
+Additionally, the quadratic or plateau feature \revision{in a response model} was not considered in the simulation study.
 
@@
 
-\textcite{Piepho2018Tutorial} demonstrate an example that a linear model is lacking in fitting to the sugar beet data \parencite{Petersen1994Agricultural}.
+\textcite{Piepho2018Tutorial} demonstrate an example \revision{where} a linear model \revision{turns out to be inadequate} \revision{for analysing} sugar beet data \parencite{Petersen1994Agricultural}.
 \textcite{Glynn2007} show that many curves exist beyond a linear trend for nutrient-response relationships.
-The curve depends on the current availability of other macro and micronutrients in the soil \parencite{Marschner2011}, meaning that a linear relationship is unlikely to be consistent across a large trial.
-For this reason, it is important to consider models with degrees higher than 1, which means a quadratic model was found to be suitable for relationships \parencite{Piepho2018Tutorial, Liben2019}.
+The \revision{response} curve \revision{often} depends on the availability of other macro and micronutrients in the soil \parencite{Marschner2011}, \revision{which means } that a linear relationship is unlikely to be consistent across a large trial.
+For this reason, it is important to consider models with \revision{terms of order} higher than \revision{unity}.
+\revision{For example,} a quadratic model \revision{can often} found to be suitable for \revision{modelling nutrient-response} relationships \parencite{Piepho2018Tutorial, Liben2019}.
 %However, when modelling this process it is still common to see linear approximations made \parencite{}. 
@@
 
-Our study uses simulation examples to demonstrate that randomisation is not essential for large strip trials.
-For the purpose of obtaining a treatment map, a systematic design is superior to a randomised design, subject to appropriate restrictions.
+Our study uses \revision{simulated} examples to demonstrate that randomisation is not essential for large strip trials.
+For the purpose of obtaining a treatment \revision{prescription} map, a systematic design is superior to a randomised design \revision{in most applications}.
 We also test the power of GWR to determine if it can successfully estimate spatially varying treatment effects for both linear and quadratic responses.
-Our results show that the optimal bandwidth found by AICc is not the best for GWR.
-Instead, a fixed bandwidth based on the experimental design is recommended.
+Our results show that the bandwidth \revision{selected using the popular method of corrected Akaike Information Criterion} (AICc) \revision{does not provide the optimal bandwidth} for \revision{analysing large strip trials using} GWR.
+Instead, a fixed bandwidth \revision{is recommended} based on \revision{the plot configurations used in} the experimental design.
 
-The structure of the paper is organised as follows: In Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and the GWR model to fit OFE data.
-In Section \ref{Sec:Simu}, we generate simulated data for the combination of the following scenarios: randomised and systematic designs; linear and quadratic response; low and high coefficient correlations; spatial variation among grids is identity (no spatial trend), $\AR\otimes\AR$ and \Matern form.
+The structure of the paper is organised as follows: In Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and \revision{introduce} the GWR model \revision{used in analysing} OFE data.
+In Section \ref{Sec:Simu}, we generate simulated data for \revision{several scenarios, where each scenario is constructed by choosing one component at a time from the} following \revision{four categories}: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) \revision{model coefficients with} low and high correlations; and (iv) spatial \revision{variance-covariance matrix} among grids \revision{given by} identity (no spatial trend), $\AR\otimes\AR$, and \Matern forms.
 Finally, in Sections \ref{Sec:Res} and \ref{Sec:Dis}, we illustrate the results and discuss their importance with respect to OFE, and how the findings should influence future trial designs.
@@
 
-This section describes the statistical model used in the simulation study.
-It outlines the basic model (Subsection \ref{sec:basic}) followed by the methodology for the spatially correlated treatment parameters (Subsection \ref{sec:spatial}), and finally GWR (Subsection \ref{sec:gwr}).
+\textcolor{green}{delete this paragraph??} This section describes the statistical model used in the simulation study.
+It outlines the basic model (S\st{ubs}ection~\ref{sec:basic})\revision{,} followed by the methodology for the spatially correlated treatment parameters (S\st{ubs}ection~\ref{sec:spatial}), and finally GWR (S\st{ubs}ection~\ref{sec:gwr}).
 
@@
 
-\subsection{Basic statistical model}\label{sec:basic}
+%\subsection{Basic statistical model}\label{sec:basic}
 
-In a conventional agricultural study, a field experiment can be considered as a rectangular matrix consisting of $r$ rows and $c$ columns, where the total number of plots in the experiment is $n=r\times c$.
-The notation $s_i\in \mathcal{R}^2, i=1,\ldots,n$ is a two-cell vector of the Cartesian coordination of the plot centroids, located on a regular grid \parencite{Zimmerman1991Randoma}.
-Hence, $y(s_i)$ denotes the dependent variable at a query location/grid $i$.
+\subsection{\revision{Hierarchical model for generating simulated data}}\label{sec:basic}
 
-With the assumption that $\bm{Y}$ is the vector of the plot data ordered as rows nested within ranges (columns), then the matrix notation of the model is 
+In a conventional agricultural study, a field experiment can be considered as a rectangular matrix\revision{, representing a regular grid with} $r$ rows and $c$ columns, where the total number of plots in the experiment is $n=r\times c$.
+\revision{Let} $s_i\in \mathcal{R}^2, i=1,\ldots,n$\revision{,} \revision{denote} the Cartesian coordinat\revision{e} of the \revision{$i$-th} plot centroid, located on a regular grid \parencite{Zimmerman1991Randoma}.
+\revision{Let} $y(s_i)$\revision{, $i=1,\ldots,n$,} denote the \revision{value of the} dependent variable \revision{recorded} at \revision{the} $i$\revision{-th plot}.
+
+\revision{Let} $\bm{Y}$ \revision{denote} the vector of the plot data ordered as rows nested within columns. The \revision{basic} model \revision{can be written using the matrix notation as follows:}
 \begin{equation}\label{eq:modelmatrix}
@@
 where $\bm{b}$ and $\bm{u}$ are vectors of fixed and random effects, respectively; $\bm{X}$ and $\bm{Z}$ are the associated design matrices; and $\bm{e}$ is the error vector.
-We further assume that $\bm{u}$ and $\bm{e}$ are pairwise independent and that their joint distribution is
+We assume that $\bm{u}$ and $\bm{e}$ are \revision{distributed} independent\revision{ly} \revision{of each other} and that their joint distribution is
 \begin{equation}\label{eq:covariance}
@@
 
-\subsection{Spatially correlated treatment parameters}\label{sec:spatial}
+%%\subsection{Spatially correlated treatment parameters}\label{sec:spatial}
 
-\textcite{Cao2022Bayesian} implemented the Bayesian hierarchical model with spatially correlated random parameters on large OFE strip trials.
+%% \revision{Extended from the basic model, }\textcite{Cao2022Bayesian} implemented the Bayesian hierarchical model with spatially correlated random parameters \revision{for analysing} large strip trials.
 Here, for the simulation study, we use the same model to generate the synthetic data.
 
-With the same notation given in the reference and previous section, the underlying model is represented as 
+\revision{Using the notation introduced above and in \textcite{Cao2022Bayesian}}, the \revision{simulation} model is \revision{given by} 
 \begin{equation}\label{eq:underlying}
 	\begin{split}
-		y(s_i)\mid \bm{u}_i,\theta_u,\sigma_e &\sim \N\left( \sum_{m=1}^{l}b_m x_m(s_i) + \sum_{j=1}^{k}u_j(s_i)z_j(s_i),~e(s_i)\right) \\
-		\bm{u}_i \mid \theta_u &\sim \N(0,V_u(\theta_u))\\
-		e(s_i) \mid \sigma_e &\sim \N(0,\sigma_e^2) 
+		y(s_i)\mid \bm{u}_i,\theta_u,\sigma_e &\sim \N\left( \sum_{m=1}^{l}b_m x_m(s_i) + \sum_{j=1}^{k}u_j(s_i)z_j(s_i),~e(s_i)\right), \\
+		\bm{u}_i \mid \theta_u &\sim \N(0,V_u(\theta_u)), \\
+		e(s_i) \mid \sigma_e &\sim \N(0,\sigma_e^2), 
 	\end{split}
 \end{equation}
-where: $x_1,\ldots, x_l$ denote $l$ fixed effects and $z_1,\ldots, z_k$ denote $k$ random effects; $b_m$ and $u_j(s)$ are the coefficients for the fixed and random terms, respectively; $\bm{u}_i$ is a vector of all random effects at grid $s_i\in\mathcal{S}$, $i=1,\ldots,n$; $\theta_u$ is a set of parameters of the covariance matrix $V_u$; and $\sigma_e$ is a positive latent variable.
+where: $x_1,\ldots, x_l$ denote $l$ fixed effects and $z_1,\ldots, z_k$ denote $k$ random effects; $b_m$ and $u_j(s)$ are the coefficients for the fixed and random terms, respectively; $\bm{u}_i$ is a vector of all random effects at \revision{the $i$-th plot,} %\in\mathcal{S}$ \revision{you need to define $\mathcal{S}$ in the previous section; in general just be careful of using any notation that you have not defined in the paper.
+It's okay to say we are borrowing notation from your previous paper, but it's a must that we define them here as well.
+This is a separate paper and we should  not expect people to go back to another paper to read this paper.
+Sorry for this long explanation.},
+$i=1,\ldots,n$; $\theta_u$ is a set of parameters of the covariance matrix $V_u$; and $\sigma_e$ is a positive latent variable.
 
 In model \eqref{eq:underlying}, the structure of the covariance matrix $V_u(\theta_u)$ of $\bm{u}_i$ can be either diagonal, which implies the treatments at grid $i$ are independent, or in general form, which means a correlation exists.
-\textcite{McElreath2015Statistical} suggest that the covariance of $\bm{u}_i$ can be $V_u = B(\sigma_u)R_uB(\sigma_u)$, where $B(\sigma_u)$ denotes the diagonal matrix of elements $\sigma_{u_j}$, $j=1,\ldots,k$.
+\textcite{McElreath2015Statistical} suggest that the covariance \revision{$V_u$} of $\bm{u}_i$ can be \revision{decomposed into $B(\sigma_u)R_uB(\sigma_u)$}, where $B(\sigma_u)$ denotes the diagonal matrix of elements $\sigma_{u_j}$, $j=1,\ldots,k$.
 For the matrix $R_u$ with correlation coefficients, we specify the Lewandowski-Kurowicka-Joe (LKJ) distribution \parencite{Lewandowski2009Generating}, which is given by
@@
 Here, $d$ is the space lag or distance; $r$ is a non-negative scaling parameter; $\nu> 0$ is a smoothness parameter determining the mean-square differentiability of the field; $\sigma_d^2$ is the variance of the process; $\Gamma$ is the Gamma function; and $K_\nu$ is the modified Bessel function of the second kind.
-If $\nu = r + \frac{1}{2}$, then the \Matern covariance can be expressed as a product of an exponential and a polynomial of order $r$ \parencite{Pandit2019Comparative, Abramowitz1974Handbook}, which simplifies the model and the computation process.
-The \Matern class $\nu=\frac{3}{2}$ and $\nu =\frac{5}{2}$ are common in application.
+If $\nu = r + 1/2$, then the \Matern covariance can be expressed as a product of an exponential and a polynomial of order $r$ \parencite{Pandit2019Comparative, Abramowitz1974Handbook}, which simplifies the model and the computation process.
+The \Matern \revision{models} \revision{with the values $3/2$ and $5/2$ for $\nu$} are common\revision{ly used} in \revision{most} application\revision{s}.
 
-Model \eqref{eq:underlying} has the advantage of reproducibility in the simulation study and robustness in estimation.
-It is possible even though only a single treatment is directly observed at each plot, and the responses of the other levels need to be estimated by interpolation because the spatial model allows using information from neighbouring plots with other treatments \parencite{Panten2010Enhancing, Piepho2011Statistical}.
+\revision{Using the above formulas and pre-defined parameters, we can generate simulated data for the study.}
 
-\subsection{Geographically weighted regression (GWR)}\label{sec:gwr}
+% \st{Model \eqref{eq:underlying} has the advantage of reproducibility in the simulation study and robustness in estimation.
+It is possible even though only a single treatment is directly observed at each plot, and the responses of the other levels need to be estimated by interpolation because the spatial model allows using information from neighbouring plots with other treatments} \parencite{Panten2010Enhancing, Piepho2011Statistical}.
 
-Geographically weighted regression (GWR) is a local regression approach and is adapted to obtain spatially-varying estimates of treatment effects for OFE \parencite{Rakshit2020Novel}.
-It is seen as a locally weighted regression method that operates by assigning a weight to each observation $i$ depending on its distance from the query grid on the field \parencite{Paez2002General}.
+\subsection{\revision{Fitting geographically weighted regression to simulated data}}\label{sec:gwr}
+
+Geographically weighted regression (GWR) is a local regression approach and is adapted \revision{recently} to obtain spatially-varying estimates of treatment effects for OFE \parencite{Rakshit2020Novel}.
+It is a locally weighted regression method that operates by assigning a weight to each observation depending on its distance from the query grid on the field \parencite{Paez2002General}.
 
@@
 \begin{equation}\label{eq:basicgwr}
-	y(s_i) = \beta_0 + \sum_{j=1}^{k} \beta_jz_j(s_i)+\varepsilon_i, 
+	y(s_i) = \beta_0 + \sum_{j=1}^{k} \beta_j \, \revision{x}_j(s_i) + \varepsilon_i, 
 \end{equation}
-where $\bm{\beta}$ and $\varepsilon\sim \N(0,\tau^2)$ are the model parameters for the $k$ levels treatments and error terms, respectively, at grid $i,\ i=1,\ldots,n$.
-The estimator of this model is given by the geographically weighted expression in
-\begin{eqnarray}\label{eq:betahat}
-	\bm{\hat{\beta}}(s) = \left( Z^\top W(s) Z \right)^{-1}Z^\top W(s) Y,
-\end{eqnarray}
-where $W(s)$ is an $n\times n$ diagonal matrix of weights, $\bm{w}$. Then it can be found by maximising the local log-likelihood 
+where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ and $\varepsilon_{i} \sim \N(0,\tau^2)$ are the model parameters for the $k$ treatment\st{s} \revision{levels} and error terms, respectively, at grid $i,\ i=1,\ldots,n$.
+
+\revision{For a query location $s$,} the local log-likelihood \revision{is given by} 
 \begin{eqnarray}\label{eq:locallog}
-	\log L(s;\beta) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_jz_j(s_i) \right)^2 
+	\log L(s;\beta) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_j \revision{x}_j(s_i) \right)^2 
 \end{eqnarray}
 with a given kernel function $K(\cdot,\cdot)$, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}.
+
+\revision{The local-likelihood} estimator,  \revision{obtained by maximising \eqref{eq:locallog},} of \revision{the regression coefficients $\bm{\beta}$ at the query location $s$} is given by  
+\begin{eqnarray}\label{eq:betahat}
+	\bm{\hat{\beta}}(s) = \left( \revision{X}^\top W(s) \revision{X} \right)^{-1}\revision{X}^\top W(s) Y,
+\end{eqnarray}
+where $W(s)$ is an $n\times n$ diagonal matrix of weights\st{, $\bm{w}$} \revision{with $i$th diagonal entry $K(s,s_i)$}.
+
 In the simulation study, we use a Gaussian kernel.
-In fact, the kernel is not the crucial factor in the GWR model fitting on OFE data.
-By contrast, the factor bandwidth has a higher influence on the estimation.
+In fact, the kernel \revision{function} is not the crucial factor in the GWR \revision{analysis}.
+\revision{In} contrast, the bandwidth has a higher influence on the estimation.
 
-The optimal bandwidth of a GWR model is usually given by the lowest AICc where 
+The optimal bandwidth \revision{for} a GWR model is usually \revision{selected} by the lowest AICc where 
 \begin{equation}\label{eq:aicc}
-	\mbox{AICc} = 2n\log (\tau^2) + n \log (2\pi) + n\frac{ n+\tr (S) }{n-2-\tr (S)},
+	\mbox{AICc} = 2n\log (\tau^2) + n \log (2\pi) + \frac{n^2+n\tr (S)}{n-2-\tr (S)},
 \end{equation}
-and $S$ is the matrix with the $i$-th row given by $Z_i\left( Z^\top W(s_i) Z \right)^{-1}Z^\top W(s_i)$ \parencite{Evans2020Assessment}.
+and $S$ is the matrix with the $i$-th row given by $\revision{X}_i\left( \revision{X}^\top W(s_i) \revision{X} \right)^{-1}\revision{X}^\top W(s_i)$ \parencite{Evans2020Assessment}.
 Alternatively, as suggested by \textcite{Rakshit2020Novel}, it can be based on the experimental design such that the local regressions capture data covering the full range of treatments.
@@
 
-To study the effect of randomised designs and systematic designs and to evaluate the power of GWR, we simulate spatially correlated large strip trials.
-The advantage of the simulation study is that the actual coefficients of the models are known, so adverse effects of model misspecification
-can be ruled out \parencite{Piepho2013Why}.
+To \revision{compare} the \revision{performances between} randomised \st{designs} and systematic designs \revision{in terms of accurate estimation of the model coefficients} \revision{using} GWR, we simulate \revision{several scenarios of} spatially correlated large strip trials.
+The advantage of the simulation study is that the actual coefficients of the models are known, so adverse effects of model misspecification can be ruled out \parencite{Piepho2013Why}.
 
-We investigate the combination of the following factors: types of design with two levels: randomised and systematic; response relationship with two levels: linear and quadratic; correlation of coefficients with two levels: low and high; spatial variation with three levels: identity (no spatial trend), $\AR\otimes\AR$ and \Matern form; GWR bandwidth with three levels: 5, 9 and optimum given by AICc.
-The fixed bandwidth 5 in the simulation study covers all treatment levels (five nitrogen levels) in a systematic design, where the information is adequate in the inference of a quadratic curve.
-Similarly, the fixed bandwidth 9 covers all possible treatment levels in a randomised design.
-This is because if all treatments are randomly allocated in the strips, there is a chance that the information of one treatment level is missing if the bandwidth is less than 9.
+We investigate the combination of the following factors: \revision{(i)} types of design with two levels, \revision{namely,} randomised and systematic; \revision{(ii)} response relationship with two levels, \revision{namely,} linear and quadratic; \revision{(iii)} correlation of coefficients \revision{of treatments within each plot} with two levels, \revision{namely,} low and high; \revision{(iv)} spatial variation \revision{between plots on the paddock} with three levels, \revision{namely,} identity (no spatial trend), $\AR\otimes\AR$, and \Matern form; \revision{(v)} GWR bandwidth with three value \revision{of} 5, 9 and the optimum \revision{value selected} by AICc.
+The fixed bandwidth \revision{of} 5 in the simulation study covers all treatment levels (five nitrogen levels) in a systematic design, where the information is adequate \revision{for} the inference \revision{based on} a quadratic \revision{response model}.
+Similarly, a fixed bandwidth of 9 is essential to cover all possible treatment levels in a randomised design.
+This necessity \revision{arises in} situations where treatments are randomly distributed across strips.
+In particular, if identical treatments are positioned at the far left edge of the first replicate block and the far right edge of the second replicate block, a bandwidth smaller than 9 would  \revision{result in} the GWR model capturing only the treatments between these boundaries, thereby missing the treatment level\revision{s} at the extremes.
 
-With model \eqref{eq:underlying}, we generate the yield as a response to nitrogen treatment in two scenarios that cover whether the yield has a linear or quadratic relationship with the nitrogen rate.
-The nitrogen rates are treated as continuous observations with five levels: 0, 35, 75, 105 and 140 kg/ha.
-A strip plot structure was used to allocate the five nitrogen levels, where each level is assigned to one strip.
-Then we assume that the experimental design of the trial consists of four replicates, each containing 5 ranges (columns) by 93 rows.
-The nitrogen rates are allocated randomly or systematically in the whole field.
-The overall layout of the trial is 20 ranges by 93 rows.
-Examples of a randomly and systematically allocated treatment map are presented in Figure \ref{fig:Nitrogen}.
+\revision{Using} model \eqref{eq:underlying}, we generate yield as a response to nitrogen treatment \revision{for} two scenarios that cover whether yield has a linear or quadratic relationship with the nitrogen rate.
+The nitrogen rates are treated as continuous observations with five levels: 0, 35, 75, 105, and 140 kg/ha.
+A strip plot structure was used to allocate the five nitrogen levels \revision{with} each level assigned to one strip.
+The experimental design of the trial consists of four replicates, each containing 5 columns by 93 rows.
+The nitrogen rates are allocated randomly or systematically  \revision{across the entire} field.
+The overall layout of the trial is 20 \revision{columns} by 93 rows.
+Examples of randomly and systematically allocated treatment map are presented in Figure \ref{fig:Nitrogen}.
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_RandNitro.pdf}
-		\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
+		\includegraphics[width=\linewidth]{Expt/Col_RandNitro_V2.pdf}
+		%\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
+        \caption{}\label{fig:RandNitrogen}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_SystNitro.pdf}
-		\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
+		\includegraphics[width=\linewidth]{Expt/Col_SystNitro_V2.pdf}
+		%\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
+        \caption{}\label{fig:SystNitrogen}
 	\end{subfigure}
-	\caption{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly \eqref{fig:RandNitrogen} and systematically \eqref{fig:SystNitrogen} allocated into strips in each replicate block.}\label{fig:Nitrogen}
+	\caption{\revision{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly \eqref{fig:RandNitrogen} and systematically \eqref{fig:SystNitrogen} allocated into strips in each replicate block.}}\label{fig:Nitrogen}
 \end{figure}
 
-With model \eqref{eq:underlying}, the nitrogen rates are treated as continuous observations with five levels.
-For a linear relationship, we assume that the true global intercept is $b_0 = 65$ and the slope is $b_1=0.05$.
-The parameters are chosen according to the estimates by \textcite{Rakshit2020Novel, Cao2022Bayesian} on the Las Rosas corn field data, which is initially provided by \textcite{Luc2004ASpatial} and embedded in the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
-The unit of yield is quintals per hectare.
-The variances of $\bm{u}_i$ are $\sigma_{u_0} = 5$ and $\sigma_{u_1}=0.01$.
-For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters for column and row are $\rho_c = 0.15$ and $\rho_r=0.5$.
-We have assumed a higher correlation in the rows due to the fact that the crop is traditionally sown and harvested along ranges where the correlation is higher in the perpendicular direction than the travel direction \parencite{Marchant2019Establishinga}.
-For the \Matern covariance matrix \eqref{eq:matcov}, we set $\sigma_d^2=1$, $r=1$ and $\nu = \frac{3}{2}$.
-After drawing samples of $\bm{u}$ from $\N(0,\Sigma_u)$, the true spatially varying coefficients are $\bm{\beta}_0 = b_0 + \bm{u}_0$ and $\bm{\beta}_1 = b_1 + \bm{u}_1$.
+\revision{SR comment: For the above figure, please delete the sub captions.
+Moreover, try to use either column or range throughout the paper.
+I would suggest use the term column throughout the paper.
+There is no need to use the term range.
+If you like to do that, then do it consistently throughout the paper.
+If you decide to use the term column, then please change the y-axis titles of the figures.
+Finally, it would be better if you could increase the font size of the text used in the figures.}
 
-Similarly, for the quadratic relationship, we have the true global intercept $b_0 = 65$, coefficients $b_1 = 0.05$ and $b_2 = -0.0003$, 
-%where the curve is in a frown shape. 
-making the curve concave down.
-We keep $\sigma_{u_0} = 5$, $\sigma_{u_1}=0.01$ and add $\sigma_{u_2}=0.0001$ because the true values are small.
+\revision{In} model \eqref{eq:underlying}, the nitrogen rates \revision{considered as the treatment factor} with \revision{the} five levels \revision{of 0, 35, 70, 105 and 140 kg/ha}.
+\revision{To specify a} linear relationship \revision{in the simulation study}, we \revision{consider the values of $65$ and $0.05$ for the} global intercept $b_0$ and slope $b_1$ coefficients, respectively.
+The\revision{se} parameters are chosen according to the estimates \revision{reported} by \textcite{Rakshit2020Novel, Cao2022Bayesian} \revision{for} the Las Rosas corn field data, which is initially provided by \textcite{Luc2004ASpatial} and \revision{can be accessed via} the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
+The unit of yield \revision{considered here} is quintals per hectare.
+The variances of \revision{the coefficients} $\bm{u}_i$ are \revision{set to $5$ for $\sigma_{u_0}$ and $0.01$ for $\sigma_{u_1}$}.
+For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters \revision{$\rho_c$ (in the column direction) and $\rho_r$ (in the row direction) are set to $0.15$ and $0.50$, respectively}.
+We \revision{assume} a higher correlation in the row \revision{direction because} the crop is traditionally sown and harvested along ranges\revision{,} \revision{and} the correlation is higher in the \revision{direction} perpendicular \revision{to the sowing} direction \parencite{Marchant2019Establishinga}.
+For the \Matern covariance matrix \eqref{eq:matcov}, we set \revision{the value of the variance parameter $\sigma_d^2$ to $1$, the value of the parameter $r$ to $1$, and the value of the parameter $\nu$ to $3/2$}.
+After drawing samples of $\bm{u}$ from $\N(0,\Sigma_u)$, the true spatially varying coefficients \revision{$\bm{\beta}_0$ and $\bm{\beta}_1$ are specified using the relations} $\bm{\beta}_0 = b_0 + \bm{u}_0$ and $\bm{\beta}_1 = b_1 + \bm{u}_1$.
+\\
+
+For the quadratic relationship, we \revision{consider}  $b_0 = 65$, $b_1 = 0.05$, and $b_2 = -0.0003$.
+\revision{These choices make the response} curve concave down.
+\revision{For the variance components,} we \revision{consider} $\sigma_{u_0} = 5$, $\sigma_{u_1}=0.01$, and $\sigma_{u_2}=0.0001$.
 The rest of the parameters remain unchanged.
@@
 
-To summarise, with the true spatially varying coefficients of the treatments, the simulated yield is obtained by 
+The simulated yield \revision{response} is obtained by 
 \begin{equation}
@@
 	\text{Quadratic} &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + (b_2 + u_{2i})N_i^2 + e_i
-\end{cases},
+\end{cases}
 \end{equation}
 where $N_i$ is the nitrogen rate, $e_i\sim \N(0,1)$ is the error term at grid $i$, $i = 1, \ldots, n$.
-Figure \ref{fig:Lines} illustrates how these curves behave for the linear and quadratic relationships.
+Figure \ref{fig:Lines} illustrates \revision{the yield response to Nitrogen} for the linear and quadratic relationships.
 
@@
 		\includegraphics[width=\linewidth]{Expt/LinlinesV2.pdf}
-		\caption{Linear relationship between crop yield and nitrogen levels, where $y=65+0.05x$.}
+		%\caption{}
         \end{subfigure}
@@
 		\includegraphics[width=\linewidth]{Expt/QualinesV2.pdf}
-		\caption{Quadratic relationship between crop yield and nitrogen levels, where $y=65+0.05x-0.003x^2$.}
+		%\caption{}
         \end{subfigure}
-	\caption{Noise-free linear and quadratic relationships between crop yield and nitrogen levels.}\label{fig:Lines}
+	\caption{\revision{The linear relationship of yield and nitrogen (\textit{left}) is $y=65+0.05N$, and the quadratic relationship between yield and nitrogen (\textit{right}) is $y=65+0.05N-0.003N^2$.}}\label{fig:Lines}
 \end{figure}
+% \revision{SR comment: remove the subcaptions from Figure~2. Include those details in the main caption.}
 
@@
 
-The purpose of the simulation study is to test the effect of different types of designs in coefficients estimation by GWR.
-Identical coefficients were used in one comparison process for two types of designs, and the yield reflects the effect of nitrogen rates.
+%\st{The purpose of the simulation study is to test the effect of different types of designs in coefficients estimation by GWR.
+Identical coefficients were used in one comparison process for two types of designs, and the yield reflects the effect of nitrogen rates.}
 
@@
 
-Running the simulation 100 times, we assessed the performance of the randomised and systematic designs for linear and quadratic responses.
-In subsection \ref{Sec:MSE} the mean squared errors are compared between the two designs for different bandwidths, parameter correlations and spatial covariance matrices.
-Subsection \ref{Sec:anova} uses an analysis of variance (ANOVA) test to explore the significance of the factors in the simulation, while subsection \ref{Sec:bandselect} states the performance of bandwidth selection using AICc.
+\revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models.
+To this end, we perform $100$ simulations of each scenario described in the previous section.} In Section~\ref{Sec:MSE}, the mean squared errors are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix.
+Section~\ref{Sec:anova} uses \revision{the} analysis of variance (ANOVA) to  \revision{assess} the significance of the factors \revision{considered} in the simulation \revision{study}.
+%\st{subsection} Section~\ref{Sec:bandselect} \st{states} \revision{presents} the \st{performance of} \revision{results of} bandwidth selection using AICc.
 
@@
 
-\subsection{Mean squared error}\label{Sec:MSE}
+\subsection{\revision{Comparison based on} mean squared errors}\label{Sec:MSE}
 
-We evaluated the true mean squared error (MSE) of the estimated coefficient differences.
-This was calculated by the difference of true coefficients, $\bm{\beta} = b + \bm{u}$, and estimated spatially varying coefficients, $\bm{\hat{\beta}} = \hat{b}+\bm{\hat{u}}$, for each grid, and then squared the discrepancy and averaged across the field for comparison.
-The results are shown in Figures \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE} where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$), ``AR1'' is for $\AR(0.15)\otimes \AR(0.5)$ and ``Matern'' is the \Matern covariance with $\nu=\frac{3}{2}$.
-Since the MSEs of $\beta_0$, $\beta_1$, and $\beta_2$ are small, we take the natural logarithm for better visualisation.
+\revision{To assess the performance of different designs for a simulation scenario,} we \revision{computed the} mean squared error (MSE) \revision{corresponding to all} coefficient \revision{estimates}.
+This was \revision{computed} by \revision{taking} the difference of true coefficients $\bm{\beta}$ (i.e., $b + \bm{u}$) and the estimated spatially varying coefficients $\bm{\hat{\beta}}$ (i.e., $\hat{b} + \bm{\hat{u}}$) for each grid, and then \revision{averaging} the squared discrepancies across \revision{all the grid points in} the field.
+The results are shown in Figures \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE}, where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$), ``AR1'' for $\AR(0.15)\otimes \AR(0.5)$\revision{,} and ``Matern'' \revision{for} \Matern covariance with $\nu=\frac{3}{2}$.
+Since the MSEs \revision{corresponding to the estimation of} $\beta_0$, $\beta_1$, and $\beta_2$ are small, we take the natural logarithm \revision{of the MSE values} for better visualisation.
 
 % Paragraph about Figure 3 and the performance for a linear response
-With the assumption of a linear response, both randomised and systematic designs perform similarly, meaning GWR is able to partition the local varying intercept and treatment coefficient.
-Figure \ref{fig:LinBetaMSE} shows that if the response is linear, the MSEs of $\hat{\beta}_0$ and $\hat{\beta}_1$ estimated by GWR, for all bandwidths,
-%with bandwidth 5, 9 and the optimal bandwidth found by AICc
-is not distinguishing between randomised and systematic designs.
-This is true regardless of the type of spatial covariance matrix when the correlation within grids is small ($\epsilon=1$), or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
+\revision{For} a linear response, both randomised and systematic designs perform similarly\revision{, particularly for the cases NS and AR1.} Figure~\ref{fig:LinBetaMSE} shows that the MSEs \revision{corresponding to} $\hat{\beta}_0$ and $\hat{\beta}_1$ for all bandwidths \revision{are fairly similar for both} designs.
+\revision{However, the results in Table~1 show that the MSE medians corresponding to $\hat{\beta}_1$ for the Matern case are consistently lower for the systematic design.} This is true regardless of the type of spatial covariance matrix \revision{considered in a simulation}.
+\\
+\textcolor{green}{SR comment: I am not sure what's going on here}
+when the correlation within grids is small ($\epsilon=1$), or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
 The GWR with bandwidth selected by AICc has a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).
@@
 
-\subsection{AICc Bandwidth selection}\label{Sec:bandselect}
+% \revision{Exclude the following section about AICc --- this is completely irrelevant for this paper. You can relegate this to the supplement file or in the appendix if you like.}
+%  \subsection{AICc bandwidth selection}\label{Sec:bandselect}
 
-From the simulation study, we found that the bandwidth given by AICc skewed to 1 if spatial covariance was included in the model, for all types of the design and the nature of the response.
+% From the simulation study, we found that the bandwidth given by AICc skewed to 1 if spatial covariance was included in the model, for all types of the design and the nature of the response.
 If spatial covariance was not introduced, the GWR tended to use all data in one row (Figure \ref{fig:histband}).
 
-\begin{figure}[!htp]
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{Expt/BandwidthLinear.pdf}
-		\caption{Histogram of optimal bandwidth for linear response.}
-	\end{subfigure}
-	\hspace{0.05\textwidth}
-	\begin{subfigure}[t]{0.45\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{Expt/BandwidthQuadra.pdf}
-		\caption{Histogram of optimal bandwidth for quadratic response.}
-	\end{subfigure}
-	\caption{Histogram of optimal bandwidth found by AICc for linear and quadratic response. }\label{fig:histband}
-\end{figure}
+% \begin{figure}[!htp]
+% 	\begin{subfigure}[t]{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\linewidth]{Expt/BandwidthLinear.pdf}
+% 		\caption{Histogram of optimal bandwidth for linear response.}
+% 	\end{subfigure}
+% 	\hspace{0.05\textwidth}
+% 	\begin{subfigure}[t]{0.45\textwidth}
+% 		\centering
+% 		\includegraphics[width=\linewidth]{Expt/BandwidthQuadra.pdf}
+% 		\caption{Histogram of optimal bandwidth for quadratic response.}
+% 	\end{subfigure}
+% 	\caption{Histogram of optimal bandwidth found by AICc for linear and quadratic response. }\label{fig:histband}
+% \end{figure}
 

### 2024-07-29 RCode/OFEExptNewPara.R
Simu 1k R code

@@ -1,0 +1,1248 @@
+source("Initialization.R")
+
+b0 <- 65
+b1 <- 0.05
+b2 <- -0.0003
+
+x1 <- seq(0,140,length=5)
+# x <- c(0,39,50.6,75.4,99.8,124.6)
+y1 <- b0 + b1*x1+b2*x1^2
+
+dat1 <- data.frame(x=x1,y=y1)
+
+x2 <- seq(0,140,length=100)
+# x <- c(0,39,50.6,75.4,99.8,124.6)
+y2 <- b0 + b1*x2+b2*x2^2
+
+dat2 <- data.frame(x=x2,y=y2)
+
+ggplot(data=dat1) + geom_point(aes(x,y),size=3) + 
+  scale_x_continuous(labels = x1,breaks = x1) +
+  geom_line(data=dat2,aes(x,y)) + thm1 +
+  xlab("Nitrogen Level") + ylab("Yield (quintals/ha)")
+
+
+y3 <- b0 + b1*x1
+dat3 <- data.frame(x=x1,y=y3)
+
+ggplot(data=dat3) + geom_point(aes(x,y),size=3) + 
+  scale_x_continuous(labels = x1,breaks = x1) +
+  geom_line(aes(x,y)) + thm1 +
+  xlab("Nitrogen Level") + ylab("Yield (quintals/ha)")
+
+
+
+
+
+
+y <- b0 + b1*x
+
+plot(x,y)
+
+
+####### parameter preparation #########
+
+M <- 100 ## simulation iterations
+
+paralist <- list(
+  Nitro  = seq(0,140,length=5),
+  nRep   = 4,
+  nRow   = 93,
+  b_0    = 65,
+  b_1    = 0.05,
+  b_2    = -0.0003,
+  sig_u0 = 5,
+  sig_u1 = 0.01,
+  sig_u2 = 0.0001,
+  rho_range = 0.15,
+  rho_row   = 0.5
+)
+lev    <- 2  # linear trend
+nRange <- 20
+nRow   <- paralist$nRow
+
+
+##### simulation study data generating functions #######
+SimuGenDat_Lin <- function(paras,covmat,eta){
+  
+  nitro  <- sample(paras$Nitro)
+  
+  nRep   <- paras$nRep
+  nRange <- nRep * length(nitro)
+  nRow   <- paras$nRow
+  N      <- nRange * nRow
+  
+  SystLevel <- rep(nitro,nRep)
[…]

### 2024-07-29 RCode/OFEExptNewPara1KSimuResults2024.R

@@ -1,0 +1,906 @@
+######### load data ############
+rm(list = ls())
+load("~/Curtin/Research/BayesTechOFE/ExptOut1Ksimu.RData")
+
+### 1 k simulations
+
+### low correlation eta = 1
+#### results , low correlation eta = 1 ####
+# NS 
+MSE_ns_LR5_sq  <- apply(MSE_ns_LR5, c(1,2), function(a) mean(a^2))
+MSE_ns_LR9_sq  <- apply(MSE_ns_LR9, c(1,2), function(a) mean(a^2))
+MSE_ns_LRbw_sq <- apply(MSE_ns_LRbw, c(1,2), function(a) mean(a^2))
+
+MSE_ns_LS5_sq <- apply(MSE_ns_LS5, c(1,2), function(a) mean(a^2))
+MSE_ns_LS9_sq <- apply(MSE_ns_LS9, c(1,2), function(a) mean(a^2))
+MSE_ns_LSbw_sq <- apply(MSE_ns_LSbw, c(1,2), function(a) mean(a^2))
+
+# ar1
+MSE_ar1_LR5_sq <- apply(MSE_ar1_LR5, c(1,2), function(a) mean(a^2))
+MSE_ar1_LR9_sq <- apply(MSE_ar1_LR9, c(1,2), function(a) mean(a^2))
+MSE_ar1_LRbw_sq <- apply(MSE_ar1_LRbw, c(1,2), function(a) mean(a^2))
+
+MSE_ar1_LS5_sq <- apply(MSE_ar1_LS5, c(1,2), function(a) mean(a^2))
+MSE_ar1_LS9_sq <- apply(MSE_ar1_LS9, c(1,2), function(a) mean(a^2))
+MSE_ar1_LSbw_sq <- apply(MSE_ar1_LSbw, c(1,2), function(a) mean(a^2))
+
+# matern
+MSE_mat_LR5_sq <- apply(MSE_mat_LR5, c(1,2), function(a) mean(a^2))
+MSE_mat_LR9_sq <- apply(MSE_mat_LR9, c(1,2), function(a) mean(a^2))
+MSE_mat_LRbw_sq <- apply(MSE_mat_LRbw, c(1,2), function(a) mean(a^2))
+
+MSE_mat_LS5_sq <- apply(MSE_mat_LS5, c(1,2), function(a) mean(a^2))
[…]

### 2024-07-29 MSforSubmission/Response.tex
Re-organise files. MS for submission

\documentclass[a4paper]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
%\geometry{left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm}                   		
\usepackage{graphicx,subcaption}					
\usepackage{amssymb}
\usepackage{indentfirst}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{lineno}
\usepackage{setspace}
\usepackage{booktabs,multirow}
\usepackage{authblk}
\usepackage{todonotes}
\usepackage{tikz}
\usepackage{float}
\usepackage[tracking=true]{microtype}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage[title]{appendix}

\usepackage{xcolor}
\newcommand\mynotes[1]{\texttt{\textcolor{orange}{#1}}}
%\renewcommand{\thesubsection}{\Alph{subsection}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newcommand{\E}{\mathrm{E}}
\newcommand{\D}{\mathcal{MD}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\Corr}{\mathrm{Corr}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\R}{\texttt{R}}
\newcommand{\asreml}{\texttt{ASReml-R}}
\newcommand{\Matern}{Mat\'ern }
\newcommand{\N}{\mathcal{N}}
\newcommand{\AR}{\mathrm{AR1}}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{io} = [trapezium, trapezium left angle=70, trapezium right angle=110, minimum width=0.5cm, minimum height=1cm, text centered, draw=black, fill=blue!30]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
% \tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
\tikzstyle{decision} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

\usepackage[url=false, isbn=false, eprint=false, backref=false, style= authoryear, backend=bibtex,uniquename=init, maxcitenames=2, giveninits=true, maxbibnames=100]{biblatex}  %%% backend=biber
\DeclareNameAlias{sortname}{family-given} %%% last-first
\addbibresource{BayesOFE.bib}

\renewcommand{\topfraction}{.9}
\renewcommand{\bottomfraction}{.9}
\renewcommand{\textfraction}{.05}
\newcommand{\qtitle}[1]{\textit{\textbf{\textcolor{blue}{#1}}}}
\newcommand{\revision}[1]{\textcolor{red}{#1}}
\newcommand{\reviewer}[1]{\textcolor{blue}{\textit{#1}}}

%\title{Statistical and Economic Analysis of Large Strip Trials in Comparative Experiments} %% Maybe move "On-farm" to keywords

\title{Revision and Response to Reviewers' Comments \\ 
\large on the manuscript (FIELD-D-23-02059R1) \\ Optimal design for on-farm strip trials --- systematic or randomised?}

\author[1,*]{Zhanglong Cao}
\author[1]{Jordan Brown}
\author[1]{Mark Gibberd}
\author[1]{Julia Easton}
\author[1,2]{Suman Rakshit}

\affil[1]{Curtin Biometry and Agricultural Data Analytics, Centre for Crop and Disease Management, Curtin University, Perth, Australia}
\affil[2]{School of Electrical Engineering, Computing and Mathematical Sciences, Curtin University, Perth, Australia}

\affil[*]{Corresponding author: Zhanglong Cao, zhanglong.cao@curtin.edu.au}

\date{}

\begin{document}
\linenumbers

\maketitle

The authors thank the Associate Editor and Reviewers for their helpful comments and valuable suggestions. All comments/recommendations are addressed below, where each reviewer's comment is presented in \textcolor{blue}{\textbf{blue text}} and each response is given in \textcolor{black}{\textbf{black text}}. As part of this revision process, the newly added materials in the revised draft of the paper are presented using \revision{\textbf{red text}}.

\section*{Reviewer 1 writes:}

\reviewer{This paper compares systematic to randomized designs for on-farm field experimentation. The objective the authors are having in mind is the estimation of spatially varying response functions. The authors find that the systematic design yields more accurate predictions, as anticipated by the authors and some cited references.}

\reviewer{1. My main suggestion is that the authors could also use the exact same simulation to evaluate performance of another objective: Estimation of the marginal regression function, given by the fixed effects b. Randomization theory would be expected to ensure that the randomized design yields unbiased estimates and also yield valid F- and t-tests for treatment effects. It would be very interesting to see how the systematic design fares in comparison when this is the specific purpose of analysis. Of course, as global estimation is the objective in this case, GWR would need to be replaced by classical regression analysis, perhaps just for the model used for simulating the data. Simulating a suitable null hypothesis may also be useful. The linear model could provide a suitable null model for the quadratic as an alternative. Depending on the outcome, such an extension of the simulation would also further accentuate the general conclusion, and potentially enforce the message that a systematic design may be more suitable for local estimation, whereas a randomized design may be preferable for global estimation.}

Thank you for your insightful suggestion. We agree that evaluating the performance of the estimation of the marginal regression function, given by the fixed effects $b$, could provide additional valuable insights. Those are some current research topics that we are working on.

The difficulty is how to analyse the global effects and what models are appropriate for the topic. \textcite{Stefanova2023Statistical} proposed an approach for comparing the treatments/varieties of a large strip OFE trial by partitioning the entire paddock into smaller regions, named pseudo-environment, then used a MET-like approach to predict the best treatments of each pseudo-environment and the entire paddock.

We would like to extend our simulation from continuous variables, such as nitrogen rate, to discrete variables, such as varieties, and incorporate \textcite{Stefanova2023Statistical}'s approach to the data to test the performance of systematic designs and randomised designs. The difficulties are how to generate these simulated data robustly,  how to automatically apply the approach to the simulated data in a few iterations, and subsequently to compare the estimated values with the true values.

In the meantime, we are investigating the GAM model, the additive model, with incorporating the spline term to accommodate the spatial variation of OFE. Hopefully, we will achieve nice results for publication.

\reviewer{2. My major questions are these (see line 156): For the randomized allocation, was a new randomization generated in each simulation run? Or was the same randomization used in each run. Regarding the systematic design, how was the systematic order determined? Was this the same in each simulation run, and was this equal to that shown in Figure 1? Or was a new systematic order chosen in each run. More importantly, what can be said about the optimal systematic order for the purpose of map estimation? How can this optimum be found? How can optimality be defined? It may well be that the authors do not have an answer to this question. However, the question is relevant, and it is worth at least mentioning in the discussion. At any rate, the choice of systematic order the authors made needs to be explained and justified.}

We appreciate the reviewer for pointing out this crucial confusion in this manuscript. It is not clearly explained in the first draft. We have revised the manuscript by the following amendments:

We added one more subsection \revision{2.3 Performance evaluation} to describe the evaluation of an optimal design:

\revision{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates. The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model (3), and the spatially varying estimates of that coefficient produced by GWR (8), and then averaging these squared differences across all the grid points. The lower the MSE, the better the design’s performance.}

At the beginning of section 4, we rewrote the paragraph that:

\revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models. To this end, we perform 100 simulations of each of the 24 scenarios, described in the previous section. In each simulation, we first generated the coefficients for all grids and then applied the treatment in each grid to calculate the yield value using the model coefficients. For the treatments in all grids, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design. For a randomised design, all replicates have different orders of the treatments.}

\reviewer{3. In the Methods section, the subheadings could be reconsidered. Perhaps they can be reworded to clarify the purpose of each model. Which model is used for simulating the data and which model is used for analysing the simulated data?}

Thank you for the comment. I have merged the subsections 2.1 and 2.2 to make a clear explanation of the model, and revised the subsection titles to: \revision{2.1 Hierarchical model for generating simulated data} and \revision{2.2 Fitting geographically weighted regression to simulated data}. Additionally, we have added one more subsection that \revision{2.3 Performance evaluation} to explain how to evaluate the performance.

\reviewer{4. At the start of Section 3, the authors state an advantage of data simulated from a parametric model. Are there any disadvantages, and what alternatives could be considered? Perhaps this is also a point for the discussion.}

Thank you for your insightful comment. It is right, while data simulated from a parametric model does have its advantages, it also has certain limitations. One potential disadvantage is that the results are heavily dependent on the assumptions of the parametric model. If these assumptions do not hold, the simulation results may not accurately reflect the real-world scenario.

So we have revised Section 3, starting with a better description of the data source and why the parameters are chosen at this level. The simulated data aligns with the authentic data from a corn field in Las Rosa. This data has been studied and reported by \textcite{Rakshit2020Novel, Cao2022Bayesian}. The assumption is based on their findings.

\reviewer{5. Also at the start of Section 3, where factors studied in the simulation are listed (from line 156), it is not immediately obvious, if the description of details of the simulations refers to the data simulation or the analysis of simulated data. Clarification would be useful. At this point, it is also still not clear which model was used for simulating the data and which for analysing the data. This only becomes clearer gradually downstream in the paper. I feel it could be made very clear much earlier in the paper.}

We have revised Section 3 for a better and clearer explanation.

\reviewer{6. It may help greatly if the statement of the objectives not made in line 190 comes much earlier.}

We have put a new sentence in the introduction section in line 89: \revision{We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}

\reviewer{7. The MSE, used for evaluating predictions, should be described in the section on simulation, as it is part of the methods.}

Thank you for the comment. We agree and have added a new sub-section \revision{2.3 Performance evaluation to describe MSE.}.

\reviewer{8. Line 168: Is the 75 for the mid N level a typo? Should this be 70? Why are the levels different from those in Figure 1?}

Thanks for pointing out the discrepancy. We have revised the mistake by updating the labels in the figures and also in the main context:

\revision{Figure 1: The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (left) and systematically (right) allocated into strips in each replicate block.}

In line 160: \revision{We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.}

\section*{Reviewer 2 writes:}

\reviewer{The paper presents results from a simulation study to compare two experimental designs, a randomized and a systematic. In my opinion, the subject should be of moderate interest to readers of the journal. The paper needs some work to be considered for publication in FCR, assuming that such technical paper is of interest to most readers of the journal. In its current form I believe it is too technical with a lot of statistical jargon. Also the organization and flow of the information needs to be improved. I made some specific comments about my concerns and on how the authors can improve the manuscript.}

\reviewer{The general suggestion is to revise the text without so much statistical jargon or add explanations that will make it easier for agronomists to follow/understand.}

We have revised the main text of the manuscript to enhance its readability and comprehension. Additionally, we have streamlined the statistical model sections for simplicity and clarity.

\reviewer{Specific comments: 1) Line 40. Please define OFE here and not in line 46 and 57}

We have now defined OFE when it first appears in the main text in line 44. The revised version is \revision{On-farm experiment (OFE) enables farmers the flexibility ...}.

\reviewer{2) Line 71. Constraints in the field.}

Thanks for pointing out the error. We have changed it to \textit{constraints \revision{in} the field.}

\reviewer{3) Lines 73-74. I do not see the value of that sentence.}

We have polished this paragraph. The purpose of this sentence is to introduce that a linear model may not be sufficient in capturing the yield curve. That's why we compared linear and quadratic curve in this study.

\reviewer{4) Lines 81-83. These are results and do not fit in the introduction.}

We have rewritten this paragraph to better fit the manuscript by:
\revision{In this study, we generate simulated data for several scenarios, where each scenario is constructed by choosing one component at a time from the following four categories: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) model coefficients with low and high correlations; and (iv) spatial variance-covariance matrix  among grids given by identity (no spatial trend), AR1 $\bigotimes$ AR1, and Mat\'{e}rn forms. We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}

\reviewer{5) Lines 84-89. There is no need to describe the structure of the paper. All papers have introduction, methods, results and discussion. I suggest to use the last paragraph to describe the objectives of the paper and why is important.}

We have removed this paragraph. Instead, we put one more sentence here: 
\revision{The GWR model in this paper is implemented with the \R-package \texttt{GWmodel} \parencite{lu2014gwmodel, Gollini2015GWmodel}.}

\reviewer{6) Lines 91-93. Again there is no need for these three lines.}

We have removed these lines and re-structured this section by merging subsections 2.1 and 2.2, and inserting a new subsection 2.3. The revised subsection titles are:

\revision{2.1 Hierarchical model for generating simulated data}.
\revision{2.2 Fitting geographically weighted regression to simulated data}.
\revision{2.3 Performance evaluation}.

\reviewer{7) 3 Simulation study. More information is needed here. I suggest starting from describing the simulated experiment. For example, I had to read up to line 160 and again after line 166 to understand that the independent variable of interest would be nitrogen fertilizer with 5 levels.}

We have rewritten the simulation section by reordering the paragraphs and making a clearer explanation.

\reviewer{8) Line 172. For someone who is not familiar with systematic design, they would have to read up to line 172 and see figure 1 to understand the difference. I suggest describing what a systematic design is early in the introduction so every reader understands what is being compared.}

We firstly in line 39 inserted the sentence \revision{ where treatments are randomly allocated in each replicate} for a randomised design.

In line 42, we rewrote the sentence as follows: \revision{With the primary aim of obtaining unbiased estimates of global treatment effects, randomised designs, which use a different layout of treatments in each replicate, are routinely used for on-farm strip trials, whereas systematic designs, which use the same layout of treatments in all replicates, are rarely used.}

In line 168, we try to remind the reader by using the following description that \revision{Examples of a randomised design, which uses different orders of treatment in each replicate, and a systematical design, which uses the same order of treatment in all replicates, are presented in Figure 1.}

\reviewer{9) 4.1 Mean squared error. I recommend to put the figures in order. Now after figure 3 we jump to figure 6 and then figure 4 followed by figure 7.}

Thank you for your suggestion. We have organised the figures in order and updated them with enhanced visualisation.

\reviewer{10) For more practical purposes, apart from comparing MSE and coefficients, it would be valuable to see two maps with optimal nitrogen rate side-by-side. One map generated by the randomized design and one generated by the systematic design. I suspect that for practical purposes maps will be very similar.}

It's a good point. From the practical point of view, that's the most interests output for growers. So, we added one more sub-section at the end of section 4: 
\revision{4.3 An example of optimal nitrogen map} with the description of the results and two optimal nitrogen maps.

\revision{In practice, growers are more interested in the prescription map that tells them where the appropriate nitrogen should be applied on the paddock. With the application of GWR, we can find the local variations in crop needs, allowing for more precise and efficient nitrogen application. Each grid of the paddock receives the optimal amount of fertiliser. Consequently, this leads to improved crop yields, reduced investment cost and high profit.}

\revision{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 from a randomised design and a systematic design using the same simulated coefficients of a quadratic curve under the assumption of $\AR\otimes\AR$ spatial covariance and low within-grid correlation. The optimal rate is given by $\hat{N} = -\hat{\beta}_1/(2\hat{\beta}_2)$ with constraints between 0 and 140. For the randomised design, GWR failed to estimate the central part of the paddock. On the contrary, the estimated map from the systematic design is more consistent.}

\begin{figure}[H]
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/optN_syst_AR1B9.pdf}
		%\caption{}
        \end{subfigure}
	\hspace{0.05\textwidth}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\includegraphics[width=\linewidth]{Expt/optN_rand_AR1B9.pdf}
		%\caption{}
        \end{subfigure}
	\caption{\revision{Optimal Nitrogen rate estimated by GWR from a randomised design (\textit{left}), and a systematic design (\textit{right}).}}\label{fig:optNmap}
\end{figure}

%\printbibliography

\end{document}

### 2024-07-29 ArchiveMS/mainV2_clean.tex
Re-organise files. MS for submission

--- 2024-02-08 mainV2_mark.tex
@@
 \begin{abstract}
-
-\zc{CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians.
+CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians.
 However, for on-farm trials, the choice may depend on the objective of the experiments.
 If the purpose is to create a prescription map of a continuous input for each plot of a grid covering a large strip trial, a systematic design may be a better choice, but it attracts less discussion and attention.
-}
 
-\zc{OBJECTIVE OR RESEARCH QUESTION: This study aims to evaluate the performance of systematic designs with geographically weighted regression (GWR) models in addressing spatial variation and estimating continuous treatment effects in large strip trials through numeric simulations.}
+OBJECTIVE OR RESEARCH QUESTION: This study aims to evaluate the performance of systematic designs with geographically weighted regression (GWR) models in addressing spatial variation and estimating continuous treatment effects in large strip trials through numeric simulations.
 
-\zc{METHODS: A Bayesian hierarchical model with spatially correlated random parameters is utilised to generate simulated data for various scenarios of large strip on-farm trials.
-The study employs GWR models to analyse the simulated data for two assumptions: a linear response and a quadratic response to the treatment effects.}
+METHODS: A Bayesian hierarchical model with spatially correlated random parameters is utilised to generate simulated data for various scenarios of large strip on-farm trials.
+The study employs GWR models to analyse the simulated data for two assumptions: a linear response and a quadratic response to the treatment effects.
 
-\zc{RESULTS: With the assumption of linear response, the difference between a systematic design and a randomised design is not significant regardless of the presence of spatial variation.
+RESULTS: With the assumption of linear response, the difference between a systematic design and a randomised design is not significant regardless of the presence of spatial variation.
 However, with the assumption of quadratic response, a systematic design is superior to a randomised design concerning the lower mean squared errors (MSE) by GWR.
-}
 
-\zc{CONCLUSIONS: The findings highlight the superiority of systematic designs for producing smooth maps of optimal input levels and the impact of spatial variation on the performance of quadratic models in strip trials.
+CONCLUSIONS: The findings highlight the superiority of systematic designs for producing smooth maps of optimal input levels and the impact of spatial variation on the performance of quadratic models in strip trials.
 Additionally, the study recommends fixed bandwidths based on experimental designs for GWR models.
-For a large strip trial to create a varying treatment map, a systemic design should be used as it has more flexibility in post-experiment statistical modelling.}
+For a large strip trial to create a varying treatment map, a systemic design should be used as it has more flexibility in post-experiment statistical modelling.
 
-\zc{IMPLICATIONS OR SIGNIFICANCE: The findings offer practical recommendations for designing large strip trials.
-By drawing attention to the considerations, especially regarding the experiment's purpose, this research contributes valuable insights for improving the efficacy and planning of future large strip trials.}
+IMPLICATIONS OR SIGNIFICANCE: The findings offer practical recommendations for designing large strip trials.
+By drawing attention to the considerations, especially regarding the experiment's purpose, this research contributes valuable insights for improving the efficacy and planning of future large strip trials.
 
+% Context: While randomised designs are commonly preferred by agronomists and biometricians, the choice of design in on-farm trials often hinges on the experiment's objective.
+For instance, when creating a prescription map of continuous inputs across a grid in large strip trials, a systematic design may be more advantageous, although it typically receives less focus and discussion.
+
+% Objective: This study evaluates the efficacy of systematic designs when combined with Geographically Weighted Regression (GWR) models in addressing spatial variation and estimating continuous treatment effects in large strip trials, using numeric simulations.
+
+% Methods: We employed a Bayesian hierarchical model featuring spatially correlated random parameters to simulate data for various scenarios in large strip on-farm trials.
+The simulated data were then analysed using GWR models under two assumptions: linear and quadratic responses to treatment effects.
+
+% Results: The results indicated that under a linear response assumption, the performance difference between systematic and randomised designs is negligible, regardless of spatial variation.
+However, for a quadratic response, the systematic design demonstrates superiority over randomised designs, evidenced by lower mean squared errors (MSE) on the model coefficients in GWR.
+
+% Conclusions: Our findings underscore the effectiveness of systematic designs in generating smooth maps of optimal input levels and illustrate the influence of spatial variation on the performance of quadratic models in strip trials.
+The study also suggests adopting fixed bandwidths in GWR models based on the experimental design.
+For large strip trials aimed at creating a variable treatment map, a systematic design is recommended due to its greater flexibility in post-experimental statistical modelling.
+
+% Implications: This research provides practical guidelines for the design of large strip trials, emphasising the importance of aligning the design with the experiment's objectives.
+It contributes valuable insights for enhancing the effectiveness and strategic planning of future large strip trials.
 \end{abstract}

### 2024-07-29 MSforSubmission/main_revision_col.tex
Re-organise files. MS for submission

--- 2024-07-18 main_revision_col.tex
@@
 
-METHODS: A Bayesian hierarchical model with spatially correlated random parameters is utilised to generate simulated data for various scenarios of large strip on-farm trials.
-The study employs GWR models to analyse the simulated data for two assumptions: a linear response and a quadratic response to the treatment effects.
+METHODS: A hierarchical model with spatially correlated random parameters is utilised to generate simulated data for various scenarios of large strip on-farm trials.
+The study employs GWR models to analyse the simulated data for two assumptions: a linear response and a quadratic response \revision{of yield} to the treatment effects.
 
@@
 Additionally, \textcolor{red}{we recommend selecting} fixed bandwidths \revision{in GWR analysis} based on \revision{the plot configurations used in} experimental designs.
-For a large strip trial, to \revision{allocate continuously varying treatments in strips}, a systemic design should be used as it \revision{allows us to obtain accurate treatment effects} in post-experiment statistical modelling.
+For a large strip trial, to \revision{produce estimates of spatially-varying treatment effects across strips}, a systemic design should be used as it \revision{allows us to obtain better estimates than those obtained from a randomised design} in post-experiment statistical modelling.
 
@@
 
-The principles of randomisation were first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
-Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design (CRD), as \revision{it is} the most straightforward \revision{and} least restrictive experimental design.
+The principle of randomisation was first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
+Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design (CRD), \zc{where treatments are randomly allocated in each replicate}.
 More complex designs, such as the randomised complete block design (RCBD), the split-plot design, the strip-plot design and the Latin square design, are also widely used in agricultural experiments \revision{to improve the precision of treatment effect estimates} \parencite{Petersen1994Agricultural}.
-\revision{With the primary aim of obtaining unbiased estimates of global treatment effects}, randomised designs are routinely used for on-farm strip trials, \revision{whereas} systematic designs are rarely used.
+\revision{With the primary aim of obtaining unbiased estimates of global treatment effects}, randomised designs \zc{, which use different layouts of treatments in each replicate,} are routinely used for on-farm strip trials, \revision{whereas} systematic designs, \zc{which use the same layout of treatments in all replicates,} are rarely used.
 
@@
 While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of OFE shifts from the conventional analysis.
-In the application of precision agriculture (PA) \revision{using} variable rate applicators (VRA) \revision{,} a prescription map of the experiment \st{before the start of the operation} \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}.
+In the application of precision agriculture (PA) \revision{using} variable rate applicators (VRA)\revision{,} a prescription map of the experiment \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}.
 Therefore, in this scenario, the goal of OFE becomes obtaining a smooth \revision{spatial} map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
@@
 
-Analysing a systematic design for the creation of an optimal treatment map for OFE is a statistically challenging task.
-\revision{The true responses} at each point on the grid \revision{corresponding to all the treatment rates are} unknown, and the treatment \revision{producing the optimum response} varies continuously across the field.
-\textcite{Cao2022Bayesian} implemented a Bayesian approach using spatially correlated random parameters for \revision{analysing} large systematic strip trials, assuming a quadratic response model with both global and local \revision{(}spatially-varying\revision{)} components.
+Analysing a systematic design for the creation of an optimal treatment map is a statistically challenging task.
+\revision{The true responses} at each point on the grid \revision{corresponding to all the treatment rates are} unknown, and the treatment \revision{producing the optimum response may vary} continuously across the field.
+\textcite{Cao2022Bayesian} implemented a Bayesian approach with spatially correlated random parameters for \revision{analysing} large systematic strip trials.
+\revision{These authors considered} a quadratic response model with both global and local \revision{(}spatially-varying\revision{)} components.
 However, Bayesian \revision{analysis can be computationally expensive} and \revision{would require at least} preliminary knowledge of Bayesian \revision{inference to interpret the results, which can be extremely demanding} for farmers and agronomists.
-Alternatively, \textcite{Rakshit2020Novel} adopt a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE.
-Additionally, \textcite{Evans2020Assessment} conclude through simulation studies that GWR is capable of accurately separating variation \revision{in yield response due to treatment from} \revision{the variation that} is not due to the applied treatment.
+Alternatively, \textcite{Rakshit2020Novel} adopted a local regression approach, called geographically weighted regression (GWR), to obtain spatially-varying estimates of treatment effects for OFE.
+Additionally, \textcite{Evans2020Assessment} concluded through simulation studies that GWR is capable of accurately separating variation \revision{in yield response due to treatment from} \revision{the variation that} is not due to the applied treatment.
 However, their study was limited by the use of a randomised design and the assumption of a linear response \revision{model}.
-\textcite{Alesso2021Design} simulated corn yield with four nitrogen levels, assigned systematically and randomly in the chessboard designs, and \revision{estimated the regression} coefficients using GWR.
+\revision{To compare between the systematic and randomised treatment allocation in the chessboard design,} \textcite{Alesso2021Design} simulated corn yield \revision{response} \revision{for} four nitrogen levels and \revision{estimated the regression} coefficients using GWR.
 They concluded that systematic designs achieved the best results in most cases.
-However, the use of chessboard design presents a problem: harvesters can smooth over abrupt treatment changes between plots, potentially leading to misleading results unless there are constraints \revision{in} the field \parencite{Pringle2004FieldScale} \textcolor{green}{SR: This line does not make sense to me.
-We need to clarify}.
-Additionally, the quadratic or plateau feature \revision{in a response model} was not considered in the simulation study.
+However, the use of chessboard design \revision{often presents several challenges, particularly during harvesting.
+Harvesters can produce erroneous data due to the abrupt treatment changes between plots} \parencite{Pringle2004FieldScale}.
+Additionally, the quadratic or plateau feature \revision{in a response model} was not considered in their simulation study.
 
@@
 
-\textcite{Piepho2018Tutorial} demonstrate an example \revision{where} a linear model \revision{turns out to be inadequate} \revision{for analysing} sugar beet data \parencite{Petersen1994Agricultural}.
-\textcite{Glynn2007} show that many curves exist beyond a linear trend for nutrient-response relationships.
+\textcite{Piepho2018Tutorial} presented an example \revision{where} a linear model \revision{turns out to be inadequate} \revision{for analysing} sugar beet data \parencite{Petersen1994Agricultural}.
+\textcite{Glynn2007} showed that many curves exist beyond a linear trend for nutrient-response relationships.
 The \revision{response} curve \revision{often} depends on the availability of other macro and micronutrients in the soil \parencite{Marschner2011}, \revision{which means } that a linear relationship is unlikely to be consistent across a large trial.
@@
 
-Our study uses \revision{simulated} examples to demonstrate that randomisation is not essential for large strip trials.
+% Our study uses \revision{simulated} examples to demonstrate that randomisation is not essential for large strip trials.
 For the purpose of obtaining a treatment \revision{prescription} map, a systematic design is superior to a randomised design \revision{in most applications}.
-We also test the power of GWR to determine if it can successfully estimate spatially varying treatment effects for both linear and quadratic responses.
-Our results show that the bandwidth \revision{selected using the popular method of corrected Akaike Information Criterion} (AICc) \revision{does not provide the optimal bandwidth} for \revision{analysing large strip trials using} GWR.
+We also test the power of GWR to determine if it can successfully estimate spatially varying treatment effects for both linear and quadratic responses \revision{in a few scenarios, for example, different spatial variation structures}.
+% % Our results show that the bandwidth \revision{selected using the popular method of corrected Akaike Information Criterion} (AICc) \revision{does not provide the optimal bandwidth} for \revision{analysing large strip trials using} GWR.
 Instead, a fixed bandwidth \revision{is recommended} based on \revision{the plot configurations used in} the experimental design.
 
-The structure of the paper is organised as follows: In Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and \revision{introduce} the GWR model \revision{used in analysing} OFE data.
+% The structure of the paper is organised as follows: In Section \ref{Sec:Meth}, we describe the statistical model for generating simulated data, which has spatially varying coefficients of treatments, and \revision{introduce} the GWR model \revision{used in analysing} OFE data.
 In Section \ref{Sec:Simu}, we generate simulated data for \revision{several scenarios, where each scenario is constructed by choosing one component at a time from the} following \revision{four categories}: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) \revision{model coefficients with} low and high correlations; and (iv) spatial \revision{variance-covariance matrix} among grids \revision{given by} identity (no spatial trend), $\AR\otimes\AR$, and \Matern forms.
@@
 
+\revision{In this study}, we generate simulated data for \revision{several scenarios, where each scenario is constructed by choosing one component at a time from the} following \revision{four categories}: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) \revision{model coefficients with} low and high correlations; and (iv) spatial \revision{variance-covariance matrix} among grids \revision{given by} identity (no spatial trend), $\AR\otimes\AR$, and \Matern forms.
+\zc{We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}
+%\revision{We would like to test the power of GWR to determine if it can successfully estimate spatially varying treatment effects for these scenarios.}
+
+\revision{The GWR model in this paper is implemented with the \R-package \texttt{GWmodel} \parencite{lu2014gwmodel, Gollini2015GWmodel}.}
+
 \section{Methods}\label{Sec:Meth}
 
-\textcolor{green}{delete this paragraph??} This section describes the statistical model used in the simulation study.
+% \textcolor{green}{delete this paragraph??} This section describes the statistical model used in the simulation study.
 It outlines the basic model (S\st{ubs}ection~\ref{sec:basic})\revision{,} followed by the methodology for the spatially correlated treatment parameters (S\st{ubs}ection~\ref{sec:spatial}), and finally GWR (S\st{ubs}ection~\ref{sec:gwr}).
@@
 \end{equation}
-where: $x_1,\ldots, x_l$ denote $l$ fixed effects and $z_1,\ldots, z_k$ denote $k$ random effects; $b_m$ and $u_j(s)$ are the coefficients for the fixed and random terms, respectively; $\bm{u}_i$ is a vector of all random effects at \revision{the $i$-th plot,} %\in\mathcal{S}$ \revision{you need to define $\mathcal{S}$ in the previous section; in general just be careful of using any notation that you have not defined in the paper.
+where $x_1,\ldots, x_l$ are $l$ fixed effects; $z_1,\ldots, z_k$ are $k$ random effects; $b_m$ and $u_j(s)$ are the coefficients for the fixed and random terms, respectively; $\bm{u}_i$ is a vector of all random effects at \revision{the $i$-th plot,} %\in\mathcal{S}$ \revision{you need to define $\mathcal{S}$ in the previous section; in general just be careful of using any notation that you have not defined in the paper.
 It's okay to say we are borrowing notation from your previous paper, but it's a must that we define them here as well.
@@
 
-In model \eqref{eq:underlying}, the structure of the covariance matrix $V_u(\theta_u)$ of $\bm{u}_i$ can be either diagonal, which implies the treatments at grid $i$ are independent, or in general form, which means a correlation exists.
-\textcite{McElreath2015Statistical} suggest that the covariance \revision{$V_u$} of $\bm{u}_i$ can be \revision{decomposed into $B(\sigma_u)R_uB(\sigma_u)$}, where $B(\sigma_u)$ denotes the diagonal matrix of elements $\sigma_{u_j}$, $j=1,\ldots,k$.
-For the matrix $R_u$ with correlation coefficients, we specify the Lewandowski-Kurowicka-Joe (LKJ) distribution \parencite{Lewandowski2009Generating}, which is given by
+In model \eqref{eq:underlying}, the structure of the covariance matrix $V_u(\theta_u)$ of $\bm{u}_i$ can be either diagonal, which implies the \revision{random terms} at grid $i$ are independent, or in general form, which means a correlation exists.
+\textcite{McElreath2015Statistical} suggested that the covariance matrix \revision{$V_u$} can be \revision{decomposed into $B(\sigma_u)R_uB(\sigma_u)$}, where $B(\sigma_u)$ denotes the diagonal matrix with diagonal elements $\sigma_{u_j}$, $j=1,\ldots,k$, and $R_u$ denotes the matrix with correlation coefficients.
+For the matrix $R_u$, we specify the Lewandowski-Kurowicka-Joe (LKJ) distribution \parencite{Lewandowski2009Generating}, which is given by
 \begin{equation}\label{eq:RPrior}
@@
 In fact, $V_s$ is the covariance matrix of all grids on the field.
-For example, if $V_s=I_{n\times n}$ is an identity matrix, each grid is independent even though the treatments within each grid are correlated.
+For example, if $V_s=I_{n\times n}$ (an identity matrix), \revision{the random terms at a grid point are independently distributed from those at other grid points,} even though the \revision{terms at that grid point are correlated amongst each other}.
 However, the correlation among grids is ubiquitous.
-Hence, we introduce a simple spatial covariance matrix such that
+Hence, we introduce a simple spatial covariance matrix such as
 \begin{equation}\label{eq:ar1cov}
@@
 \end{equation}
-where AR1 is the separable first-order auto-regressive model in the column and row direction which is controlled by the correlation parameters $\rho_c$ and $\rho_r$, respectively \parencite{Butler2017ASRemlR}.
+where \revision{$\AR \otimes \AR$} is the separable first-order auto-regressive model in the column and row directions, controlled by the correlation parameters $\rho_c$ and $\rho_r$, respectively \parencite{Butler2017ASRemlR}.
 
-Besides the above $\AR\otimes\AR$ covariance, the \Matern class covariance  
+\revision{On the other hand}, the \Matern class covariance \revision{is given by}
 \begin{equation}\label{eq:matcov}
-V_s(d) = \sigma^2 \frac{2^{1-\nu}}{\Gamma(\nu)} \left( \sqrt{2\nu} \frac{d}{r}\right)^\nu K_\nu\left( \sqrt{2\nu} \frac{d}{r}\right)
+V_s(d) = \sigma^2 \frac{2^{1-\nu}}{\Gamma(\nu)} \left( \sqrt{2\nu} \frac{d}{\zc{\gamma}}\right)^\nu K_\nu\left( \sqrt{2\nu} \frac{d}{\zc{\gamma}}\right),
 \end{equation}
-is also used in spatial analysis \parencite{Cressie1999Classes} and in capturing spatial variation in OFE \parencite{Selle2019Flexible}.
-Here, $d$ is the space lag or distance; $r$ is a non-negative scaling parameter; $\nu> 0$ is a smoothness parameter determining the mean-square differentiability of the field; $\sigma_d^2$ is the variance of the process; $\Gamma$ is the Gamma function; and $K_\nu$ is the modified Bessel function of the second kind.
-If $\nu = r + 1/2$, then the \Matern covariance can be expressed as a product of an exponential and a polynomial of order $r$ \parencite{Pandit2019Comparative, Abramowitz1974Handbook}, which simplifies the model and the computation process.
-The \Matern \revision{models} \revision{with the values $3/2$ and $5/2$ for $\nu$} are common\revision{ly used} in \revision{most} application\revision{s}.
+ where $d$ is the space lag or distance; $\zc{\gamma}$ is a non-negative scaling parameter; $\nu> 0$ is a smoothness parameter; \revision{$\sigma^2$ is the variance parameter}; $\Gamma$ is the Gamma function; and $K_\nu$ is the modified Bessel function of the second kind.
+\revision{The \Matern covariance} is commonly used in the analysis \revision{of geostatistical data} \parencite{Cressie1999Classes}.
+\revision{Moreover, it has also been used} in capturing spatial variation in OFE \parencite{Selle2019Flexible}.
+If $\nu = \zc{\gamma} + 1/2$, then the \Matern covariance can be expressed as a product of an exponential and a polynomial of order $\zc{\gamma}$ \parencite{Pandit2019Comparative, Abramowitz1974Handbook}, which simplifies the model and the computation process.
+The \Matern \revision{models} \revision{with the values $3/2$ and $5/2$ for $\nu$} are \revision{used} in \revision{most} application\revision{s}.
 
-\revision{Using the above formulas and pre-defined parameters, we can generate simulated data for the study.}
+\zc{In each iteration of the simulation process, we used the above formulae and pre-defined parameter values to generate $2\times n$ coefficients for the linear response and $3\times n$ coefficients for the quadratic response.
+Then these coefficients are applied to simulate yield response across strips for both  randomised and systematic design layouts.}
 
@@
 \end{equation}
-where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ and $\varepsilon_{i} \sim \N(0,\tau^2)$ are the model parameters for the $k$ treatment\st{s} \revision{levels} and error terms, respectively, at grid $i,\ i=1,\ldots,n$.
+where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ and $\varepsilon_{i} \sim \N(0,\tau^2)$ are the model parameters for the $k$ treatment \revision{levels} and error terms, respectively, at grid $i,\ i=1,\ldots,n$.
 
@@
 \end{eqnarray}
-where $W(s)$ is an $n\times n$ diagonal matrix of weights\st{, $\bm{w}$} \revision{with $i$th diagonal entry $K(s,s_i)$}.
+where $W(s)$ is an $n\times n$ diagonal matrix of weights \revision{with $i$-th diagonal entry $K(s,s_i)$}.
 
@@
 In fact, the kernel \revision{function} is not the crucial factor in the GWR \revision{analysis}.
-\revision{In} contrast, the bandwidth has a higher influence on the estimation.
+\revision{In} contrast, the bandwidth has a higher influence on estimation.
 
@@
 
-The GWR model in this paper is implemented with the \R-package \texttt{GWmodel} \parencite{lu2014gwmodel, Gollini2015GWmodel}.
+%% The GWR model in this paper is implemented with the \R-package \texttt{GWmodel} \parencite{lu2014gwmodel, Gollini2015GWmodel}.
+
+\subsection{\revision{Performance evaluation}}
+
+\zc{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates.} \revision{The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model \eqref{eq:underlying}, and the spatially varying estimates of that coefficient produced by GWR \eqref{eq:basicgwr}, and then averaging these squared differences across all the grid points.
+The lower the MSE, the better the design's performance.} \zc{The advantage of the simulation study is that the actual coefficients of the models are known, so} \revision{possible} \zc{adverse effects of model misspecification can be} \revision{omitted while assessing the performances of different designs on parameter estimation} \parencite{Piepho2013Why}.
 
@@
 
-To \revision{compare} the \revision{performances between} randomised \st{designs} and systematic designs \revision{in terms of accurate estimation of the model coefficients} \revision{using} GWR, we simulate \revision{several scenarios of} spatially correlated large strip trials.
+% To \revision{compare} the \revision{performances between} randomised and systematic designs \revision{in terms of accurate estimation of the model coefficients} \revision{using} GWR, we simulate \revision{several scenarios of} spatially correlated large strip trials.
 The advantage of the simulation study is that the actual coefficients of the models are known, so adverse effects of model misspecification can be ruled out \parencite{Piepho2013Why}.
 
-We investigate the combination of the following factors: \revision{(i)} types of design with two levels, \revision{namely,} randomised and systematic; \revision{(ii)} response relationship with two levels, \revision{namely,} linear and quadratic; \revision{(iii)} correlation of coefficients \revision{of treatments within each plot} with two levels, \revision{namely,} low and high; \revision{(iv)} spatial variation \revision{between plots on the paddock} with three levels, \revision{namely,} identity (no spatial trend), $\AR\otimes\AR$, and \Matern form; \revision{(v)} GWR bandwidth with three value \revision{of} 5, 9 and the optimum \revision{value selected} by AICc.
-The fixed bandwidth \revision{of} 5 in the simulation study covers all treatment levels (five nitrogen levels) in a systematic design, where the information is adequate \revision{for} the inference \revision{based on} a quadratic \revision{response model}.
-Similarly, a fixed bandwidth of 9 is essential to cover all possible treatment levels in a randomised design.
-This necessity \revision{arises in} situations where treatments are randomly distributed across strips.
-In particular, if identical treatments are positioned at the far left edge of the first replicate block and the far right edge of the second replicate block, a bandwidth smaller than 9 would  \revision{result in} the GWR model capturing only the treatments between these boundaries, thereby missing the treatment level\revision{s} at the extremes.
+\revision{The simulation study is based on the real life data recorded from a corn field in Las Rosas, Argentina.
+This data set was originally provided by \textcite{Luc2004ASpatial} and can be accessed via the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
+In 2001, a systematic design was used, incorporating six rates of nitrogen: 0, 39, 50.6, 75.4, 99.8, and 124.6 kg/ha, in three replicates.
+Each replicate consists of 93 rows and 6 columns after data preprocessing; see \textcite{Rakshit2020Novel} for further details about the preprocessing steps.
+The unit of yield is quintals per hectare.}
 
-\revision{Using} model \eqref{eq:underlying}, we generate yield as a response to nitrogen treatment \revision{for} two scenarios that cover whether yield has a linear or quadratic relationship with the nitrogen rate.
-The nitrogen rates are treated as continuous observations with five levels: 0, 35, 75, 105, and 140 kg/ha.
-A strip plot structure was used to allocate the five nitrogen levels \revision{with} each level assigned to one strip.
-The experimental design of the trial consists of four replicates, each containing 5 columns by 93 rows.
-The nitrogen rates are allocated randomly or systematically  \revision{across the entire} field.
-The overall layout of the trial is 20 \revision{columns} by 93 rows.
-Examples of randomly and systematically allocated treatment map are presented in Figure \ref{fig:Nitrogen}.
+\revision{Studies by \textcite{Rakshit2020Novel, Cao2022Bayesian} suggest that the yield produced by the maximum nitrogen rate of 124.6 kg/ha may be improved by using a higher rate.
+Thus, we made some adjustments while selecting the nitrogen rates for our simulation study.
+We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.
+Additionally, we increased the number of replicates from three to four.
+Consequently, the final layout of the trial used in the simulation consisted of 93 rows and 20 columns.
+Examples of a randomised design, \zc{which uses different orders of treatment in each replicate}, and a systematic design, \zc{which uses the same order of treatment in all replicates}, for this layout are presented in Figure \ref{fig:Nitrogen}.}
 
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_RandNitro_V2.pdf}
+		\includegraphics[width=\linewidth]{Expt/Col_RandNitro_V4.pdf}
 		%\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
-        \caption{}\label{fig:RandNitrogen}
 	\end{subfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_SystNitro_V2.pdf}
+		\includegraphics[width=\linewidth]{Expt/Col_SystNitro_V4.pdf}
 		%\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
-        \caption{}\label{fig:SystNitrogen}
 	\end{subfigure}
-	\caption{\revision{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly \eqref{fig:RandNitrogen} and systematically \eqref{fig:SystNitrogen} allocated into strips in each replicate block.}}\label{fig:Nitrogen}
+	\caption{\revision{The nitrogen treatments with five levels (0, 35, 70, 105 and 140 kg/ha) randomly (\textit{left}) and systematically (\textit{right}) allocated into strips in each replicate block.}}\label{fig:Nitrogen}
 \end{figure}
 
-\revision{SR comment: For the above figure, please delete the sub captions.
-Moreover, try to use either column or range throughout the paper.
-I would suggest use the term column throughout the paper.
-There is no need to use the term range.
-If you like to do that, then do it consistently throughout the paper.
-If you decide to use the term column, then please change the y-axis titles of the figures.
-Finally, it would be better if you could increase the font size of the text used in the figures.}
+\zc{We investigate \revision{all possible} combination\revision{s} of the following factors}: \revision{(i)} types of design with two levels, \revision{namely,} randomised and systematic; \revision{(ii)} response relationship with two levels, \revision{namely,} linear and quadratic; \revision{(iii)} correlation coefficients \revision{corresponding to the random effects within each plot} with two levels, \revision{namely,} low and high; \revision{(iv)} spatial variation \revision{between grid points} with three levels, \revision{namely,} identity (no spatial trend), $\AR\otimes\AR$, and \Matern form.
+\zc{This results in \revision{24} unique combinations.
+For each combination, we simulated yield data and fitted the GWR model for three bandwidth values of 5, 9 and the optimum \revision{value selected} by AICc.} \revision{For a systematic design in our simulation study, all the treatment levels (five nitrogen levels) can be covered by the bandwidth of 5, making it adequate for inference based on a quadratic response model}.
+\revision{On the other hand}, the bandwidth of 9 \revision{may be necessary} to cover all possible treatment levels in a randomised design.
+In particular, if identical treatments are positioned at the far left edge of the first replicate block and \revision{at} the far right edge of the second replicate block, a bandwidth smaller than 9 would  \revision{result in} the GWR model capturing only the treatments between these boundaries, thereby missing the treatment level\revision{s} at the extremes.
 
-\revision{In} model \eqref{eq:underlying}, the nitrogen rates \revision{considered as the treatment factor} with \revision{the} five levels \revision{of 0, 35, 70, 105 and 140 kg/ha}.
-\revision{To specify a} linear relationship \revision{in the simulation study}, we \revision{consider the values of $65$ and $0.05$ for the} global intercept $b_0$ and slope $b_1$ coefficients, respectively.
-The\revision{se} parameters are chosen according to the estimates \revision{reported} by \textcite{Rakshit2020Novel, Cao2022Bayesian} \revision{for} the Las Rosas corn field data, which is initially provided by \textcite{Luc2004ASpatial} and \revision{can be accessed via} the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
-The unit of yield \revision{considered here} is quintals per hectare.
+\revision{To specify the} linear relationship \revision{in the simulation study}, we \revision{consider the values of $65$ and $0.05$ for the} global intercept $b_0$ and slope $b_1$ coefficients, respectively, \zc{in model \eqref{eq:underlying}}.
 The variances of \revision{the coefficients} $\bm{u}_i$ are \revision{set to $5$ for $\sigma_{u_0}$ and $0.01$ for $\sigma_{u_1}$}.
-For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters \revision{$\rho_c$ (in the column direction) and $\rho_r$ (in the row direction) are set to $0.15$ and $0.50$, respectively}.
-We \revision{assume} a higher correlation in the row \revision{direction because} the crop is traditionally sown and harvested along ranges\revision{,} \revision{and} the correlation is higher in the \revision{direction} perpendicular \revision{to the sowing} direction \parencite{Marchant2019Establishinga}.
+The\revision{se} parameters are chosen according to the estimates \revision{reported} by \textcite{Cao2022Bayesian}.
+For the $\AR\otimes\AR$ covariance matrix in \eqref{eq:ar1cov}, the two correlation parameters \revision{$\rho_c$ and $\rho_r$ are set to $0.15$ and $0.50$, respectively}.
+We \revision{assume} a higher correlation in the row \revision{direction because} the crop is traditionally sown and harvested along \revision{the column direction,} \revision{and} the correlation is higher in the \revision{direction} perpendicular \revision{to the sowing} direction \parencite{Marchant2019Establishinga}.
 For the \Matern covariance matrix \eqref{eq:matcov}, we set \revision{the value of the variance parameter $\sigma_d^2$ to $1$, the value of the parameter $r$ to $1$, and the value of the parameter $\nu$ to $3/2$}.
-After drawing samples of $\bm{u}$ from $\N(0,\Sigma_u)$, the true spatially varying coefficients \revision{$\bm{\beta}_0$ and $\bm{\beta}_1$ are specified using the relations} $\bm{\beta}_0 = b_0 + \bm{u}_0$ and $\bm{\beta}_1 = b_1 + \bm{u}_1$.
-\\
+After drawing samples of $\bm{u}$ from $\N(0,\Sigma_u)$, the spatially varying coefficients \revision{$\bm{\beta}_0$ and $\bm{\beta}_1$ are specified using the relations} $\bm{\beta}_0 = b_0 + \bm{u}_0$ and $\bm{\beta}_1 = b_1 + \bm{u}_1$.
 
-For the quadratic relationship, we \revision{consider}  $b_0 = 65$, $b_1 = 0.05$, and $b_2 = -0.0003$.
-\revision{These choices make the response} curve concave down.
-\revision{For the variance components,} we \revision{consider} $\sigma_{u_0} = 5$, $\sigma_{u_1}=0.01$, and $\sigma_{u_2}=0.0001$.
-The rest of the parameters remain unchanged.
-Therefore, the true spatially varying coefficients are $\bm{\beta}_0 = b_0 + \bm{u}_0$, $\bm{\beta}_1 = b_1 + \bm{u}_1$ and $\bm{\beta}_2 = b_2 + \bm{u}_2$.
+For the quadratic relationship, we \revision{consider the} \zc{values of $65$, $0.05$ and $-0.0003$ for the coefficients $b_0$, $b_1$, and $b_2$, respectively.} \revision{These choices make the response} curve concave down.
+\revision{For the variance components,} we \zc{set to $5$ for $\sigma_{u_0}$, $0.01$ for $\sigma_{u_1}$, and $0.0001$ for $\sigma_{u_2}$}.
+The rest of the parameters \revision{left} unchanged.
+\revision{Consequently}, the true spatially varying coefficients are $\bm{\beta}_0 = b_0 + \bm{u}_0$, $\bm{\beta}_1 = b_1 + \bm{u}_1$, and $\bm{\beta}_2 = b_2 + \bm{u}_2$ \zc{for the quadratic model}.
 
-The simulated yield \revision{response} is obtained by 
-\begin{equation}
-\begin{cases}
-	% \text{Linear}  &y_i = b_0 + b_1N_i + u_{0i} + u_{1i}N_i + e_i \\
-	\text{Linear}  &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + e_i \\
-	% \text{Quadratic} &y_i = b_0 + b_1N_i + b_2N_i^2 + u_{0i} + u_{1i}N_i  + u_{2i}N_i^2 + e_i
-	\text{Quadratic} &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + (b_2 + u_{2i})N_i^2 + e_i
-\end{cases}
-\end{equation}
-where $N_i$ is the nitrogen rate, $e_i\sim \N(0,1)$ is the error term at grid $i$, $i = 1, \ldots, n$.
-Figure \ref{fig:Lines} illustrates \revision{the yield response to Nitrogen} for the linear and quadratic relationships.
-
-\begin{figure}[!htp]
+Figure \ref{fig:Lines} illustrates \revision{the global yield response to Nitrogen} for the linear and quadratic relationships.
+\begin{figure}[H]
 	\begin{subfigure}[t]{0.45\textwidth}
@@
         \end{subfigure}
-	\caption{\revision{The linear relationship of yield and nitrogen (\textit{left}) is $y=65+0.05N$, and the quadratic relationship between yield and nitrogen (\textit{right}) is $y=65+0.05N-0.003N^2$.}}\label{fig:Lines}
+	\caption{\revision{The global linear relationship of yield and nitrogen is $y=65+0.05N$ (\textit{left}), and the global quadratic relationship between yield and nitrogen is $y=65+0.05N-0.003N^2$ (\textit{right}).}}\label{fig:Lines}
 \end{figure}
-% \revision{SR comment: remove the subcaptions from Figure~2. Include those details in the main caption.}
 
-% Examples of the yield maps with true $\AR\otimes\AR$ spatially varying coefficients are in Figures \ref{fig:LinearYieldMap} and \ref{fig:QuadYieldMap}. 
-% \begin{figure}[!htp]
-% 	\centering
-% 	\begin{subfigure}[t]{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/LinearRandYield01.pdf}
-% 		\caption{Yield map of the linear response of the randomised design. }
-% 	\end{subfigure}
-% 	\begin{subfigure}[t]{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/LinearSystYield01.pdf}
-% 		\caption{Yield map of the linear response of the systematic design. }
-% 	\end{subfigure}
-% 	\caption{Yield maps of linear response of randomly and systematically allocated nitrogen rates.}\label{fig:LinearYieldMap}
-% \end{figure}
-
-% \begin{figure}[!htp]
-% 	\centering
-% 	\begin{subfigure}[t]{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/QuadRandYield01.pdf}
-% 		\caption{Yield map of the quadratic response of the randomised design. }
-% 	\end{subfigure}
-% 	\begin{subfigure}[t]{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/QuadSystYield01.pdf}
-% 		\caption{Yield map of the quadratic response of the systematic design. }
-% 	\end{subfigure}
-% 	\caption{Yield maps of quadratic response of randomly and systematically allocated nitrogen rates.}\label{fig:QuadYieldMap}
-% \end{figure}
-
-%% To fit the data, we use basic GWR with Gaussian kernels.
-
-%\st{The purpose of the simulation study is to test the effect of different types of designs in coefficients estimation by GWR.
-Identical coefficients were used in one comparison process for two types of designs, and the yield reflects the effect of nitrogen rates.}
+\zc{To summarise, the} simulated yield \revision{response} is obtained by 
+\begin{equation}
+\begin{cases}
+	\text{Linear}  &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + e_i \\
+	\text{Quadratic} &y_i = b_0 + u_{0i} + (b_1 + u_{1i})N_i + (b_2 + u_{2i})N_i^2 + e_i
+\end{cases}
+\end{equation}
+where $N_i$ is the nitrogen rate, $e_i\sim \N(0,1)$ is the error term at grid $i$, $i = 1, \ldots, n$.
 
@@
 \revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models.
-To this end, we perform $100$ simulations of each scenario described in the previous section.} In Section~\ref{Sec:MSE}, the mean squared errors are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix.
+To this end, we perform 1\,000 simulations of each \revision{of the 24} scenarios\zc{, described} in the previous section.} \zc{In each simulation, we first generated the coefficients for all grids and then applied the treatment in each grid to calculate the yield value using the model coefficients.
+For the treatments in all grids, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design.
+For a randomised design, all replicates have different orders of the treatments.} In Section~\ref{Sec:MSE}, the mean squared errors are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix.
 Section~\ref{Sec:anova} uses \revision{the} analysis of variance (ANOVA) to  \revision{assess} the significance of the factors \revision{considered} in the simulation \revision{study}.
@@
 
-\revision{To assess the performance of different designs for a simulation scenario,} we \revision{computed the} mean squared error (MSE) \revision{corresponding to all} coefficient \revision{estimates}.
+% \revision{To assess the performance of different designs for a simulation scenario,} we \revision{computed the} mean squared error (MSE) \revision{corresponding to all} coefficient \revision{estimates}.
 This was \revision{computed} by \revision{taking} the difference of true coefficients $\bm{\beta}$ (i.e., $b + \bm{u}$) and the estimated spatially varying coefficients $\bm{\hat{\beta}}$ (i.e., $\hat{b} + \bm{\hat{u}}$) for each grid, and then \revision{averaging} the squared discrepancies across \revision{all the grid points in} the field.
-The results are shown in Figures \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE}, where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$), ``AR1'' for $\AR(0.15)\otimes \AR(0.5)$\revision{,} and ``Matern'' \revision{for} \Matern covariance with $\nu=\frac{3}{2}$.
-Since the MSEs \revision{corresponding to the estimation of} $\beta_0$, $\beta_1$, and $\beta_2$ are small, we take the natural logarithm \revision{of the MSE values} for better visualisation.
+
+\revision{Figures~\ref{fig:LinBetaMSE} and \ref{fig:LinBetaMSEeta01} show the results of linear models for the cases of low ($\epsilon = 1$) and high ($\epsilon = 0.1$) spatial correlations, respectively, while Figures~\ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show the results of quadratic models for the same low and high correlations, respectively.
+To specify the covariance matrix $V_s$ used in producing the results in these figures, we use the following labels: (i) ``NS'' for the identity matrix representing no spatial correlation, (ii) ``AR1'' for $\AR(0.15)\otimes \AR(0.5)$, and (iii) ``Matern'' for \Matern covariance with $\nu=3/2$.}
+
+% \st{The MSE results are shown in Figures} \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE}\st{, where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$),} \st{``AR1'' for $\AR(0.15)\otimes \AR(0.5)$, and ``Matern'' for} \Matern \st{covariance with $\nu=3/2$.
+Since the MSE  $\zc{\bm{\beta}}_0$, $\zc{\bm{\beta}}_1$, and $\zc{\bm{\beta}}_2$ are small, we take the natural logarithm for better visualisation.}
 
 % Paragraph about Figure 3 and the performance for a linear response
-\revision{For} a linear response, both randomised and systematic designs perform similarly\revision{, particularly for the cases NS and AR1.} Figure~\ref{fig:LinBetaMSE} shows that the MSEs \revision{corresponding to} $\hat{\beta}_0$ and $\hat{\beta}_1$ for all bandwidths \revision{are fairly similar for both} designs.
-\revision{However, the results in Table~1 show that the MSE medians corresponding to $\hat{\beta}_1$ for the Matern case are consistently lower for the systematic design.} This is true regardless of the type of spatial covariance matrix \revision{considered in a simulation}.
-\\
-\textcolor{green}{SR comment: I am not sure what's going on here}
-when the correlation within grids is small ($\epsilon=1$), or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
-The GWR with bandwidth selected by AICc has a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).
+\revision{For} a linear response, both randomised and systematic designs perform similarly\revision{, particularly for the cases NS and AR1.} Figure~\ref{fig:LinBetaMSE} shows that the MSEs \revision{corresponding to} $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ for all bandwidths \revision{are fairly similar for both} designs.
+\revision{However, the results in Table~1 show that the MSE medians corresponding to $\zc{\hat{\bm{\beta}}}_1$ for the \Matern case are consistently lower for the systematic design.}
+This is true regardless of \revision{the correlation within grids considered in a simulation}, small ($\epsilon=1$) or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
+%% The GWR with bandwidth selected by AICc has a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
+	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_V3.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
 The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation between the parameters ($\epsilon=1$).}\label{fig:LinBetaMSE}
+\end{figure}
+
+\begin{figure}[!thp]
+	\centering
+	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_eta01_V3.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
+The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation between the parameters ($\epsilon=0.1$).}\label{fig:LinBetaMSEeta01}
 \end{figure}
@@
 However, if the assumption is a quadratic response, Figures \ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show that the GWR with a fixed bandwidth of a systematic design outperforms a randomised design if the spatial correlation is taken into account.
-With the optimal bandwidth, GWR successfully estimates the global intercepts $\beta_0$ but failed in estimating local varying coefficients $\beta_1$ and $\beta_2$, where the MSE is relatively larger than with fixed bandwidth.
+With the optimal bandwidth, GWR successfully estimates the global intercepts $\zc{\bm{\beta}}_0$ but failed in estimating local varying coefficients $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, where the MSE is relatively larger than with fixed bandwidth.
 However, if we only compare across two types of designs, it still proves that GWR is robust to fit a systematic design rather than a randomised design if the assumption is a quadratic response, regardless of the intensity of the correlation within grids.
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
+	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_V3.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$, $\zc{\hat{\bm{\beta}}}_1$ and $\zc{\hat{\bm{\beta}}}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
 The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation amongst the parameters ($\epsilon=1$).} \label{fig:QuadBetaMSE}
@@
 
+\begin{figure}[!thp]
+	\centering
+	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_eta01_V3.pdf}
+	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$, $\zc{\hat{\bm{\beta}}}_1$ and $\zc{\hat{\bm{\beta}}}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
+The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation amongst the parameters ($\epsilon=0.1$).} \label{fig:QuadBetaMSEeta01}
+\end{figure}
 % Bandwidth MSE Result
@@
 MSE analyses revealed that the choice of bandwidth significantly influenced the relative performance based on both the spatial covariance matrix and the coefficient characteristics.
-In scenarios without spatial variation for $\beta_1$ and $\beta_2$, the AICc-selected bandwidth demonstrated the lowest MSE, followed by fixed bandwidths of 9 and 5, respectively.
-However, when the spatial variation was present (utilising either AR1$\otimes$AR1 or \Matern covariance structures), the bandwidth of 9 consistently produced the most accurate estimations for $\beta_1$ and $\beta_2$, outperforming the bandwidths of 5 and the one chosen by AICc.
-Notably, for the intercept ($\beta_0$), significant changes in MSE amongst the bandwidths were observed only in the context of the \Matern spatial covariance.
+In scenarios without spatial variation for $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, the AICc-selected bandwidth demonstrated the lowest MSE, followed by fixed bandwidths of 9 and 5, respectively.
+However, when the spatial variation was present (utilising either AR1$\otimes$AR1 or \Matern covariance structures), the bandwidth of 9 consistently produced the most accurate estimations for $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, outperforming the bandwidths of 5 and the one chosen by AICc.
+Notably, for the intercept ($\zc{\bm{\beta}}_0$), significant changes in MSE amongst the bandwidths were observed only in the context of the \Matern spatial covariance.
 Here, the bandwidth selected by AICc resulted in the smallest MSE, highlighting its efficacy when dealing with spatially correlated residuals following the \Matern covariance structure.
 
-Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} are the median MSEs of the linear response for two scenarios: the correlation is low and the correlation is high.
+Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} are the median MSE of the linear response for two scenarios: the correlation is low and the correlation is high.
+
+% \begin{table}[!htp]
+% 	\centering
+% \begin{threeparttable}
+% 	\caption{Median MSE of GWR coefficient estimates for a linear response when the correlation between the parameters is low ($\epsilon=1$).}\label{tb:MSElinear_old}
+% 	\begin{tabular}{llcccccc}
+% 		\toprule
+% 		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
+%    		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
+% 		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.903 &	24.924 &	24.983&	24.886\tnote{$\dagger$} &	24.911 &	24.965 \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.147&	0.118&	0.105&	0.147&	0.117&	0.104\tnote{$\dagger$}  \\  \midrule
+% 		\multirow{2}{*}{AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.308&	24.617&	24.126&	24.319&	24.617&	23.246\tnote{$\dagger$}  \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.215	&0.147	&1.208&	0.214&	0.146\tnote{$\dagger$}	&1.143 \\ \midrule
+% 		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.303	&23.566	&9.647&	21.164&	23.526&	9.239\tnote{$\dagger$} \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.157	&0.121&	0.845&	0.138&	0.115\tnote{$\dagger$} &	0.749 \\
+% 		\bottomrule
+% 	\end{tabular}
+% 	\begin{tablenotes}
+% 	\item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
+% 	\end{tablenotes}
+% \end{threeparttable}
+% \end{table}
 
@@
    		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
-		\multirow{2}{*}{NS}   & $\hat{\beta}_0$ & 24.903 &	24.924 &	24.983&	24.886\tnote{$\dagger$} &	24.911 &	24.965 \\ 
-		& $\hat{\beta}_1 (\times 10^3)$ & 0.147&	0.118&	0.105&	0.147&	0.117&	0.104\tnote{$\dagger$}  \\  \midrule
-		\multirow{2}{*}{AR1}  & $\hat{\beta}_0$ & 24.308&	24.617&	24.126&	24.319&	24.617&	23.246\tnote{$\dagger$}  \\ 
-		& $\hat{\beta}_1 (\times 10^3)$ & 0.215	&0.147	&1.208&	0.214&	0.146\tnote{$\dagger$}	&1.143 \\ \midrule
-		\multirow{2}{*}{\Matern} & $\hat{\beta}_0$ & 21.303	&23.566	&9.647&	21.164&	23.526&	9.239\tnote{$\dagger$} \\ 
-		& $\hat{\beta}_1 (\times 10^3)$ & 0.157	&0.121&	0.845&	0.138&	0.115\tnote{$\dagger$} &	0.749 \\
+		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.852 &	24.933 &	24.912&	24.781\tnote{$\dagger$} &	24.850 &	24.861 \\ 
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.683 &	1.341 &	1.398 &	1.615 &	1.320\tnote{$\dagger$} &	1.361 \\  \midrule
+		\multirow{2}{*}{AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.401 &	24.649 &	23.695 &	24.295 &	24.684 &	23.118\tnote{$\dagger$} \\ 
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.489 &	1.790 &	10.071 &	2.441 &	1.740\tnote{$\dagger$} &	9.995 \\ \midrule
+		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.482 &	22.432 &	9.801 &	20.319 &	22.194 &	9.280\tnote{$\dagger$} \\ 
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.683 &	1.378 &	8.049 &	1.398 &	1.197\tnote{$\dagger$} &	7.022 \\
 		\bottomrule
@@
 \end{table}
+
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{rrrrrrr}
+%   \hline
+%  & X1 & X2 & X3 & X4 & X5 & X6 \\ 
+%   \hline
+% 1 & 24.852 & 24.933 & 24.912 & 24.781 & 24.850 & 24.861 \\ 
+%   2 & 1.683 & 1.341 & 1.398 & 1.615 & 1.320 & 1.361 \\ 
+%   3 & 24.401 & 24.649 & 23.695 & 24.295 & 24.684 & 23.118 \\ 
+%   4 & 2.489 & 1.790 & 10.071 & 2.441 & 1.740 & 9.995 \\ 
+%   5 & 20.482 & 22.432 & 9.801 & 20.319 & 22.194 & 9.280 \\ 
+%   6 & 1.683 & 1.378 & 8.049 & 1.398 & 1.197 & 7.022 \\ 
+%    \hline
+% \end{tabular}
+% \end{table}
+
+% \begin{table}[!htp]
+% 	\centering
+% \begin{threeparttable}
+% 	\caption{Median MSE of GWR coefficient estimates of linear response when the correlation between the parameters is high ($\epsilon=0.1$).}\label{tb:MSElinearHigh}
+% 	\begin{tabular}{llcccccc}
+% 		\toprule
+% 		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
+% 		& Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
+% 		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$  & 24.961	&24.991	&24.958	&24.934\tnote{$\dagger$}	&24.992	&25.020 \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.144&	0.115&	0.103\tnote{$\dagger$} &	0.145&	0.116&	0.104 \\ \midrule
+% 		\multirow{2}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$  & 24.234&	24.518&	23.696&	24.171	&24.497&	23.421\tnote{$\dagger$}  \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$   & 0.216	&0.144\tnote{$\dagger$} &	1.024&	0.211&	0.146&	1.027 \\ \midrule
+% 		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$  & 20.882&	22.811&	9.823&	20.770	&22.789	&9.257\tnote{$\dagger$}  \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$  & 0.152&	0.120&	0.939&	0.140&	0.112\tnote{$\dagger$} &	0.815 \\ 
+% 		\bottomrule
+% 	\end{tabular}
+% 		\begin{tablenotes}
+% 	\item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
+% 	\end{tablenotes}
+% \end{threeparttable}
+% \end{table}
 
@@
    		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
-		\multirow{2}{*}{NS}   & $\hat{\beta}_0$  & 24.961	&24.991	&24.958	&24.934\tnote{$\dagger$}	&24.992	&25.020 \\
-		& $\hat{\beta}_1 (\times 10^3)$ & 0.144&	0.115&	0.103\tnote{$\dagger$} &	0.145&	0.116&	0.104 \\ \midrule
-		\multirow{2}{*}{AR1$\otimes$AR1}  & $\hat{\beta}_0$  & 24.234&	24.518&	23.696&	24.171	&24.497&	23.421\tnote{$\dagger$}  \\
-		& $\hat{\beta}_1 (\times 10^3)$   & 0.216	&0.144\tnote{$\dagger$} &	1.024&	0.211&	0.146&	1.027 \\ \midrule
-		\multirow{2}{*}{\Matern} & $\hat{\beta}_0$  & 20.882&	22.811&	9.823&	20.770	&22.789	&9.257\tnote{$\dagger$}  \\
-		& $\hat{\beta}_1 (\times 10^3)$  & 0.152&	0.120&	0.939&	0.140&	0.112\tnote{$\dagger$} &	0.815 \\ 
+		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.808 &	24.925 &	24.927&	24.761\tnote{$\dagger$}  &	24.824 &	24.837 \\ 
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.623 &	1.334 &	1.382 &	1.590 &	1.304\tnote{$\dagger$}  &	1.352 \\  \midrule
+		\multirow{2}{*}{AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.379 &	24.690 &	23.650 &	24.321\tnote{$\dagger$}  &	24.633 &	23.416 \\ 
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.343 &	1.683\tnote{$\dagger$}  &	9.889 &	2.372 &	1.691 &	9.409 \\ \midrule
+		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.221 &	21.835 &	9.852 &	19.863 &	21.667 &	9.383\tnote{$\dagger$}  \\ 
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.731 &	1.390 &	8.109 &	1.422 &	1.204\tnote{$\dagger$}  &	7.013 \\
 		\bottomrule
@@
 
-% \vspace{12pt}
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{rrrrrrr}
+%   \hline
+%  & X1 & X2 & X3 & X4 & X5 & X6 \\ 
+%   \hline
+% 1 & 24.808 & 24.925 & 24.927 & 24.761 & 24.824 & 24.837 \\ 
+%   2 & 1.623 & 1.334 & 1.382 & 1.590 & 1.304 & 1.352 \\ 
+%   3 & 24.379 & 24.690 & 23.650 & 24.321 & 24.633 & 23.416 \\ 
+%   4 & 2.343 & 1.683 & 9.889 & 2.372 & 1.691 & 9.409 \\ 
+%   5 & 20.221 & 21.835 & 9.852 & 19.863 & 21.667 & 9.383 \\ 
+%   6 & 1.731 & 1.390 & 8.109 & 1.422 & 1.204 & 7.013 \\ 
+%    \hline
+% \end{tabular}
+% \end{table}
 
@@
 Despite the intensity of the correlation, the data fitted by GWR from systematic designs are superior to randomised designs, in terms of having a lower MSE.
+
+% \begin{table}[!htp]
+% 	\centering
+% \begin{threeparttable}
+% 	\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is low ($\epsilon=1$).}\label{tb:MSEquadratic_old}
+% 	\begin{tabular}{llcccccc} \toprule
+% 		 &  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
+% 		  & Coefficient & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+% 		\multirow{3}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 25.218 & 25.150 & 25.152  & 25.263 & 25.179 & 25.138\tnote{$\dagger$}  \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 7.417  & 3.823  & 1.625 & 7.233  & 3.529  & 1.516\tnote{$\dagger$}  \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 4.157  & 2.168  & 1.242\tnote{$\dagger$} & 4.135  & 2.269  & 1.269   \\ \midrule 
+% 		\multirow{3}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$  & 25.185 & 25.092\tnote{$\dagger$} & 30.315  & 25.166 & 25.230 & 27.831  \\
+% 		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 18.395 & 7.414  & 151.595 & 16.243 & 7.124\tnote{$\dagger$}  & 123.181  \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 9.491  & 4.244  & 74.420  & 8.305  & 3.777\tnote{$\dagger$}  & 61.619 \\ \midrule
+% 		\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$  & 21.532 & 23.502 & 17.680  & 21.384 & 23.319 & 15.631\tnote{$\dagger$} \\
+% 		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 9.502  & 4.326  & 112.914 & 6.121  & 2.901\tnote{$\dagger$}  & 96.829  \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.071  & 2.537  & 56.789  & 3.324  & 1.889\tnote{$\dagger$}  & 44.707 \\ \bottomrule
+% 	\end{tabular}
+% 	    \begin{tablenotes}
+% 	        \item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
+% 	    \end{tablenotes}
+% \end{threeparttable}
+% \end{table}
 
@@
  & Coefficient & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule 
-		\multirow{3}{*}{NS}   & $\hat{\beta}_0$ & 25.218 & 25.150 & 25.152  & 25.263 & 25.179 & 25.138\tnote{$\dagger$}  \\
-		& $\hat{\beta}_1 (\times 10^4)$ & 7.417  & 3.823  & 1.625 & 7.233  & 3.529  & 1.516\tnote{$\dagger$}  \\
-		& $\hat{\beta}_2 (\times 10^8)$  & 4.157  & 2.168  & 1.242\tnote{$\dagger$} & 4.135  & 2.269  & 1.269   \\ \midrule 
-		\multirow{3}{*}{AR1$\otimes$AR1}  & $\hat{\beta}_0$  & 25.185 & 25.092\tnote{$\dagger$} & 30.315  & 25.166 & 25.230 & 27.831  \\
-		&$\hat{\beta}_1 (\times 10^4)$  & 18.395 & 7.414  & 151.595 & 16.243 & 7.124\tnote{$\dagger$}  & 123.181  \\
-		& $\hat{\beta}_2 (\times 10^8)$ & 9.491  & 4.244  & 74.420  & 8.305  & 3.777\tnote{$\dagger$}  & 61.619 \\ \midrule
-		\multirow{3}{*}{\Matern} & $\hat{\beta}_0$  & 21.532 & 23.502 & 17.680  & 21.384 & 23.319 & 15.631\tnote{$\dagger$} \\
-		&$\hat{\beta}_1 (\times 10^4)$  & 9.502  & 4.326  & 112.914 & 6.121  & 2.901\tnote{$\dagger$}  & 96.829  \\
-		& $\hat{\beta}_2 (\times 10^8)$  & 5.071  & 2.537  & 56.789  & 3.324  & 1.889\tnote{$\dagger$}  & 44.707 \\ \bottomrule
+\multirow{3}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 25.186 & 25.200 & 25.224 & 25.176 & 25.140\tnote{$\dagger$} & 25.197 \\ 
+ & $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 9.870 & 5.490 & 5.662 & 9.529 & 5.167\tnote{$\dagger$} & 5.438 \\ 
+  & $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 5.130 & 3.064 & 3.177 & 4.938 & 3.001\tnote{$\dagger$} & 3.147 \\  \midrule
+\multirow{3}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 25.123 & 25.168 & 27.760 & 25.072\tnote{$\dagger$} & 25.133 & 26.707 \\ 
+& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 21.213 & 11.472 & 113.436 & 19.230 & 10.014\tnote{$\dagger$} & 91.858 \\ 
+& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 10.473 & 5.921 & 54.624 & 9.584 & 5.304\tnote{$\dagger$} & 44.645 \\  \midrule
+\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$  & 20.329 & 22.047 & 16.455 & 20.111 & 21.933 & 14.570\tnote{$\dagger$} \\ 
+&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 12.378 & 7.026 & 100.752 & 8.590 & 4.663\tnote{$\dagger$} & 80.409 \\ 
+& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 6.295 & 3.648 & 49.783 & 4.467 & 2.774\tnote{$\dagger$} & 39.595 \\ 
+   \bottomrule
 \end{tabular}
@@
 \end{table}
+
+% \begin{table}[!htp]
+% 	\centering
+% \begin{threeparttable}
+% 	\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is high ($\epsilon=0.1$).}\label{tb:MSEquadraticHigh}
+% 	\begin{tabular}{llcccccc} \toprule
+% 		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
+% 		$\epsilon=0.1$  & Coefficients & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+% 		\multirow{3}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$  & 25.075 & 25.067 & 25.015  & 25.082 & 25.060 & 25.012\tnote{$\dagger$} \\
+% 		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 6.683  & 3.466  & 1.478\tnote{$\dagger$} & 7.353  & 3.472  & 1.506 \\
+% 		&$\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 3.779  & 2.101  & 1.222\tnote{$\dagger$} & 3.806  & 2.124  & 1.284 \\  \midrule
+% 		\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$  & 25.103 & 25.223 & 29.266  & 25.033 & 25.032\tnote{$\dagger$} & 27.378 \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 16.260 & 6.845  & 130.335 & 16.228 & 6.314\tnote{$\dagger$}  & 112.599  \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 8.488  & 3.931  & 61.765  & 7.915  & 3.533\tnote{$\dagger$}  & 54.866  \\  \midrule
+% 		\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.780 & 23.622 & 18.832  & 21.409 & 23.296 & 15.728\tnote{$\dagger$}  \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 11.367 & 5.085  & 122.638 & 6.205  & 2.892\tnote{$\dagger$}  & 88.256 \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.979  & 2.981  & 60.298  & 3.025  & 1.803\tnote{$\dagger$}  & 43.156  \\ \bottomrule
+% 	\end{tabular}
+% 		    \begin{tablenotes}
+% 	        \item[$\dagger$] \footnotesize Indicates the smallest MSE for the row.
+% 	    \end{tablenotes}
+% \end{threeparttable}
+% \end{table}
 
@@
 		$\epsilon=0.1$  & Coefficients & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
-		\multirow{3}{*}{NS} & $\hat{\beta}_0$  & 25.075 & 25.067 & 25.015  & 25.082 & 25.060 & 25.012\tnote{$\dagger$} \\
-		&$\hat{\beta}_1 (\times 10^4)$  & 6.683  & 3.466  & 1.478\tnote{$\dagger$} & 7.353  & 3.472  & 1.506 \\
-		&$\hat{\beta}_2 (\times 10^8)$  & 3.779  & 2.101  & 1.222\tnote{$\dagger$} & 3.806  & 2.124  & 1.284 \\  \midrule
-		\multirow{3}{*}{AR1$\otimes$AR1} & $\hat{\beta}_0$  & 25.103 & 25.223 & 29.266  & 25.033 & 25.032\tnote{$\dagger$} & 27.378 \\
-		& $\hat{\beta}_1 (\times 10^4)$ & 16.260 & 6.845  & 130.335 & 16.228 & 6.314\tnote{$\dagger$}  & 112.599  \\
-		& $\hat{\beta}_2 (\times 10^8)$  & 8.488  & 3.931  & 61.765  & 7.915  & 3.533\tnote{$\dagger$}  & 54.866  \\  \midrule
-		\multirow{3}{*}{\Matern} & $\hat{\beta}_0$ & 21.780 & 23.622 & 18.832  & 21.409 & 23.296 & 15.728\tnote{$\dagger$}  \\
-		& $\hat{\beta}_1 (\times 10^4)$ & 11.367 & 5.085  & 122.638 & 6.205  & 2.892\tnote{$\dagger$}  & 88.256 \\
-		& $\hat{\beta}_2 (\times 10^8)$  & 5.979  & 2.981  & 60.298  & 3.025  & 1.803\tnote{$\dagger$}  & 43.156  \\ \bottomrule
+		\multirow{3}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$  & 25.133 & 25.108 & 25.116  & 25.146 & 25.099\tnote{$\dagger$} & 25.146 \\
+		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 9.273  & 5.218  & 5.354 & 8.803  & 4.994\tnote{$\dagger$}  & 5.152 \\
+		&$\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 4.846  & 2.901  & 3.009 & 4.687  & 2.822\tnote{$\dagger$}  & 2.908 \\  \midrule
+		\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$  & 24.916 & 24.983 & 27.370  & 24.801\tnote{$\dagger$} & 24.971 & 26.101 \\
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 19.312 & 10.594  & 104.207 & 19.721 & 10.200\tnote{$\dagger$}  & 93.399  \\
+		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 9.586  & 5.417\tnote{$\dagger$}  & 52.289  & 10.187  & 5.882  & 44.602  \\  \midrule
+		\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.661 & 22.407 & 16.603  & 20.215 & 21.972 & 14.505\tnote{$\dagger$}  \\
+		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 11.689 & 6.585  & 100.833 & 8.148  & 4.351\tnote{$\dagger$}  & 85.996 \\
+		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.976  & 3.568  & 47.692  & 4.194  & 2.459\tnote{$\dagger$}  & 40.541  \\ \bottomrule
 	\end{tabular}
@@
 \end{table}
+
+% \begin{table}[ht]
+% \centering
+% \begin{tabular}{rrrrrrr}
+%   \hline
+%  & X1 & X2 & X3 & X4 & X5 & X6 \\ 
+%   \hline
+% 1 & 25.133 & 25.108 & 25.116 & 25.146 & 25.099 & 25.146 \\ 
+%   2 & 9.273 & 5.218 & 5.354 & 8.803 & 4.994 & 5.152 \\ 
+%   3 & 4.846 & 2.901 & 3.009 & 4.687 & 2.822 & 2.908 \\ 
+%   4 & 24.916 & 24.983 & 27.370 & 24.801 & 24.971 & 26.101 \\ 
+%   5 & 19.312 & 10.594 & 104.207 & 19.721 & 10.200 & 93.399 \\ 
+%   6 & 9.586 & 5.417 & 52.289 & 10.187 & 5.882 & 44.602 \\ 
+%   7 & 20.661 & 22.407 & 16.603 & 20.215 & 21.972 & 14.505 \\ 
+%   8 & 11.689 & 6.585 & 100.833 & 8.148 & 4.351 & 85.996 \\ 
+%   9 & 5.976 & 3.568 & 47.692 & 4.194 & 2.459 & 40.541 \\ 
+%    \hline
+% \end{tabular}
+% \end{table}
 
@@
 
+% \begin{table}[!htp]
+% 	\centering
+% 	\caption{ANOVA analyses were conducted on the main factors and their second order interactions.
+The table lists degrees of freedom (Df), sum of squared errors (Sum Sq) and p-values of F tests (Pr($>$F)).
+}\label{tb:LMMoutput_old}
+% 	\begin{tabular}{r | lll | lll}
+% 		\toprule
+% 		 & \multicolumn{3}{c|}{Linear}  & \multicolumn{3}{c}{Quadratic}  \\
+%     & Df & Sum Sq  & Pr(\textgreater{}F) & Df & Sum Sq  & Pr(\textgreater{}F) \\ \midrule 
+% Design & 1  & 8.46  & 0.0935  & 1  & 74.03 & \textless{}0.001  \\
+% Bandwidth & 2  & 7453.09 & \textless{}0.001  & 2  & 90.29  & \textless{}0.001  \\
+% Covariance ($V_s$)  & 2  & 16958.42  & \textless{}0.001  & 2  & 6122.84 & \textless{}0.001 \\
+% Coefficients ($\zc{\bm{\beta}}$)  & 1  & 903705.52 & \textless{}0.001  & 2  & 1419372.21 & \textless{}0.001  \\
+% Correlation  ($\epsilon$)  & 1  & 5.63  & 0.171   & 1  & 0.07  & 0.8976  \\
+% Design:Bandwidth  & 2  & 9.21 & 0.216  & 2  & 113.48   & \textless{}0.001  \\
+% Design:Covariance & 2  & 3.91 & 0.5217  & 2  & 37.55  & 0.0134 \\
+% Design:Coefficients  & 1  & 8.45 & 0.0935  & 2  & 147.55 & \textless{}0.001  \\
+% Design:Correlation  & 1  & 0  & 0.9832  & 1  & 0.01  & 0.9541  \\
+% Bandwidth:Covariance   & 4  & 12283.13  & \textless{}0.001  & 4  & 3135.47  & \textless{}0.001  \\
+% Bandwidth:Coefficients & 2  & 7456.81 & \textless{}0.001  & 4  & 179.38 & \textless{}0.001  \\
+% Bandwidth:Correlation  & 2  & 5.95  & 0.3716  & 2  & 0.85  & 0.9073  \\
+% Covariance:Coefficients  & 2  & 16959.68  & \textless{}0.001  & 4  & 12248.74 & \textless{}0.001  \\
+% Covariance:Correlation & 2  & 0.26  & 0.9572  & 2  & 11.57  & 0.2649  \\
+% Coefficients:Correlation & 1  & 5.63  & 0.171   & 2  & 0.15  & 0.9834  \\ \bottomrule  
+% 	\end{tabular}
+% \end{table}
+
 \begin{table}[!htp]
@@
 \caption{ANOVA analyses were conducted on the main factors and their second order interactions.
-The table lists degrees of freedom (Df), sum of squared errors (Sum Sq) and p-values of F tests (Pr($>$F)).
-}\label{tb:LMMoutput}
-	\begin{tabular}{r | lll | lll}
-		\toprule
+The table lists degrees of freedom (Df), sum of squared errors (Sum Sq) and p-values of F tests (Pr($>$F)).}\label{tb:LMMoutput}
+\begin{tabular}{r | lll | lll} \toprule
 		& \multicolumn{3}{c|}{Linear}  & \multicolumn{3}{c}{Quadratic}  \\
-    & Df & Sum Sq  & Pr(\textgreater{}F) & Df & Sum Sq  & Pr(\textgreater{}F) \\ \midrule 
-Design & 1  & 8.46  & 0.0935  & 1  & 74.03 & \textless{}0.001  \\
-Bandwidth & 2  & 7453.09 & \textless{}0.001  & 2  & 90.29  & \textless{}0.001  \\
-Covariance ($V_s$)  & 2  & 16958.42  & \textless{}0.001  & 2  & 6122.84 & \textless{}0.001 \\
-Coefficients ($\beta$)  & 1  & 903705.52 & \textless{}0.001  & 2  & 1419372.21 & \textless{}0.001  \\
-Correlation  ($\epsilon$)  & 1  & 5.63  & 0.171   & 1  & 0.07  & 0.8976  \\
-Design:Bandwidth  & 2  & 9.21 & 0.216  & 2  & 113.48   & \textless{}0.001  \\
-Design:Covariance & 2  & 3.91 & 0.5217  & 2  & 37.55  & 0.0134 \\
-Design:Coefficients  & 1  & 8.45 & 0.0935  & 2  & 147.55 & \textless{}0.001  \\
-Design:Correlation  & 1  & 0  & 0.9832  & 1  & 0.01  & 0.9541  \\
-Bandwidth:Covariance   & 4  & 12283.13  & \textless{}0.001  & 4  & 3135.47  & \textless{}0.001  \\
-Bandwidth:Coefficients & 2  & 7456.81 & \textless{}0.001  & 4  & 179.38 & \textless{}0.001  \\
-Bandwidth:Correlation  & 2  & 5.95  & 0.3716  & 2  & 0.85  & 0.9073  \\
-Covariance:Coefficients  & 2  & 16959.68  & \textless{}0.001  & 4  & 12248.74 & \textless{}0.001  \\
-Covariance:Correlation & 2  & 0.26  & 0.9572  & 2  & 11.57  & 0.2649  \\
-Coefficients:Correlation & 1  & 5.63  & 0.171   & 2  & 0.15  & 0.9834  \\ \bottomrule  
+	  & Df & Sum Sq & Pr($>$F) & Df & Sum Sq & Pr($>$F) \\ \midrule
+Design   & 1.000 & 101.843 & 0.390 & 1.000 & 889.015 & 0.011 \\ 
+Bandwidth  & 2.000 & 64905.377 & $<0.01$ & 2.000 & 996.936 & 0.027 \\ 
+Covariance ($V_s$) & 2.000 & 188790.814 & $<0.01$ & 2.000 & 82458.618 & $<0.01$ \\ 
+Correlation ($\epsilon$) & 1.000 & 34.065 & 0.619 & 1.000 & 10.147 & 0.786 \\ 
+Design:Bandwidth & 2.000 & 36.983 & 0.874 & 2.000 & 1181.450 & 0.014 \\ 
+Design:Covariance ($V_s$)       & 2.000 & 43.486 & 0.854 & 2.000 & 579.136 & 0.123 \\ 
+Design:Correlation ($\epsilon$) & 1.000 & 5.912 & 0.836 & 1.000 & 2.800 & 0.887 \\ 
+Bandwidth:Covariance ($V_s$)  & 4.000 & 107351.708 & $<0.01$ & 4.000 & 24235.863 & $<0.01$ \\ 
+Bandwidth:Correlation ($\epsilon$)    & 2.000 & 32.424 & 0.889 & 2.000 & 0.938 & 0.997 \\ 
+Covariance ($V_s$):Correlation ($\epsilon$)          & 2.000 & 62.468 & 0.797 & 2.000 & 113.953 & 0.662 \\ 
+		\bottomrule
 \end{tabular}
 \end{table}
+
+\subsection{\zc{An example of optimal nitrogen map}}
+
+\zc{In practice, growers are more interested in the prescription map that tells them where the appropriate nitrogen should be applied on the paddock.
+With the application of GWR, we can find the local variations in crop needs, allowing for more precise and efficient nitrogen application.
+Each grid of the paddock receives the optimal amount of fertiliser.
+Consequently, this leads to improved crop yields, reduced investment cost and high profit.}
+
+\zc{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 from a randomised design and a systematic design using the same simulated coefficients of a quadratic curve under the assumption of $\AR\otimes\AR$ spatial covariance and low within-grid correlation.
+The optimal rate at grid $i$ is given by $\hat{N}_i = -\hat{\beta}_{1i}/(2\hat{\beta}_{2i})$ with constraints between 0 and 140, $i=1,\ldots,n$.
+For the randomised design, GWR failed to estimate the central part of the paddock.
+On the contrary, the estimated map from the systematic design is more consistent.}
+
+\begin{figure}[H]
+	\begin{subfigure}[t]{0.45\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{Expt/optN_syst_AR1B9.pdf}
+		%\caption{}
+        \end{subfigure}
+	\hspace{0.05\textwidth}
+	\begin{subfigure}[t]{0.45\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{Expt/optN_rand_AR1B9.pdf}
+		%\caption{}
+        \end{subfigure}
+	\caption{\zc{Optimal Nitrogen rate estimated by GWR from a randomised design (\textit{left}), and a systematic design (\textit{right}).}}\label{fig:optNmap}
+\end{figure}
 
@@
 
-\appendix
-
-\section{Figures}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_eta01.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$ and $\hat{\beta}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
-The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation between the parameters ($\epsilon=0.1$).}\label{fig:LinBetaMSEeta01}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_eta01.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\hat{\beta}_0$, $\hat{\beta}_1$ and $\hat{\beta}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
-The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation amongst the parameters ($\epsilon=0.1$).} \label{fig:QuadBetaMSEeta01}
-\end{figure}
-
 \renewcommand\bibname{References}% change bibliography title to references

### 2024-07-30 RCode/OFEExptNewPara1KSimuResults2024.R
updated scripts

@@ -526,15 +526,15 @@ LinAll[nms] <- lapply(LinAll[nms], as.factor)
 QuaAll[nms] <- lapply(QuaAll[nms], as.factor)
 
 
-linall.as <- asreml(Value ~ Design + BandWidth + Cov +  Eta, ## had + FacBeta
-                  data = LinAll)
-wald(linall.as,denDF = "default",ssType = "conditional")
-
-
-quaall.as <- asreml(Value ~ Design + BandWidth + Cov + Eta, ## had + FacBeta
-                    data = QuaAll)
-wald(quaall.as,denDF = "default",ssType = "conditional")
-
+# linall.as <- asreml(Value ~ Design + BandWidth + Cov +  Eta, ## had + FacBeta
+#                   data = LinAll)
+# wald(linall.as,denDF = "default",ssType = "conditional")
+# 
+# 
+# quaall.as <- asreml(Value ~ Design + BandWidth + Cov + Eta, ## had + FacBeta
+#                     data = QuaAll)
+# wald(quaall.as,denDF = "default",ssType = "conditional")
+# 
 
 
 linall.aov <- aov(Value ~ Design + BandWidth + Cov  + Eta +  ## had + FacBeta
@@ -701,11 +701,123 @@ library(viridis)
 
 custom_colors <- c("Randomised" = "gray70", "Systematic" = "white")
 
+generate_plots <- function(data, custom_colors) {
+  data$Cov <- factor(data$Cov, levels = c("NS","AR1","Matern" ))
+  
+  plot_list <- lapply(unique(data$Beta), function(beta, Eta = unique(data$Eta)) {
+    lapply(sort(unique(data$Cov)), function(cov) {
+      p <- ggplot(subset(data, Beta == beta & Cov == as.character(cov)), 
+                  aes(BandWidth, Value)) +
+        geom_boxplot(aes(fill = Design)) +
+        ylab("") + xlab("") +
+        thm1 +
+        scale_x_discrete(labels = c("5", "9", "AICc")) +
+        scale_fill_manual(values = custom_colors) +
+        theme(plot.margin = unit(c(0, 0.5, 0, 0), "cm")) 
+      
+      if (beta == 1) {
+        p <- p +       
+          labs(title = bquote(beta[.(beta)] ~ .("x") ~10^4 ~ .(", ") ~ 
+                                .(as.character(cov)) ~ .(", ") ~ epsilon ~"=" ~.(Eta)))+
+          scale_y_log10(labels = function(x) x * 1e4)
[…]

### 2024-07-30 RCode/Initialization.R
initialisation script

@@ -1,0 +1,287 @@
+rm(list=ls())
+library(dplyr)
+library(ggplot2)
+library(rgdal)
+# library(sf)
+library(raster)
+library(lattice)
+library(latticeExtra)
+library(classInt)
+library(GWmodel)
+library(maptools)
+library(spatstat)
+library(tidyr)
+library(agridat)
+# library(asreml)
+library(stringr)
+library(mvtnorm)
+library(matrixcalc)
+library(rstan)
+library(brms)
+library(metR)
+library(colorRamps)
+library(corrplot)
+library(ggridges)
+library(mgcViz)
+library(mgcv)
+library(rethinking)
+library(fields)
+library(bayesplot)
+library(reshape2)
+library(SpatialTools)
+library(loo)
+library(MASS)
+library(convoSPAT)
+library(ggpubr)
+
+
+MSE <- function(a,b) mean((a-b)^2)
+
+thm1 <- theme_bw() + 
+  theme(axis.title = element_text(size=20),
+        axis.text = element_text(size=20),
+        legend.title = element_text(size=20),
+        legend.text = element_text(size=20),
+        legend.key.width = unit(1,"cm"),
+        legend.position = "top",
+        strip.text.x = element_text(size = 20),
+        strip.text.y = element_text(size=20))
+
+skew <- function(x) {
+  xdev <- x - mean(x)
+  n <- length(x)
+  r <- sum(xdev^3) / sum(xdev^2)^1.5
+  return(r * sqrt(n) * (1 - 1/n)^1.5)
+}
+
+rsq_bayes <- function(post){
+  var_mu <- apply(post$mu, 1, var)
+  sigma2 <- post$sigma^2
+  rsq_bayes <- var_mu / (var_mu + sigma2)
+  print(summary(rsq_bayes))
+  print(quantile(rsq_bayes,c(0.025,0.5,0.975)))
+}
+
+sumstan <- function(fit){
+  
+  return(c(mean(fit),
+           sd(fit),
+           quantile(fit,c(0.025,0.5,0.975))))
+  
+}
+AR1CorMat <- function(rho,n) {
+  exponent <- abs(matrix(1:n - 1, nrow = n, ncol = n, byrow = TRUE) - 
+                    (1:n - 1))
[…]

### 2024-08-23 Revision1/Response.tex
revision submitted

--- 2024-07-29 MSforSubmission/Response.tex
@@
 \revision{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates.
-The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model (3), and the spatially varying estimates of that coefficient produced by GWR (8), and then averaging these squared differences across all the grid points.
-The lower the MSE, the better the design’s performance.}
+The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model (3), and the spatially varying estimates of that coefficient produced by GWR, and then averaging these squared differences across all the grid points, shown in equation (12).
+The lower the MSE, the better the design's performance.}
+
+\revision{The MSE corresponding to the estimation of spatially varying $\beta_{j}$ is given by}
+\begin{equation*}\label{eq:mse}
+\revision{\text{MSE}_j = \frac{1}{n} \sum_{i=1}^{n} \left( (b_j+u_{ji}) - \hat{\beta}_{ji} \right)^2},
+\end{equation*}
+\revision{where $j = 0, 1$ for a linear response and $j = 0, 1, 2$ for a quadratic response.}
 
@@
 \revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models.
-To this end, we perform 100 simulations of each of the 24 scenarios, described in the previous section.
-In each simulation, we first generated the coefficients for all grids and then applied the treatment in each grid to calculate the yield value using the model coefficients.
-For the treatments in all grids, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design.
-For a randomised design, all replicates have different orders of the treatments.}
+To this end, we perform 1000 simulations of each of the 24 scenarios, described in the previous section.
+In each simulation, we first generate the coefficients for all grids and then apply the treatment in each grid to calculate the yield value using the model coefficients.
+For the treatment order in each iteration, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design.
+For a randomised design, all replicates have random orders of the treatments.}
 
@@
 
-So we have revised Section 3, starting with a better description of the data source and why the parameters are chosen at this level.
+We have put one paragraph in the discussion section that 
+\revision{Our study employs simulation to evaluate the effectiveness of GWR in estimating coefficients for both randomised and systematic designs.
+However, a potential drawback of using simulation is its high dependency on the assumptions underlying the parametric model.
+If these assumptions are incorrect or fail to accurately represent real-world conditions, the simulation results may not reliably reflect the actual scenario.}
+
+Additionally, we have revised Section 3, starting with a better description of the data source and why the parameters are chosen at this level.
 The simulated data aligns with the authentic data from a corn field in Las Rosa.
@@
 
-We have put a new sentence in the introduction section in line 89: \revision{We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}
+We have put a new sentence in the introduction section in line 90: \revision{We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}
 
@@
 
-In line 160: \revision{We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.}
+In line 72: \revision{We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.}
 
@@
 
-We have now defined OFE when it first appears in the main text in line 44. The revised version is \revision{On-farm experiment (OFE) enables farmers the flexibility ...}.
+We have now defined OFE when it first appears in the main text in line 45. The revised version is \revision{On-farm experiment (OFE) enables farmers the flexibility ...}.
 
@@
 We have rewritten this paragraph to better fit the manuscript by:
-\revision{In this study, we generate simulated data for several scenarios, where each scenario is constructed by choosing one component at a time from the following four categories: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) model coefficients with low and high correlations; and (iv) spatial variance-covariance matrix  among grids given by identity (no spatial trend), AR1 $\bigotimes$ AR1, and Mat\'{e}rn forms.
+\revision{In this study, we generate simulated data for several scenarios, where each scenario is constructed by choosing one component at a time from the following four categories: (i) randomised and systematic designs; (ii) linear and quadratic responses; (iii) model coefficients with low and high correlations; and (iv) spatial variance-covariance matrix
+90 among grids given by identity (no spatial trend), AR1 $\bigotimes$ AR1, and Mat\'{e}rn forms.
 We subsequently evaluate the efficacy of GWR in accurately estimating the spatially varying treatment effects across these scenarios.}
@@
 
-We firstly in line 39 inserted the sentence \revision{ where treatments are randomly allocated in each replicate} for a randomised design.
+We firstly in line 39 inserted the sentence \revision{where treatments are randomly allocated in each replicate} for a randomised design.
 
-In line 42, we rewrote the sentence as follows: \revision{With the primary aim of obtaining unbiased estimates of global treatment effects, randomised designs, which use a different layout of treatments in each replicate, are routinely used for on-farm strip trials, whereas systematic designs, which use the same layout of treatments in all replicates, are rarely used.}
+In line 41, we rewrote the sentence as follows: \revision{With the primary aim of obtaining unbiased estimates of global treatment effects, randomised designs, which use different
+layouts of treatments in each replicate, are routinely used for on-farm strip trials, whereas systematic designs, which use the same layout of treatments in all replicates, are rarely used.}
 
-In line 168, we try to remind the reader by using the following description that \revision{Examples of a randomised design, which uses different orders of treatment in each replicate, and a systematical design, which uses the same order of treatment in all replicates, are presented in Figure 1.}
+In line 174, we try to remind the reader by using the following description that \revision{Examples of a randomised design, which uses different orders of treatment in each replicate, and a systematic design, which uses the same order of treatment in all replicates, for this layout are presented in Figure 1.}
 
@@
 
-\revision{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 from a randomised design and a systematic design using the same simulated coefficients of a quadratic curve under the assumption of $\AR\otimes\AR$ spatial covariance and low within-grid correlation.
-The optimal rate is given by $\hat{N} = -\hat{\beta}_1/(2\hat{\beta}_2)$ with constraints between 0 and 140.
-For the randomised design, GWR failed to estimate the central part of the paddock.
+\revision{Figure \ref{fig:yieldmap} is the simulated crop yield map with the assumption of a quadratic response curve and \Matern spatial covariance and low within-grid correlation.
+These two yield maps have the same coefficients but different yields due to different treatment layouts.}
+
+\begin{figure}[!htp]
+\centering
+    \begin{subfigure}[t]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{quad_random_yield_mat.pdf}
+		%\caption{}
+    \end{subfigure}
+    %\hspace{0.05\textwidth}
+    \begin{subfigure}[t]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{quad_syst_yield_mat.pdf}
+		%\caption{}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{quad_diff_yield_mat.pdf}
+		%\caption{}
+    \end{subfigure}
+	\caption{\revision{Simulated yield map of a randomised design (\textit{top}), and a systematic design (\textit{middle}), and the difference of these two designs (\textit{bottom}).}}\label{fig:yieldmap}
+\end{figure}
+
+\revision{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 using the above yield data.
+The optimal rate at grid $i$ is given by $\hat{N}_i = -\hat{\beta}_{1i}/(2\hat{\beta}_{2i})$ with constraints between 0 and 140, $i=1,\ldots,n$.
+For the randomised design, GWR underestimated the right part of the paddock.
 On the contrary, the estimated map from the systematic design is more consistent.}
 
-\begin{figure}[H]
+\begin{figure}[!htp]
 	\begin{subfigure}[t]{0.45\textwidth}
 		\centering
-		\includegraphics[width=\linewidth]{Expt/optN_syst_AR1B9.pdf}
+		\includegraphics[width=\linewidth]{optN_rand_matB9.pdf}
 		%\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/optN_rand_AR1B9.pdf}
+		\includegraphics[width=\linewidth]{optN_syst_matB9.pdf}
 		%\caption{}
@@
 
-%\printbibliography
-
 \end{document}

### 2024-08-23 Revision1/main_revision_clear.tex
revision submitted

--- 2024-07-29 MSforSubmission/main_revision_col.tex
@@
 
-\newcommand{\revision}[1]{\textcolor{red}{#1}}
-\newcommand{\zc}[1]{\textcolor{blue}{#1}}
+\newcommand{\revision}[1]{\textcolor{black}{#1}}
+\newcommand{\zc}[1]{\textcolor{black}{#1}}
 
-\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=biber, maxcitenames=2, giveninits=true, maxbibnames=100, uniquename=init]{biblatex}
+\usepackage[url=false, isbn=false, eprint=false, backref=true, style= authoryear, backend=bibtex, maxcitenames=2, giveninits=true, maxbibnames=100, uniquename=init]{biblatex}
 %backend=bibtex
@@
 CONTEXT OR PROBLEM: Randomised designs are often preferred over systematic designs by agronomists and biometricians.
-However, for on-farm trials, the choice may depend on the objective of the experiments.
+For on-farm trials, \zc{however}, the choice may depend on the objective of the experiments.
 If the purpose is to create a prescription map of a continuous input for each plot of a grid covering a large strip trial, a systematic design may be a better choice, but it attracts less discussion and attention.
@@
 RESULTS: With the assumption of \revision{a} quadratic response, a systematic design is superior to a randomised design \revision{in terms of achieving lower mean squared errors (MSE) with GWR}.
-However, with the assumption of \revision{a} linear response, the difference between a systematic design and a randomised design is not significant, regardless of the presence of spatial variation.
+\zc{With} the assumption of \revision{a} linear response, the difference \zc{of MSE} between a systematic design and a randomised design is not significant, regardless of the presence of spatial variation.
 
-CONCLUSIONS: The findings highlight the superiority of systematic designs in producing smooth \revision{spatial} maps of optimal input levels \revision{for quadratic response models in large strip trials, even when impacted by significant spatial variation.}.
-Additionally, \textcolor{red}{we recommend selecting} fixed bandwidths \revision{in GWR analysis} based on \revision{the plot configurations used in} experimental designs.
+CONCLUSIONS: The findings highlight the superiority of systematic designs in producing smooth \revision{spatial} maps of optimal input levels \revision{for quadratic response models in large strip trials, even when impacted by significant spatial variation.} Additionally, \revision{we recommend selecting} fixed bandwidths \revision{in GWR analysis} based on \revision{the plot configurations used in} experimental designs.
 For a large strip trial, to \revision{produce estimates of spatially-varying treatment effects across strips}, a systemic design should be used as it \revision{allows us to obtain better estimates than those obtained from a randomised design} in post-experiment statistical modelling.
@@
 The principle of randomisation was first expounded in 1925 by \textcite{Fisher1934Statistical}, who analysed a few systematically arranged experiments and pointed out that randomisation can provide valid tests of significance subject to appropriate restrictions, such as experimental units arranged in blocks or in rows and columns of a Latin square \parencite{Verdooren2020History}.
-Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design (CRD), \zc{where treatments are randomly allocated in each replicate}.
-More complex designs, such as the randomised complete block design (RCBD), the split-plot design, the strip-plot design and the Latin square design, are also widely used in agricultural experiments \revision{to improve the precision of treatment effect estimates} \parencite{Petersen1994Agricultural}.
+Traditionally, small-plot trials for agriculture are designed to \revision{obtain unbiased estimates of} treatment effects \revision{using} the completely randomised design, \zc{where treatments are randomly allocated into plots}.
+More complex designs, such as the randomised complete block design, the split-plot design, the strip-plot design and the Latin square design, are also widely used in agricultural experiments \revision{to improve the precision of treatment effect estimates} \parencite{Petersen1994Agricultural}.
 \revision{With the primary aim of obtaining unbiased estimates of global treatment effects}, randomised designs \zc{, which use different layouts of treatments in each replicate,} are routinely used for on-farm strip trials, \revision{whereas} systematic designs, \zc{which use the same layout of treatments in all replicates,} are rarely used.
@@
 While randomisation is often considered a crucial prerequisite for obtaining valid statistical inferences \parencite{Piepho2013Why}, this is not always the case when the goal of OFE shifts from the conventional analysis.
-In the application of precision agriculture (PA) \revision{using} variable rate applicators (VRA)\revision{,} a prescription map of the experiment \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}.
+In the application of precision agriculture \revision{using} variable rate applicators\revision{,} a prescription map of the experiment \revision{is required to optimally apply varying treatments across a field} \parencite{Pringle2004FieldScale}.
 Therefore, in this scenario, the goal of OFE becomes obtaining a smooth \revision{spatial} map showing the optimal level of a controllable input, such as nitrogen rates, across a grid made of rows and columns covering the whole field.
-\revision{An important point to note here is} that only a single \revision{treatment level} can be directly observed at any one point on the grid, and the response for other levels at the same grid must be interpolated.
+\revision{An important point to note here is} that only a single \revision{treatment level} can be directly observed at any one point on the grid, and the response for other levels \zc{in} the same grid must be interpolated.
 If a randomised design is conducted, the interpolation distances to locations with treatment levels of interest will vary throughout the field.
@@
 Additionally, \textcite{Evans2020Assessment} concluded through simulation studies that GWR is capable of accurately separating variation \revision{in yield response due to treatment from} \revision{the variation that} is not due to the applied treatment.
-However, their study was limited by the use of a randomised design and the assumption of a linear response \revision{model}.
+\zc{The limitations in} their study \zc{are} the use of a randomised design and the assumption of a linear response \revision{model}.
 \revision{To compare between the systematic and randomised treatment allocation in the chessboard design,} \textcite{Alesso2021Design} simulated corn yield \revision{response} \revision{for} four nitrogen levels and \revision{estimated the regression} coefficients using GWR.
@@
 
-The underlying template model for the GWR, according to \textcite{Leung2000Statistical}, is given by 
+The underlying template model for GWR is given by 
 \begin{equation}\label{eq:basicgwr}
@@
 \end{equation}
-where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ and $\varepsilon_{i} \sim \N(0,\tau^2)$ are the model parameters for the $k$ treatment \revision{levels} and error terms, respectively, at grid $i,\ i=1,\ldots,n$.
+where $\bm{\beta}\revision{ = (\beta_0, \beta_{1}, \ldots, \beta_{k})^{\top}}$ are model parameters corresponding to the $k$ treatment \revision{levels} and $\varepsilon_{i} \sim \N(0,\tau^2)$,  $i=1,\ldots,n$,  are independent and identically distributed error terms at $n$ grid points.
 
@@
 \begin{eqnarray}\label{eq:locallog}
-	\log L(s;\beta) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_j \revision{x}_j(s_i) \right)^2 
+	\log L(s; \bm{\beta}) = - \frac{1}{2\tau^2}\sum_{i=1}^{n}K(s,s_i)\left( y(s_i) -\beta_0 - \sum_{j=1}^{k}\beta_j \revision{x}_j(s_i) \right)^2 
 \end{eqnarray}
-with a given kernel function $K(\cdot,\cdot)$, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}.
+where $K(\cdot,\cdot)$ is a given kernel function, such as Gaussian, exponential, bi-square or tri-cube \parencite{Gollini2015GWmodel}.
 
@@
 
-In the simulation study, we use a Gaussian kernel.
+\revision{To obtain GWR estimates of model parameters} in the simulation study, we have used a Gaussian kernel.
 In fact, the kernel \revision{function} is not the crucial factor in the GWR \revision{analysis}.
-\revision{In} contrast, the bandwidth has a higher influence on estimation.
+\revision{In} contrast, the bandwidth has a higher influence on the estimates.
 
-The optimal bandwidth \revision{for} a GWR model is usually \revision{selected} by the lowest AICc where 
+The optimal bandwidth \revision{for} a GWR model is usually \revision{selected} by the lowest AICc, which is given by 
 \begin{equation}\label{eq:aicc}
@@
 \end{equation}
-and $S$ is the matrix with the $i$-th row given by $\revision{X}_i\left( \revision{X}^\top W(s_i) \revision{X} \right)^{-1}\revision{X}^\top W(s_i)$ \parencite{Evans2020Assessment}.
-Alternatively, as suggested by \textcite{Rakshit2020Novel}, it can be based on the experimental design such that the local regressions capture data covering the full range of treatments.
+where $S$ is the matrix with the $i$-th row given by $\revision{X}_i\left( \revision{X}^\top W(s_i) \revision{X} \right)^{-1}\revision{X}^\top W(s_i)$ \parencite{Evans2020Assessment}, \zc{and $\tr(\cdot)$ is the trace of a square matrix returning the sum of the elements on the main diagonal.} Alternatively, as suggested by \textcite{Rakshit2020Novel}, it can \zc{be chosen according to} the experimental design such that the local regressions capture data covering the full range of treatments.
 
@@
 
-\zc{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates.} \revision{The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model \eqref{eq:underlying}, and the spatially varying estimates of that coefficient produced by GWR \eqref{eq:basicgwr}, and then averaging these squared differences across all the grid points.
-The lower the MSE, the better the design's performance.} \zc{The advantage of the simulation study is that the actual coefficients of the models are known, so} \revision{possible} \zc{adverse effects of model misspecification can be} \revision{omitted while assessing the performances of different designs on parameter estimation} \parencite{Piepho2013Why}.
+\zc{To compare the performances of randomised and systematic designs in terms of accurate estimation of the model coefficients using GWR, we use the mean squared errors (MSE) corresponding to all coefficient estimates.} \revision{The MSE for a coefficient was computed by first taking the differences between the true coefficient, specified in model \eqref{eq:underlying}, and the spatially varying estimates of that coefficient produced by GWR, and then averaging these squared differences across all the grid points, shown in equation \eqref{eq:mse}.
+The lower the MSE, the better the design's performance.}
+
+\revision{The MSE corresponding to the estimation of spatially varying $\beta_{j}$ is given by}
+\begin{equation}\label{eq:mse}
+\zc{\text{MSE}_j = \frac{1}{n} \sum_{i=1}^{n} \left( (b_j+u_{ji}) - \hat{\beta}_{ji} \right)^2},
+\end{equation}
+\zc{where $j = 0, 1$ for a linear response and $j = 0, 1, 2$ for a quadratic response.}
+
+%This part is not needed and wrong also in our context and confusing....\zc{The advantage of the simulation study is that the actual coefficients of the models are known, so} \revision{possible} \zc{adverse effects of model misspecification can be} \revision{omitted while assessing the performances of different designs on parameter estimation} \parencite{Piepho2013Why}.
 
@@
 
-\revision{The simulation study is based on the real life data recorded from a corn field in Las Rosas, Argentina.
+\revision{The simulation study is performed using realistic values for the model parameters, which are selected based on the analysis results of a real-life data recorded from a corn field in Las Rosas, Argentina.
 This data set was originally provided by \textcite{Luc2004ASpatial} and can be accessed via the \texttt{R}-package \texttt{agridat} \parencite{White2008Agridat}.
@@
 \revision{Studies by \textcite{Rakshit2020Novel, Cao2022Bayesian} suggest that the yield produced by the maximum nitrogen rate of 124.6 kg/ha may be improved by using a higher rate.
-Thus, we made some adjustments while selecting the nitrogen rates for our simulation study.
-We used five evenly spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.
-Additionally, we increased the number of replicates from three to four.
-Consequently, the final layout of the trial used in the simulation consisted of 93 rows and 20 columns.
+Thus, we have made some adjustments while selecting the nitrogen rates for our simulation study.
+We use five evenly-spaced nitrogen rates: 0, 35, 70, 105, and 140 kg/ha.
+Additionally, we increase the number of replicates from three to four.
+Consequently, the final layout of the trial used in the simulation consists of 93 rows and 20 columns.
 Examples of a randomised design, \zc{which uses different orders of treatment in each replicate}, and a systematic design, \zc{which uses the same order of treatment in all replicates}, for this layout are presented in Figure \ref{fig:Nitrogen}.}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_RandNitro_V4.pdf}
+		\includegraphics[width=\linewidth]{Col_RandNitro_V4.pdf}
 		%\caption{Treatments are randomly allocated into large strips in each replicate block.}\label{fig:RandNitrogen}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/Col_SystNitro_V4.pdf}
+		\includegraphics[width=\linewidth]{Col_SystNitro_V4.pdf}
 		%\caption{Treatments are systematically allocated into large strips in each replicate block.}\label{fig:SystNitrogen}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/LinlinesV2.pdf}
+		\includegraphics[width=\linewidth]{LinlinesV2.pdf}
 		%\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{Expt/QualinesV2.pdf}
+		\includegraphics[width=\linewidth]{QualinesV2.pdf}
 		%\caption{}
@@
 \revision{In this section, we assess the performances of randomised and systematic designs in terms of their utility to accurately estimate the model parameters for both linear and quadratic response models.
-To this end, we perform 1\,000 simulations of each \revision{of the 24} scenarios\zc{, described} in the previous section.} \zc{In each simulation, we first generated the coefficients for all grids and then applied the treatment in each grid to calculate the yield value using the model coefficients.
-For the treatments in all grids, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design.
-For a randomised design, all replicates have different orders of the treatments.} In Section~\ref{Sec:MSE}, the mean squared errors are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix.
-Section~\ref{Sec:anova} uses \revision{the} analysis of variance (ANOVA) to  \revision{assess} the significance of the factors \revision{considered} in the simulation \revision{study}.
+To this end, we perform 1000 simulations of each \revision{of the 24} scenarios\zc{, described} in the previous section.} \zc{In each simulation, we first generate the coefficients for all grids and then apply the treatment in each grid to calculate the yield value using the model coefficients.
+For the treatment order in each iteration, we randomly picked an order of treatments for a single replicate and repeated this sequence across all other replicates to construct a systematic design.
+For a randomised design, all replicates have random orders of the treatments.}
+
+% In Section~\ref{Sec:MSE}, the MSEs are compared between the two designs for different \revision{factors, including the choice of} bandwidth, parameter correlation, and spatial covariance matrix.
+% Section~\ref{Sec:anova} uses \revision{the} analysis of variance (ANOVA) to  \revision{assess} the significance of the factors \revision{considered} in the simulation \revision{study}.
 %\st{subsection} Section~\ref{Sec:bandselect} \st{states} \revision{presents} the \st{performance of} \revision{results of} bandwidth selection using AICc.
@@
 
-\revision{Figures~\ref{fig:LinBetaMSE} and \ref{fig:LinBetaMSEeta01} show the results of linear models for the cases of low ($\epsilon = 1$) and high ($\epsilon = 0.1$) spatial correlations, respectively, while Figures~\ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show the results of quadratic models for the same low and high correlations, respectively.
-To specify the covariance matrix $V_s$ used in producing the results in these figures, we use the following labels: (i) ``NS'' for the identity matrix representing no spatial correlation, (ii) ``AR1'' for $\AR(0.15)\otimes \AR(0.5)$, and (iii) ``Matern'' for \Matern covariance with $\nu=3/2$.}
-
-% \st{The MSE results are shown in Figures} \ref{fig:LinBetaMSE} and \ref{fig:QuadBetaMSE}\st{, where ``NS'' stands for no spatial variation ($V_s=I_{n\times n}$),} \st{``AR1'' for $\AR(0.15)\otimes \AR(0.5)$, and ``Matern'' for} \Matern \st{covariance with $\nu=3/2$.
-Since the MSE  $\zc{\bm{\beta}}_0$, $\zc{\bm{\beta}}_1$, and $\zc{\bm{\beta}}_2$ are small, we take the natural logarithm for better visualisation.}
+\revision{Figures~\ref{fig:LinBetaMSE} and \ref{fig:LinBetaMSEeta01} show the results of linear models for the cases of low ($\epsilon = 1$) and high ($\epsilon = 0.1$) correlations, respectively, while Figures~\ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show the results of quadratic models for the same low and high correlations, respectively.
+To specify the covariance matrix $V_s$ used in producing the results in these figures, we use the following labels: (i) ``NS'' for the identity matrix representing no spatial correlation, (ii) ``AR1'' for $\AR(0.15)\otimes \AR(0.5)$, and (iii) ``Matern'' for \Matern covariance with $\nu=3/2$.} \zc{Note that the model parameters and their corresponding MSEs are small values, and this makes it difficult to compare the MSEs of different scenarios using the original scale of MSE values.
+Therefore, to enhance clarity in visualisation and comparison, we have multiplied the MSEs of $\bm{\beta}_1$ and $\bm{\beta}_2$ by $10^4$ and $10^8$, respectively, in the figures presented below.
+}
 
 % Paragraph about Figure 3 and the performance for a linear response
-\revision{For} a linear response, both randomised and systematic designs perform similarly\revision{, particularly for the cases NS and AR1.} Figure~\ref{fig:LinBetaMSE} shows that the MSEs \revision{corresponding to} $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ for all bandwidths \revision{are fairly similar for both} designs.
-\revision{However, the results in Table~1 show that the MSE medians corresponding to $\zc{\hat{\bm{\beta}}}_1$ for the \Matern case are consistently lower for the systematic design.}
-This is true regardless of \revision{the correlation within grids considered in a simulation}, small ($\epsilon=1$) or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
+\revision{For} the linear response model, both randomised and systematic designs perform similarly\revision{, particularly for the case NS.} Figure~\ref{fig:LinBetaMSE} shows that the MSE \revision{corresponding to} $\zc{\hat{\bm{\beta}}}_0$ for all bandwidths \revision{are fairly similar for both} designs \zc{without spatial correlation}.
+\zc{However, when a spatial covariance matrix is incorporated in the model, the MSE results, presented also in Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh}, in the figures below show that the MSE medians corresponding to $\hat{\bm{\beta}}_1$ for $\AR\otimes\AR$ and \Matern cases are lower for the systematic design.}
+%This is true regardless of \revision{the correlation within grids considered in a simulation}, small ($\epsilon=1$) or high ($\epsilon=0.1$) as is shown in Figure \ref{fig:LinBetaMSEeta01}.
 %% The GWR with bandwidth selected by AICc has a smaller MSE for its coefficients than the model with a fixed bandwidth (Figure \ref{fig:LinBetaMSE}).
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_V3.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
-The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation between the parameters ($\epsilon=1$).}\label{fig:LinBetaMSE}
+	\includegraphics[width=\linewidth]{Col_LinCombMSE_newpar_1K_V4.pdf}
+	\caption{\zc{Boxplots of MSE for $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
+The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation between the parameters ($\epsilon=1$).}}\label{fig:LinBetaMSE}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_LinCombMSE_newpar_eta01_V3.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
-The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation between the parameters ($\epsilon=0.1$).}\label{fig:LinBetaMSEeta01}
+	\includegraphics[width=\linewidth]{Col_LinCombMSE_newpar_1K_eta01_V4.pdf}
+	\caption{\zc{Boxplots of MSE for $\zc{\hat{\bm{\beta}}}_0$ and $\zc{\hat{\bm{\beta}}}_1$ in GWR models using different bandwidths for the simulated data with a linear response.
+The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation between the parameters ($\epsilon=0.1$).}}\label{fig:LinBetaMSEeta01}
 \end{figure}
@@
 % Paragraph about Figure 4 and the performance for a linear response
-However, if the assumption is a quadratic response, Figures \ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show that the GWR with a fixed bandwidth of a systematic design outperforms a randomised design if the spatial correlation is taken into account.
-With the optimal bandwidth, GWR successfully estimates the global intercepts $\zc{\bm{\beta}}_0$ but failed in estimating local varying coefficients $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, where the MSE is relatively larger than with fixed bandwidth.
-However, if we only compare across two types of designs, it still proves that GWR is robust to fit a systematic design rather than a randomised design if the assumption is a quadratic response, regardless of the intensity of the correlation within grids.
+\revision{For} the quadratic response \revision{model}, Figures \ref{fig:QuadBetaMSE} and \ref{fig:QuadBetaMSEeta01} show that the GWR estimates \revision{of both ${\bm{\beta}}_{1}$ and ${\bm{\beta}}_{2}$ based on fixed bandwidths of $5$ and $9$ for systematic designs outperform the estimates obtained for randomised designs when spatial correlation (``AR1'' and ``Matern") is present in yield data}.
+\revision{Using the AICc optimal bandwidth, GWR successfully estimates the intercepts $\zc{\bm{\beta}_0}$ but fails to accurately estimate} \zc{linear and quadratic} coefficients $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, \revision{resulting in MSEs that are relatively larger than those obtained using a fixed bandwidth}.
+\revision{Overall, the results of our simulation study indicate that the systematic designs are superior to randomised designs in enabling accurate and precise estimation of spatially varying treatment effects, especially when the response model is a quadratic function of the treatment levels.}
+
+%If we only compare across two types of designs, it proves that \zc{fitting} GWR to a systematic design \zc{is more robust} than \zc{fitting it to} a randomised design if the assumption is a quadratic response.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_V3.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$, $\zc{\hat{\bm{\beta}}}_1$ and $\zc{\hat{\bm{\beta}}}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
-The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation amongst the parameters ($\epsilon=1$).} \label{fig:QuadBetaMSE}
+	\includegraphics[width=\linewidth]{Col_QuaCombMSE_newpar_1K_V4.pdf}
+	\caption{\zc{Boxplots of MSE for $\zc{\hat{\bm{\beta}}}_0$, $\zc{\hat{\bm{\beta}}}_1$ and $\zc{\hat{\bm{\beta}}}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
+The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a low correlation amongst the parameters ($\epsilon=1$).}} \label{fig:QuadBetaMSE}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=\linewidth]{Expt/Col_QuaCombMSE_newpar_eta01_V3.pdf}
-	\caption{Boxplots of the logarithm of MSE for $\zc{\hat{\bm{\beta}}}_0$, $\zc{\hat{\bm{\beta}}}_1$ and $\zc{\hat{\bm{\beta}}}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
-The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation amongst the parameters ($\epsilon=0.1$).} \label{fig:QuadBetaMSEeta01}
+	\includegraphics[width=\linewidth]{Col_QuaCombMSE_newpar_1K_eta01_V4.pdf}
+	\caption{\zc{Boxplots of MSE for $\zc{\hat{\bm{\beta}}}_0$, $\zc{\hat{\bm{\beta}}}_1$ and $\zc{\hat{\bm{\beta}}}_2$ in GWR models using different bandwidths for the simulated data with a quadratic response.
+The simulated data had different spatial covariance matrices (NS, AR1$\otimes$AR1 and \Matern) and a high correlation amongst the parameters ($\epsilon=0.1$).}} \label{fig:QuadBetaMSEeta01}
 \end{figure}
@@
 When no spatial variation was simulated for $\beta_1$ and $\beta_2$, the AICc-selected bandwidth has the lowest MSE, followed by the fixed bandwidths of 9 and then 5.
-When there is spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ has the lowest MSEs when using bandwidth 9, followed by 5 and then bandwidth from AICc.
+When there is spatial variation (either AR1$\otimes$AR1 or \Matern) present the estimation for $\beta_1$ and $\beta_2$ has the lowest MSE when using bandwidth 9, followed by 5 and then bandwidth from AICc.
 The intercept ($\beta_0$) shows only significant changes in MSE amongst the bandwidths when the \Matern spatial covariance was considered.
@@
 
-MSE analyses revealed that the choice of bandwidth significantly influenced the relative performance based on both the spatial covariance matrix and the coefficient characteristics.
-In scenarios without spatial variation for $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, the AICc-selected bandwidth demonstrated the lowest MSE, followed by fixed bandwidths of 9 and 5, respectively.
-However, when the spatial variation was present (utilising either AR1$\otimes$AR1 or \Matern covariance structures), the bandwidth of 9 consistently produced the most accurate estimations for $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, outperforming the bandwidths of 5 and the one chosen by AICc.
-Notably, for the intercept ($\zc{\bm{\beta}}_0$), significant changes in MSE amongst the bandwidths were observed only in the context of the \Matern spatial covariance.
-Here, the bandwidth selected by AICc resulted in the smallest MSE, highlighting its efficacy when dealing with spatially correlated residuals following the \Matern covariance structure.
+\revision{Moreover,} MSE \zc{comparisons} reveal that the choice of bandwidth \zc{may influence} the relative performance \revision{of the two designs differently depending on whether the intercept coefficient or the slope coefficients are being estimated.
+Differences in relative performance are also observed for different forms of spatial covariance matrices considered in the simulation scenarios.}  In scenarios without spatial variation, \revision{when estimating} \zc{$\zc{\bm{\beta}}_0$}, $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, the AICc-selected bandwidths \revision{produce} \zc{the lowest} MSE \revision{medians}.
+\zc{In contrast, when} spatial variation \zc{is} present (utilising either AR1$\otimes$AR1 or \Matern covariance structures), the bandwidth of 9 consistently produces the most accurate estimates of $\zc{\bm{\beta}}_1$ and $\zc{\bm{\beta}}_2$, outperforming the \revision{estimates obtained using either the} bandwidth of 5 or the one chosen by AICc.
+%% Notably, for the intercept ($\zc{\bm{\beta}}_0$), significant changes in MSE amongst the bandwidths \zc{are} observed only in the context of the \Matern spatial covariance.
+% Here, the bandwidth selected by AICc resulted in the smallest MSE, highlighting its efficacy when dealing with spatially correlated residuals following the \Matern covariance structure.
 
-Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} are the median MSE of the linear response for two scenarios: the correlation is low and the correlation is high.
+Tables \ref{tb:MSElinear} and \ref{tb:MSElinearHigh} \revision{present} the median MSEs \revision{corresponding to the parameter estimation for} the linear response \revision{model in the} two scenarios \revision{of low ($\epsilon=1$) and high ($\epsilon= 0.1$) correlations, respectively}.
 
@@
 % \begin{threeparttable}
-% 	\caption{Median MSE of GWR coefficient estimates for a linear response when the correlation between the parameters is low ($\epsilon=1$).}\label{tb:MSElinear_old}
+% 	\caption{\zc{Median MSE of GWR coefficient estimates for a linear response when the correlation between the parameters is low ($\epsilon=1$).}}\label{tb:MSElinear}
 % 	\begin{tabular}{llcccccc}
 % 		\toprule
-% 		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
-%    		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
-% 		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.903 &	24.924 &	24.983&	24.886\tnote{$\dagger$} &	24.911 &	24.965 \\ 
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.147&	0.118&	0.105&	0.147&	0.117&	0.104\tnote{$\dagger$}  \\  \midrule
-% 		\multirow{2}{*}{AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.308&	24.617&	24.126&	24.319&	24.617&	23.246\tnote{$\dagger$}  \\ 
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.215	&0.147	&1.208&	0.214&	0.146\tnote{$\dagger$}	&1.143 \\ \midrule
-% 		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.303	&23.566	&9.647&	21.164&	23.526&	9.239\tnote{$\dagger$} \\ 
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.157	&0.121&	0.845&	0.138&	0.115\tnote{$\dagger$} &	0.749 \\
+% 		&  & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+%   	\multirow{2}{*}{$V_s$ with $\epsilon=1$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+% 		&  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+% 		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.852 &	24.933 &	24.912&	\bf{24.781}\tnote{$\dagger$} &	24.850 &	24.861 \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.683 &	1.341 &	1.398 &	1.615 &	\bf{1.320}\tnote{$\dagger$} &	1.361 \\  \midrule
+%  \multirow{2}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.401 &	24.649 &	23.695 &	24.295 &	24.684 &	\bf{23.118}\tnote{$\dagger$} \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.489 &	1.790 &	10.071 &	2.441 &	\bf{1.740}\tnote{$\dagger$} &	9.995 \\ \midrule
+% 		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.482 &	22.432 &	9.801 &	20.319 &	22.194 &	\bf{9.280}\tnote{$\dagger$} \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.683 &	1.378 &	8.049 &	1.398 &	\bf{1.197}\tnote{$\dagger$} &	7.022 \\
 % 		\bottomrule
@@
 \begin{threeparttable}
-	\caption{Median MSE of GWR coefficient estimates for a linear response when the correlation between the parameters is low ($\epsilon=1$).}\label{tb:MSElinear}
-	\begin{tabular}{llcccccc}
+\caption{\zc{Median MSE of GWR coefficient estimates for a linear response when the correlation between the parameters is low ($\epsilon=1$).}}\label{tb:MSElinear}
+\begin{tabular}{ll|ccc|ccc}
 \toprule
-		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
-   		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
-		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.852 &	24.933 &	24.912&	24.781\tnote{$\dagger$} &	24.850 &	24.861 \\ 
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.683 &	1.341 &	1.398 &	1.615 &	1.320\tnote{$\dagger$} &	1.361 \\  \midrule
-		\multirow{2}{*}{AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.401 &	24.649 &	23.695 &	24.295 &	24.684 &	23.118\tnote{$\dagger$} \\ 
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.489 &	1.790 &	10.071 &	2.441 &	1.740\tnote{$\dagger$} &	9.995 \\ \midrule
-		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.482 &	22.432 &	9.801 &	20.319 &	22.194 &	9.280\tnote{$\dagger$} \\ 
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.683 &	1.378 &	8.049 &	1.398 &	1.197\tnote{$\dagger$} &	7.022 \\
+\multicolumn{2}{c}{Linear Response with $\epsilon=1$} & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+\multirow{2}{*}{$V_s$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+&  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+\multirow{2}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$ & \bf{24.868}\tnote{$\dagger$}  & 24.927   & 24.952   & 24.883     & 24.931     & 24.953 \\
+  &$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.458   & 1.175   & 1.048 & 1.479    & 1.185   & \bf{1.045}\tnote{$\dagger$}   \\ \midrule
+\multirow{2}{*}{AR1}& $\zc{\hat{\bm{\beta}}}_0$ & 24.471  & 24.807   & 24.134   & 24.513      & 24.788    & \bf{23.538}\tnote{$\dagger$}  \\
+     & $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.178   & 1.484    & 12.744     & 2.173    & \bf{1.463}\tnote{$\dagger$}     & 11.922  \\ \midrule
+\multirow{2}{*}{Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.125  & 23.215   & 9.667      & 20.928     & 23.100    & \bf{8.871}\tnote{$\dagger$} \\
+      & $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$& 1.600   & 1.232    & 8.591      & 1.343     & \bf{1.123}\tnote{$\dagger$}  & 7.030   \\ 
 \bottomrule
@@
 
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{rrrrrrr}
-%   \hline
-%  & X1 & X2 & X3 & X4 & X5 & X6 \\ 
-%   \hline
-% 1 & 24.852 & 24.933 & 24.912 & 24.781 & 24.850 & 24.861 \\ 
-%   2 & 1.683 & 1.341 & 1.398 & 1.615 & 1.320 & 1.361 \\ 
-%   3 & 24.401 & 24.649 & 23.695 & 24.295 & 24.684 & 23.118 \\ 
-%   4 & 2.489 & 1.790 & 10.071 & 2.441 & 1.740 & 9.995 \\ 
-%   5 & 20.482 & 22.432 & 9.801 & 20.319 & 22.194 & 9.280 \\ 
-%   6 & 1.683 & 1.378 & 8.049 & 1.398 & 1.197 & 7.022 \\ 
-%    \hline
-% \end{tabular}
-% \end{table}
-
 % \begin{table}[!htp]
@@
 % \begin{threeparttable}
-% 	\caption{Median MSE of GWR coefficient estimates of linear response when the correlation between the parameters is high ($\epsilon=0.1$).}\label{tb:MSElinearHigh}
+% 	\caption{\zc{Median MSE of GWR coefficient estimates of linear response when the correlation between the parameters is high ($\epsilon=0.1$).} \revision{NOTE: to be updated} }\label{tb:MSElinearHigh}
 % 	\begin{tabular}{llcccccc}
 % 		\toprule
-% 		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
-% 		& Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
-% 		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$  & 24.961	&24.991	&24.958	&24.934\tnote{$\dagger$}	&24.992	&25.020 \\
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$ & 0.144&	0.115&	0.103\tnote{$\dagger$} &	0.145&	0.116&	0.104 \\ \midrule
-% 		\multirow{2}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$  & 24.234&	24.518&	23.696&	24.171	&24.497&	23.421\tnote{$\dagger$}  \\
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$   & 0.216	&0.144\tnote{$\dagger$} &	1.024&	0.211&	0.146&	1.027 \\ \midrule
-% 		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$  & 20.882&	22.811&	9.823&	20.770	&22.789	&9.257\tnote{$\dagger$}  \\
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^3)$  & 0.152&	0.120&	0.939&	0.140&	0.112\tnote{$\dagger$} &	0.815 \\ 
+% 		&  & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+%   	\multirow{2}{*}{$V_s$ with $\epsilon=0.1$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+% 		&  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+% 		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.808 &	24.925 &	24.927&	\bf{24.761}\tnote{$\dagger$}  &	24.824 &	24.837 \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.623 &	1.334 &	1.382 &	1.590 &	\bf{1.304}\tnote{$\dagger$}  &	1.352 \\  \midrule
+% 		\multirow{2}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.379 &	24.690 &	23.650 &	24.321  &	24.633 &	\bf{23.416}\tnote{$\dagger$} \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.343 &	\bf{1.683}\tnote{$\dagger$}  &	9.889 &	2.372 &	1.691 &	9.409 \\ \midrule
+% 		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.221 &	21.835 &	9.852 &	19.863 &	21.667 &	\bf{9.383}\tnote{$\dagger$}  \\ 
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.731 &	1.390 &	8.109 &	1.422 &	\bf{1.204}\tnote{$\dagger$}  &	7.013 \\
 % 		\bottomrule
@@
 \begin{threeparttable}
-	\caption{Median MSE of GWR coefficient estimates of linear response when the correlation between the parameters is high ($\epsilon=0.1$).}\label{tb:MSElinearHigh}
-	\begin{tabular}{llcccccc}
+\caption{\zc{Median MSE of GWR coefficient estimates of linear response when the correlation between the parameters is high ($\epsilon=0.1$).}}\label{tb:MSElinearHigh}
+\begin{tabular}{ll|ccc|ccc}
 \toprule
-		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
-   		 & Coefficient & 5  &  9  & AICc & 5   & 9  & AICc \\ \midrule
-		\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 24.808 &	24.925 &	24.927&	24.761\tnote{$\dagger$}  &	24.824 &	24.837 \\ 
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.623 &	1.334 &	1.382 &	1.590 &	1.304\tnote{$\dagger$}  &	1.352 \\  \midrule
-		\multirow{2}{*}{AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.379 &	24.690 &	23.650 &	24.321\tnote{$\dagger$}  &	24.633 &	23.416 \\ 
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 2.343 &	1.683\tnote{$\dagger$}  &	9.889 &	2.372 &	1.691 &	9.409 \\ \midrule
-		\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.221 &	21.835 &	9.852 &	19.863 &	21.667 &	9.383\tnote{$\dagger$}  \\ 
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.731 &	1.390 &	8.109 &	1.422 &	1.204\tnote{$\dagger$}  &	7.013 \\
+\multicolumn{2}{c}{Linear Response with $\epsilon=0.1$} & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+\multirow{2}{*}{$V_s$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+&  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+\multirow{2}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & \bf{24.964}\tnote{$\dagger$}  & 25.000 & 25.018    & 24.970 & 25.006 & 25.031 \\ 
+& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ &  1.455  & 1.181  & 1.047     & 1.456  & 1.180  & \bf{1.044}\tnote{$\dagger$}   \\  \midrule
+\multirow{2}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 24.490 & 24.773 & 23.928    & 24.457 & 24.780 & \bf{23.524}\tnote{$\dagger$}    \\ 
+& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ &  2.168  & \bf{1.464}\tnote{$\dagger$}  & 12.014    & 2.159  & 1.472  & 11.153    \\ \midrule
+\multirow{2}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.247 & 23.376 & 9.668     & 21.100 & 23.330 & \bf{9.093}\tnote{$\dagger$}  \\ 
+& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 1.596 & 1.233  & 8.518     & 1.359  & \bf{1.129}\tnote{$\dagger$}  & 7.676 \\
 \bottomrule
@@
 
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{rrrrrrr}
-%   \hline
-%  & X1 & X2 & X3 & X4 & X5 & X6 \\ 
-%   \hline
-% 1 & 24.808 & 24.925 & 24.927 & 24.761 & 24.824 & 24.837 \\ 
-%   2 & 1.623 & 1.334 & 1.382 & 1.590 & 1.304 & 1.352 \\ 
-%   3 & 24.379 & 24.690 & 23.650 & 24.321 & 24.633 & 23.416 \\ 
-%   4 & 2.343 & 1.683 & 9.889 & 2.372 & 1.691 & 9.409 \\ 
-%   5 & 20.221 & 21.835 & 9.852 & 19.863 & 21.667 & 9.383 \\ 
-%   6 & 1.731 & 1.390 & 8.109 & 1.422 & 1.204 & 7.013 \\ 
-%    \hline
-% \end{tabular}
-% \end{table}
+Tables \ref{tb:MSEquadratic} and \ref{tb:MSEquadraticHigh} \revision{present} the median MSEs \revision{corresponding to the estimation of} quadratic response models for the two scenarios \revision{of low ($\epsilon = 1$) and high ($\epsilon = 0.1$) correlations, respectively}.
+\revision{}
 
-Tables \ref{tb:MSEquadratic} and \ref{tb:MSEquadraticHigh} are the median MSE of the quadratic response for two scenarios: correlation is low and correlation is high.
-Despite the intensity of the correlation, the data fitted by GWR from systematic designs are superior to randomised designs, in terms of having a lower MSE.
+%Despite the intensity of the correlation, the \zc{estimates given} by GWR from systematic designs are superior to randomised designs, in terms of having lower MSE.
 
@@
 \begin{threeparttable}
-\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is low ($\epsilon=1$).}\label{tb:MSEquadratic}
-\begin{tabular}{llcccccc} \toprule
- &  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
- & Coefficient & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule 
-\multirow{3}{*}{NS}   & $\zc{\hat{\bm{\beta}}}_0$ & 25.186 & 25.200 & 25.224 & 25.176 & 25.140\tnote{$\dagger$} & 25.197 \\ 
- & $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 9.870 & 5.490 & 5.662 & 9.529 & 5.167\tnote{$\dagger$} & 5.438 \\ 
-  & $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 5.130 & 3.064 & 3.177 & 4.938 & 3.001\tnote{$\dagger$} & 3.147 \\  \midrule
-\multirow{3}{*}{AR1$\otimes$AR1}  & $\zc{\hat{\bm{\beta}}}_0$ & 25.123 & 25.168 & 27.760 & 25.072\tnote{$\dagger$} & 25.133 & 26.707 \\ 
-& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 21.213 & 11.472 & 113.436 & 19.230 & 10.014\tnote{$\dagger$} & 91.858 \\ 
-& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 10.473 & 5.921 & 54.624 & 9.584 & 5.304\tnote{$\dagger$} & 44.645 \\  \midrule
-\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$  & 20.329 & 22.047 & 16.455 & 20.111 & 21.933 & 14.570\tnote{$\dagger$} \\ 
-&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 12.378 & 7.026 & 100.752 & 8.590 & 4.663\tnote{$\dagger$} & 80.409 \\ 
-& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 6.295 & 3.648 & 49.783 & 4.467 & 2.774\tnote{$\dagger$} & 39.595 \\ 
+\caption{\zc{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is low ($\epsilon=1$).}}\label{tb:MSEquadratic}
+\begin{tabular}{ll|ccc|ccc}
+\toprule
+\multicolumn{2}{c}{Quadratic Response with $\epsilon=1$} & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+\multirow{2}{*}{$V_s$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+		  &  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+\multirow{3}{*}{NS}     & $\zc{\hat{\bm{\beta}}}_0$  & 25.184 & 25.106 & 25.086    & 25.172 & 25.109 & \bf{25.072}\tnote{$\dagger$}   \\
+   &  $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 7.215  & 3.385  & 1.480     & 7.045  & 3.297  & \bf{1.471}\tnote{$\dagger$}      \\
+   & $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 4.016  & 2.157  & \bf{1.232}\tnote{$\dagger$}     & 3.871  & 2.090  & 1.243     \\ \midrule
+\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$  & 25.012     & \bf{25.005}\tnote{$\dagger$}  & 29.797    & 25.008 & 25.013 & 27.712    \\
+   &  $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 16.741 & 7.1907  & 146.097   & 16.730 & \bf{7.1906}\tnote{$\dagger$}   & 123.256   \\
+   & $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 8.601  & 3.979  & 70.112    & 8.595  & \bf{3.933}\tnote{$\dagger$}   & 59.913    \\ \midrule
+\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$  & 21.503 & 23.470 & 18.331    & 21.305 & 23.359 & \bf{15.800}\tnote{$\dagger$}      \\
+   & $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 10.397 & 4.790  & 121.474   & 7.368  & \bf{3.276}\tnote{$\dagger$}    & 98.902    \\
+   & $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$ & 5.470  & 2.808  & 58.626    & 3.912  & \bf{2.068}\tnote{$\dagger$}   & 47.653    \\ 
    \bottomrule
@@
 % \begin{threeparttable}
-% 	\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is high ($\epsilon=0.1$).}\label{tb:MSEquadraticHigh}
+% 	\caption{\zc{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is high ($\epsilon=0.1$).}}\label{tb:MSEquadraticHigh}
 % 	\begin{tabular}{llcccccc} \toprule
-% 		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
-% 		$\epsilon=0.1$  & Coefficients & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
-% 		\multirow{3}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$  & 25.075 & 25.067 & 25.015  & 25.082 & 25.060 & 25.012\tnote{$\dagger$} \\
-% 		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 6.683  & 3.466  & 1.478\tnote{$\dagger$} & 7.353  & 3.472  & 1.506 \\
-% 		&$\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 3.779  & 2.101  & 1.222\tnote{$\dagger$} & 3.806  & 2.124  & 1.284 \\  \midrule
-% 		\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$  & 25.103 & 25.223 & 29.266  & 25.033 & 25.032\tnote{$\dagger$} & 27.378 \\
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 16.260 & 6.845  & 130.335 & 16.228 & 6.314\tnote{$\dagger$}  & 112.599  \\
-% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 8.488  & 3.931  & 61.765  & 7.915  & 3.533\tnote{$\dagger$}  & 54.866  \\  \midrule
-% 		\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.780 & 23.622 & 18.832  & 21.409 & 23.296 & 15.728\tnote{$\dagger$}  \\
-% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 11.367 & 5.085  & 122.638 & 6.205  & 2.892\tnote{$\dagger$}  & 88.256 \\
-% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.979  & 2.981  & 60.298  & 3.025  & 1.803\tnote{$\dagger$}  & 43.156  \\ \bottomrule
+% 		&  & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+%   	\multirow{2}{*}{$V_s$ with $\epsilon=0.1$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+% 		  &  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+% 		\multirow{3}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$  & 25.133 & 25.108 & 25.116  & 25.146 & \bf{25.099}\tnote{$\dagger$} & 25.146 \\
+% 		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 9.273  & 5.218  & 5.354 & 8.803  & \bf{4.994}\tnote{$\dagger$}  & 5.152 \\
+% 		&$\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 4.846  & 2.901  & 3.009 & 4.687  & \bf{2.822}\tnote{$\dagger$}  & 2.908 \\  \midrule
+% 		\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$  & 24.916 & 24.983 & 27.370  & \bf{24.801}\tnote{$\dagger$} & 24.971 & 26.101 \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 19.312 & 10.594  & 104.207 & 19.721 & \bf{10.200}\tnote{$\dagger$}  & 93.399  \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 9.586  & \bf{5.417}\tnote{$\dagger$}  & 52.289  & 10.187  & 5.882  & 44.602  \\  \midrule
+% 		\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.661 & 22.407 & 16.603  & 20.215 & 21.972 & \bf{14.505}\tnote{$\dagger$}  \\
+% 		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 11.689 & 6.585  & 100.833 & 8.148  & \bf{4.351}\tnote{$\dagger$}  & 85.996 \\
+% 		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.976  & 3.568  & 47.692  & 4.194  & \bf{2.459}\tnote{$\dagger$}  & 40.541  \\ \bottomrule
 % 	\end{tabular}
@@
 \begin{threeparttable}
-	\caption{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is high ($\epsilon=0.1$).}\label{tb:MSEquadraticHigh}
-	\begin{tabular}{llcccccc} \toprule
-		&  & \multicolumn{3}{c}{Randomised} & \multicolumn{3}{c}{Systematic} \\ 
-		$\epsilon=0.1$  & Coefficients & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
-		\multirow{3}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$  & 25.133 & 25.108 & 25.116  & 25.146 & 25.099\tnote{$\dagger$} & 25.146 \\
-		&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 9.273  & 5.218  & 5.354 & 8.803  & 4.994\tnote{$\dagger$}  & 5.152 \\
-		&$\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 4.846  & 2.901  & 3.009 & 4.687  & 2.822\tnote{$\dagger$}  & 2.908 \\  \midrule
-		\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$  & 24.916 & 24.983 & 27.370  & 24.801\tnote{$\dagger$} & 24.971 & 26.101 \\
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 19.312 & 10.594  & 104.207 & 19.721 & 10.200\tnote{$\dagger$}  & 93.399  \\
-		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 9.586  & 5.417\tnote{$\dagger$}  & 52.289  & 10.187  & 5.882  & 44.602  \\  \midrule
-		\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 20.661 & 22.407 & 16.603  & 20.215 & 21.972 & 14.505\tnote{$\dagger$}  \\
-		& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 11.689 & 6.585  & 100.833 & 8.148  & 4.351\tnote{$\dagger$}  & 85.996 \\
-		& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.976  & 3.568  & 47.692  & 4.194  & 2.459\tnote{$\dagger$}  & 40.541  \\ \bottomrule
+	\caption{\zc{Median MSE of GWR coefficient estimates of quadratic response when the correlation amongst the parameters is high ($\epsilon=0.1$).}}\label{tb:MSEquadraticHigh}
+\begin{tabular}{ll|ccc|ccc}
+\toprule
+\multicolumn{2}{c}{Quadratic Response with $\epsilon=0.1$} & \multicolumn{3}{c}{Randomised Design} & \multicolumn{3}{c}{Systematic Design} \\ \midrule
+\multirow{2}{*}{$V_s$} & \multirow{2}{*}{Coefficients}  & \multicolumn{6}{c}{Bandwidth}\\ 
+		  &  & 5  & 9  & AICc & 5  & 9  & AICc \\ \midrule
+\multirow{3}{*}{NS} & $\zc{\hat{\bm{\beta}}}_0$  & 25.076 & 25.036 & 25.017    & 25.076 & \bf{25.006}\tnote{$\dagger$} & 25.013      \\
+&$\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$  & 6.974  & 3.281  &  \bf{1.473}\tnote{$\dagger$} & 7.011  & 3.326  & 1.494      \\
+&$\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 3.900  & 2.093  & \bf{1.224}\tnote{$\dagger$}  & 3.888  & 2.114  & 1.225\\  \midrule
+\multirow{3}{*}{AR1$\otimes$AR1} & $\zc{\hat{\bm{\beta}}}_0$ & \bf{24.993}\tnote{$\dagger$} & 25.051 & 29.454    & 25.027 & 25.032 & 27.809\\
+& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 16.835 & 7.350  & 137.643   & 16.678 & \bf{7.220}\tnote{$\dagger$}  & 123.024  \\
+& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 8.547  & 4.065  & 65.609    & 8.413  & \bf{3.955}\tnote{$\dagger$} & 57.375      \\  \midrule
+\multirow{3}{*}{\Matern} & $\zc{\hat{\bm{\beta}}}_0$ & 21.542 & 23.376 & \bf{16.560}\tnote{$\dagger$}  & 20.837 & 23.039 & 16.630    \\
+& $\zc{\hat{\bm{\beta}}}_1 (\times 10^4)$ & 11.864 & 4.953  & 108.094   & 8.248  & \bf{3.532}\tnote{$\dagger$}  & 95.428   \\
+& $\zc{\hat{\bm{\beta}}}_2 (\times 10^8)$  & 5.389  & 3.121  & 48.640    & 3.506  & \bf{1.940}\tnote{$\dagger$}  & 38.378    \\ \bottomrule
 \end{tabular}
@@
 
-% \begin{table}[ht]
-% \centering
-% \begin{tabular}{rrrrrrr}
-%   \hline
-%  & X1 & X2 & X3 & X4 & X5 & X6 \\ 
-%   \hline
-% 1 & 25.133 & 25.108 & 25.116 & 25.146 & 25.099 & 25.146 \\ 
-%   2 & 9.273 & 5.218 & 5.354 & 8.803 & 4.994 & 5.152 \\ 
-%   3 & 4.846 & 2.901 & 3.009 & 4.687 & 2.822 & 2.908 \\ 
-%   4 & 24.916 & 24.983 & 27.370 & 24.801 & 24.971 & 26.101 \\ 
-%   5 & 19.312 & 10.594 & 104.207 & 19.721 & 10.200 & 93.399 \\ 
-%   6 & 9.586 & 5.417 & 52.289 & 10.187 & 5.882 & 44.602 \\ 
-%   7 & 20.661 & 22.407 & 16.603 & 20.215 & 21.972 & 14.505 \\ 
-%   8 & 11.689 & 6.585 & 100.833 & 8.148 & 4.351 & 85.996 \\ 
-%   9 & 5.976 & 3.568 & 47.692 & 4.194 & 2.459 & 40.541 \\ 
-%    \hline
-% \end{tabular}
-% \end{table}
+\subsection{\zc{Comparison of density plot}}
 
-\subsection{ANOVA}\label{Sec:anova}
+\zc{Figure \ref{fig:combinedbeta_mat} illustrate the density plots comparing the true coefficients of $\beta_0$, $\beta_1$, and $\beta_2$ with their estimates derived from both randomised and systematic designs with \Matern covariance and low within-grid correlation and fitted by GWR with bandwidth 9.
+The plots reveal that the true coefficients are well-represented by the GWR estimates, with the systematic design showing slightly tighter distributions compared to the randomised design of $\hat{\beta}_1$ and $\hat{\beta}_2$.
+This suggests the systematic design provides more precise estimates under the given conditions.}
 
-Furthermore, ANOVA techniques were used for the analyses of the above results.
-The analyses were performed for two scenarios of different responses separately.
-For each response, the coefficients were also taken into account in the model.
-The objective of the analysis was to investigate the five main factors: two types of design, three bandwidths, three covariance matrices, coefficients $\bm{\beta}$ and correlation $\epsilon$.
-The significance patterns of the second-order interactions were also of interest.
-The results are listed in Table \ref{tb:LMMoutput}.
+\begin{figure}[!htp]
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{density_mat_1k_b0.pdf}
+        %\caption{Plot 1}
+        \label{fig:beta0_mat}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{density_mat_1k_b1.pdf}
+        %\caption{Plot 2}
+        \label{fig:beta1_mat}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{density_mat_1k_b2.pdf}
+        %\caption{Plot 3}
+        \label{fig:beta2_mat}
+    \end{subfigure}
+    \caption{\zc{Density plots comparing the true coefficients of $\beta_0$ (left), $\beta_1$ (middle), and $\beta_2$ (right) with their estimates from GWR with bandwidth 9, based on 1000 simulations.}}
+    \label{fig:combinedbeta_mat}
+\end{figure}
 
-The results are consistent with what was observed in the previous subsection that, for the linear response, the difference between the randomised and systematic designs was not significant.
-However, for the quadratic response, the design and its interactions with the bandwidth and the coefficients were significant.
-For both scenarios, the intensity of the correlation and all its interactions were not significant (Table \ref{tb:LMMoutput}).
-Therefore, the GWR performs similarly with a low or high correlation between coefficients.
-Also of note was that bandwidth and its second-order interactions with variables other than correlation were found to be significant for both response types.
+% \subsection{ANOVA}\label{Sec:anova}
+
+% \revision{The analysis of variance (ANOVA) was used to investigate whether the differences in the results for the two designs are statistically significant and to identify the main simulation factors contributing to these differences} \zc{of the coefficients}.
+The analyses were performed separately for \zc{each coefficient} the two \revision{response models}.
+The \revision{main effects of simulation factors considered in the ANOVA models include} two designs, three bandwidths, three covariance matrices, and \zc{two types of spatial} correlation.
+\revision{We have also included all the second-order interactions in the ANOVA models}.
+The \revision{ANOVA} results are \revision{presented below} in Table~\ref{tb:LMMoutput}.
+
+% \zc{The ANOVA results indicate that the main effects of design, bandwidth, and covariance are highly significant in both the linear and quadratic models at the 5\% significance level.} 
+% \st{The ANOVA results are consistent with what was observed in the previous subsection.
+For the linear response, the difference between the randomised and systematic design is not statistically significant at the 5\% significance level.
+In contrast, for the quadratic response model, the difference in simulation results due to different designs is statistically significant ($p$-value = 0.0177) at the 5\% significance level.}
+% \zc{Bandwidth selection and covariance are all significant factors influencing the difference in results between the two design types.
+It is recommended that the bandwidth should be selected according to the trial design.
+Interestingly, the correlation within each grid is not an important factor for linear response.
+The interaction between design and bandwidth is significant in the quadratic response but not in the linear response.
+The interaction between bandwidth and covariance is significant in both response assumptions.
+These results suggest that bandwidth and covariance are crucial factors influencing GWR, with significant interaction effects.}
+
+% % \begin{table}[!htp]
+% % \centering
+% % \caption{\zc{ANOVA results for the two response models showing the statisical significances of main effects and second-order interactions.
+Values reported are degrees of freedom (Df), the sum of squared errors (Sum Sq), and p-values of F tests (Pr($>$F)).}}\label{tb:LMMoutput}
+% % \begin{tabular}{r | lll | lll} \toprule
+% % 		& \multicolumn{3}{c|}{Linear}  & \multicolumn{3}{c}{Quadratic}  \\
+% % 	  & Df & Sum Sq & Pr($>$F) & Df & Sum Sq & Pr($>$F) \\ \midrule
+% % Design                       & 1  & 50     & 0.541 & 1  & 756   & 0.0177 \\ 
+% % Bandwidth                    & 2  & 72446  & $<0.001$ & 2  & 882   & 0.0377 \\ 
+% % Covariance ($V_s$)           & 2  & 167132 & $<0.001$ & 2  & 63668 & $<0.001$ \\ 
+% % Correlation ($\epsilon$)     & 1  & 16     & 0.729 & 1  & 9     & 0.8015 \\ 
+% % Design$\times$Bandwidth      & 2  & 46     & 0.841 & 2  & 1232  & 0.0103  \\ 
+% % Design$\times$Covariance ($V_s$)& 2  & 27     & 0.903 & 2  & 404   & 0.2224 \\ 
+% % Bandwidth$\times$Covariance ($V_s$)  & 4  & 120500 & $<0.001$ & 4  & 36174 & $<0.001$ \\ 
+% % Design$\times$Correlation ($\epsilon$) & 1  & 1     & 0.918 & 1  & 68    & 0.4777 \\ 
+% % Bandwidth$\times$Correlation ($\epsilon$) & 2  & 1     & 0.995 & 2  & 74    & 0.7604 \\ 
+% % Covariance ($V_s$)$\times$Correlation ($\epsilon$)   & 2  & 34     & 0.881 & 2  & 23    & 0.9181 \\ 
+% % \bottomrule
+% % \end{tabular}
+% % \end{table}
 
@@
 % \centering
-% 	\caption{ANOVA analyses were conducted on the main factors and their second order interactions.
-The table lists degrees of freedom (Df), sum of squared errors (Sum Sq) and p-values of F tests (Pr($>$F)).
-}\label{tb:LMMoutput_old}
-% 	\begin{tabular}{r | lll | lll}
-% 		\toprule
-% 		 & \multicolumn{3}{c|}{Linear}  & \multicolumn{3}{c}{Quadratic}  \\
-%     & Df & Sum Sq  & Pr(\textgreater{}F) & Df & Sum Sq  & Pr(\textgreater{}F) \\ \midrule 
-% Design & 1  & 8.46  & 0.0935  & 1  & 74.03 & \textless{}0.001  \\
-% Bandwidth & 2  & 7453.09 & \textless{}0.001  & 2  & 90.29  & \textless{}0.001  \\
-% Covariance ($V_s$)  & 2  & 16958.42  & \textless{}0.001  & 2  & 6122.84 & \textless{}0.001 \\
-% Coefficients ($\zc{\bm{\beta}}$)  & 1  & 903705.52 & \textless{}0.001  & 2  & 1419372.21 & \textless{}0.001  \\
-% Correlation  ($\epsilon$)  & 1  & 5.63  & 0.171   & 1  & 0.07  & 0.8976  \\
-% Design:Bandwidth  & 2  & 9.21 & 0.216  & 2  & 113.48   & \textless{}0.001  \\
-% Design:Covariance & 2  & 3.91 & 0.5217  & 2  & 37.55  & 0.0134 \\
-% Design:Coefficients  & 1  & 8.45 & 0.0935  & 2  & 147.55 & \textless{}0.001  \\
-% Design:Correlation  & 1  & 0  & 0.9832  & 1  & 0.01  & 0.9541  \\
-% Bandwidth:Covariance   & 4  & 12283.13  & \textless{}0.001  & 4  & 3135.47  & \textless{}0.001  \\
-% Bandwidth:Coefficients & 2  & 7456.81 & \textless{}0.001  & 4  & 179.38 & \textless{}0.001  \\
-% Bandwidth:Correlation  & 2  & 5.95  & 0.3716  & 2  & 0.85  & 0.9073  \\
-% Covariance:Coefficients  & 2  & 16959.68  & \textless{}0.001  & 4  & 12248.74 & \textless{}0.001  \\
-% Covariance:Correlation & 2  & 0.26  & 0.9572  & 2  & 11.57  & 0.2649  \\
-% Coefficients:Correlation & 1  & 5.63  & 0.171   & 2  & 0.15  & 0.9834  \\ \bottomrule  
+% \caption{\zc{ANOVA results for the two response models showing the statisical significances of main effects and second-order interactions.
+Values reported are degrees of freedom (Df), the sum of squared errors (Sum Sq), and p-values of F tests (Pr($>$F)).}}\label{tb:LMMoutput}
+% \resizebox{\textwidth}{!}{%
+% \begin{tabular}{r|lll|lll|lll} \toprule
+%  & \multicolumn{3}{c|}{Linear $\beta_1$} & \multicolumn{3}{c}{Quadratic $\beta_1$} & \multicolumn{3}{c}{Quadratic $\beta_2$}   \\ 
+%  & Df  & Sum Sq  ($\times 10^{6}$)  & Pr($>$F)  & Df   & Sum Sq   & Pr($>$F)& Df & Sum Sq ($\times 10^{12}$)   & Pr($>$F)\\ \midrule
+% Design& 1   & 3.2 & $<0.001$  & 1& 0.0016   & $<0.001$  & 1  & 4 & $<0.001$ \\
+% Bandwidth   & 2   & 2441.8 & $<0.001$  & 2& 0.4151   & $<0.001$  & 2  & 907 & $<0.001$ \\
+% Covariance ($V_s$)  & 2   & 914.4 & $<0.001$  & 2& 0.1487   & $<0.001$   & 2  & 332 & $<0.001$ \\
+% Correlation ($\epsilon$)  & 1   & $<0.1$ & 0.561& 1& 0.0001   & $<0.001$& 1  & 1 & $<0.001$  \\
+% Design$\times$Bandwidth & 2   & 2.6 & $<0.001$  & 2& 0.0020   & $<0.001$   & 2  & 4.5 & $<0.001$ \\
+% Design$\times$Covariance ($V_s$)& 2   & 1.8 & $<0.001$  & 2& 0.0008   & $<0.001$  & 2  & 2 & $<0.001$ \\
+% Design$\times$Correlation ($\epsilon$)& 1   & 1 & 0.284& 1& 0.0001   & $<0.001$  & 1  & 0.1 & 0.025 \\
+% Bandwidth$\times$Covariance ($V_s$) & 4   & 1405.3 & $<0.001$  & 4& 0.2293   & $<0.001$  & 4  & 507 & $<0.001$ \\
+% Bandwidth$\times$Correlation ($\epsilon$) & 2   & $<0.1$ & 0.986& 2& 0.0002   & $<0.001$  & 2  & 1.70 & $<0.001$ \\
+% Covariance ($V_s$)$\times$Correlation ($\epsilon$)& 2   & 0.3 & 0.082& 2& 0.0001   & 0.011 & 2  & 0.9 & $<0.001$   \\ \bottomrule
 % \end{tabular}
+% }
 % \end{table}
 
-\begin{table}[!htp]
-\centering
-\caption{ANOVA analyses were conducted on the main factors and their second order interactions.
-The table lists degrees of freedom (Df), sum of squared errors (Sum Sq) and p-values of F tests (Pr($>$F)).}\label{tb:LMMoutput}
-\begin{tabular}{r | lll | lll} \toprule
-		& \multicolumn{3}{c|}{Linear}  & \multicolumn{3}{c}{Quadratic}  \\
-	  & Df & Sum Sq & Pr($>$F) & Df & Sum Sq & Pr($>$F) \\ \midrule
-Design   & 1.000 & 101.843 & 0.390 & 1.000 & 889.015 & 0.011 \\ 
-Bandwidth  & 2.000 & 64905.377 & $<0.01$ & 2.000 & 996.936 & 0.027 \\ 
-Covariance ($V_s$) & 2.000 & 188790.814 & $<0.01$ & 2.000 & 82458.618 & $<0.01$ \\ 
-Correlation ($\epsilon$) & 1.000 & 34.065 & 0.619 & 1.000 & 10.147 & 0.786 \\ 
-Design:Bandwidth & 2.000 & 36.983 & 0.874 & 2.000 & 1181.450 & 0.014 \\ 
-Design:Covariance ($V_s$)       & 2.000 & 43.486 & 0.854 & 2.000 & 579.136 & 0.123 \\ 
-Design:Correlation ($\epsilon$) & 1.000 & 5.912 & 0.836 & 1.000 & 2.800 & 0.887 \\ 
-Bandwidth:Covariance ($V_s$)  & 4.000 & 107351.708 & $<0.01$ & 4.000 & 24235.863 & $<0.01$ \\ 
-Bandwidth:Correlation ($\epsilon$)    & 2.000 & 32.424 & 0.889 & 2.000 & 0.938 & 0.997 \\ 
-Covariance ($V_s$):Correlation ($\epsilon$)          & 2.000 & 62.468 & 0.797 & 2.000 & 113.953 & 0.662 \\ 
-		\bottomrule
-\end{tabular}
-\end{table}
+% \zc{In designing an OFE trial, it is crucial to consider the types of trial design and the covariance matrix depending on the purpose of the experiment.
+Furthermore, when fitting the GWR model to OFE trial data, the bandwidth selection is a key factor that requires careful consideration.}
 
@@
 
-\zc{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 from a randomised design and a systematic design using the same simulated coefficients of a quadratic curve under the assumption of $\AR\otimes\AR$ spatial covariance and low within-grid correlation.
+\zc{Figure \ref{fig:yieldmap} is the simulated crop yield map with the assumption of a quadratic response curve and \Matern spatial covariance and low within-grid correlation.
+These two yield maps have the same coefficients but different yields due to different treatment layouts.}
+
+\begin{figure}[!htp]
+\centering
+    \begin{subfigure}[t]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{quad_random_yield_mat.pdf}
+		%\caption{}
+    \end{subfigure}
+    %\hspace{0.05\textwidth}
+    \begin{subfigure}[t]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{quad_syst_yield_mat.pdf}
+		%\caption{}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{quad_diff_yield_mat.pdf}
+		%\caption{}
+    \end{subfigure}
+	\caption{\zc{Simulated yield map of a randomised design (\textit{top}), and a systematic design (\textit{middle}), and the difference of these two designs (\textit{bottom}).}}\label{fig:yieldmap}
+\end{figure}
+
+\zc{Figure \ref{fig:optNmap} illustrates an example of the optimal Nitrogen rate (kg/ha) map estimated by GWR with a bandwidth of 9 using the above yield data.
 The optimal rate at grid $i$ is given by $\hat{N}_i = -\hat{\beta}_{1i}/(2\hat{\beta}_{2i})$ with constraints between 0 and 140, $i=1,\ldots,n$.
-For the randomised design, GWR failed to estimate the central part of the paddock.
+For the randomised design, GWR underestimated the right part of the paddock.
 On the contrary, the estimated map from the systematic design is more consistent.}
 
-\begin{figure}[H]
+\begin{figure}[!htp]
 	\begin{subfigure}[t]{0.45\textwidth}
 		\centering
-		\includegraphics[width=\linewidth]{Expt/optN_syst_AR1B9.pdf}
+		\includegraphics[width=\linewidth]{optN_rand_matB9.pdf}
 		%\caption{}
@@
 
-% For linear response, the type of design is not a key factor that the design and its interactions with other factors are not significant.
-On the contrary, if the response is quadratic, design becomes a key factor and the interactions are significant as well.
-For both scenarios, the correlation intensity and most of its interactions are not significant.
-Hence, either low or high correlation between coefficients works well with GWR.
-Moreover, bandwidth selection should be based on the design rather than optimality criteria.
-The results are consistent with the above boxplots.
-
-% \revision{Exclude the following section about AICc --- this is completely irrelevant for this paper. You can relegate this to the supplement file or in the appendix if you like.}
-%  \subsection{AICc bandwidth selection}\label{Sec:bandselect}
-
-% From the simulation study, we found that the bandwidth given by AICc skewed to 1 if spatial covariance was included in the model, for all types of the design and the nature of the response.
-If spatial covariance was not introduced, the GWR tended to use all data in one row (Figure \ref{fig:histband}).
-
-% \begin{figure}[!htp]
-% 	\begin{subfigure}[t]{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/BandwidthLinear.pdf}
-% 		\caption{Histogram of optimal bandwidth for linear response.}
-% 	\end{subfigure}
-% 	\hspace{0.05\textwidth}
-% 	\begin{subfigure}[t]{0.45\textwidth}
-% 		\centering
-% 		\includegraphics[width=\linewidth]{Expt/BandwidthQuadra.pdf}
-% 		\caption{Histogram of optimal bandwidth for quadratic response.}
-% 	\end{subfigure}
-% 	\caption{Histogram of optimal bandwidth found by AICc for linear and quadratic response. }\label{fig:histband}
-% \end{figure}
-
 \section{Discussion}\label{Sec:Dis}
@@
 Agronomists and biometricians generally prefer randomised designs for OFE trials.
-According to the performance metrics used, our simulation study shows a systematic design performs either preferably or similarly to a randomised design for the purposes of creating a varying treatment map.
-The differentiating factors included primarily the response type and the spatial covariance model, while the correlation amongst the treatment coefficients was not found to be important.
-These are factors that can be assessed by the farmer beforehand, and this should dictate which design should be used.
-However, given that a systematic design is easier to implement in the field, and shows little downside for the purposes of creating a varying treatment map, we will advocate for the use of systematic designs.
+\zc{This is likely due to their experience with small-plot field experiments, where randomised designs are employed.} \zc{O}ur simulation study shows a systematic design performs either preferably or similarly to a randomised design for the purposes of creating a varying treatment map \zc{when using the performance metrics stated}.
+The differentiating factors \zc{primarily included} the response type and the spatial covariance model, while the correlation amongst the treatment coefficients \zc{is} not found to be important.
+These are factors that can be assessed by the farmer \zc{and their agronomists} beforehand, and this should dictate which design should be used.
+\zc{G}iven that a systematic design is easier to implement in the field, and shows little downside to \zc{creating} a varying treatment map, the use of systematic designs \zc{is recommended}.
 
 %2. How response type affected the performance, and what this means
-The response type was the main differentiating factor between randomised and systematic designs.
-When the response was quadratic, the systematic design performed favourably, which contrasted the result for the linear design.
-Given this, if a farmer expects an approximately linear response in the field, then the selection of the design may not be important.
+The response type \zc{is} the main differentiating factor between randomised and systematic designs.
+When the response \zc{is} quadratic, the systematic design performed favourably, \zc{contrasting with} the result \zc{of} the linear design.
+Given this, if an approximately linear response \zc{is expected} in the field, then the selection of the design may not be important.
 However, given the variable nature of the relationship between response and treatment over a large field (see \textcite{Rakshit2020Novel}), it may be wise to implement a systematic design for the potential outcome of a quadratic relationship.
@@
 %- Is a \Matern class more realistic and what are its limitations? %-
-Another consideration for farmers as to which design to use is the expected spatial covariance structure in the field.
-When no spatial structure was simulated, the differences between the prediction from the systematic and random design were minimal.
+
+Another consideration for \zc{agronomists and biometricians when selecting} which design to use is the expected spatial covariance structure in the field.
+When no spatial structure was simulated, the differences between the prediction from the systematic and random design \zc{are} minimal.
 This result should be expected given that if there are no spatial autocorrelations, then the individual query grids are independent observations, and therefore the design is not important.
-However, when a first-order auto-regressive structure was simulated, the differences were noticeable when a quadratic response was used, showing systematic designs to be preferential.
+However, when a first-order auto-regressive structure was simulated, the differences \zc{are} noticeable when a quadratic response was used, showing systematic designs to be preferential.
 The largest difference between the two designs occurred when considering the \Matern spatial covariance structure, which showed a clear preference for systematic designs when a quadratic response was considered, and also a small preference for systematic designs for a linear response.
-Therefore, only if spatial variability was predicted to be negligible in the field would using a randomised design be reasonable given a quadratic response.
-This assumption of negligible spatial variability would be difficult to reason with given the large fields used in on-farm experimentation (add reference), meaning that in the application a systematic design should be used.
+Therefore, only if spatial variability \zc{is} predicted to be negligible in the field would using a randomised design be reasonable given a quadratic response.
+This assumption of negligible spatial variability would be difficult to reason with given the large fields used in on-farm experimentation, meaning that in the application a systematic design should be used.
 
@@
 %3. Bandwidth selection and why that is important [good]
-There were found to be significant deficiencies in using AICc for bandwidth selection.
-The AICc-minimising bandwidths skewed to 1 and, in a few cases, ended in 93 (number of rows).
-Even though the bandwidth was optimal according to AICc, the MSE was higher than when using a fixed bandwidth.
-Therefore, we recommended using the fixed bandwidth based on the experimental design (5 or 9 in this case), rather than the recommended bandwidth from AICc which is prone to either over-fitting or being too generalised.
-Selecting the bandwidth based on the experimental design is also theoretically better since only a single measurement is observed in each grid, all levels of the treatment factor should be included in a GWR window at the same time to interpolate the %quadratic curve
-relationship. Otherwise, the interpolation is incomplete if more than one level is missing.
+There \zc{are} significant deficiencies \zc{found} in using AICc for bandwidth selection.
+The AICc-\zc{selected} bandwidths skewed to 1 and, in a few cases, ended in 93 (number of rows).
+Even though the bandwidth \zc{is} optimal according to AICc, the MSE \zc{is} higher than when using a fixed bandwidth.
+Therefore, a fixed bandwidth based on the experimental design (5 or 9 in this case) \zc{is recommended}, rather than \zc{AICc-selected bandwidth}.
+Selecting the bandwidth based on the experimental design is also theoretically better since \zc{when} only a single measurement is observed in each grid, all levels of the treatment factor should be included in a GWR window at the same time to interpolate the relationship.
+\zc{If more than one level is missing, then the interpolation is incomplete.}
+
+\zc{Our study employs simulation to evaluate the effectiveness of GWR in estimating coefficients for both randomised and systematic designs.
+However, a potential drawback of using simulation is its high dependency on the assumptions underlying the parametric model.
+If these assumptions are incorrect or fail to accurately represent real-world conditions, the simulation results may not reliably reflect the actual scenario.}
 
@@
 
-Agronomists and biometricians generally prefer randomised designs for OFE trials.
+% Agronomists and biometricians generally prefer randomised designs for OFE trials.
 With the purpose of creating a varying treatment map, our simulation study proves that a systematic design produces better performance metrics, under particular circumstances, than a randomised design for large on-farm trials in terms of robustness and smaller MSE on coefficients.
@@
 
+\zc{This research offers a number of recommendations for agronomists and biometricians for designing OFE trials.}
+\zc{
+\begin{itemize}
+    \item Systematic designs are suitable for OFE trials, particularly when the results will be used to develop a variable rate map for the treatment, such as fertiliser. 
+    \item Incorporation of a quadratic function for GWR is preferred for systematic designs when spatial variability is present.
+    \item Using a fixed bandwidth for GWR analysis based on experimental design, such as the number of treatments. 
+\end{itemize}
+}
 % Perhaps we add a comment along the lines - "Further research is needed in the case of OFE (and GWR?) when it comes to more complex designs such as chequerboard, donut etc."
@@
 
-Curtin Biometry and Data Analytics (CBADA) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
+Curtin Biometry and \zc{Agricultural} Data Analytics (CBADA) gratefully acknowledges the support from the Grains Research and Development Corporation of Australia (GRDC).
 

### 2024-08-23 RCode/OFEExptNewParaSimu2024.R

@@ -1,0 +1,1249 @@
+source("Initialization.R")
+
+b0 <- 65
+b1 <- 0.05
+b2 <- -0.0003
+
+# x1 <- seq(0,140,length=5)
+x1 <- c(0,39,50.6,75.4,99.8,124.6)
+y1 <- b0 + b1*x1 + b2*x1^2
+
+dat1 <- data.frame(x=x1,y=y1)
+
+# x2 <- seq(0,140,length=100)
+x2 <- c(0,39,50.6,75.4,99.8,124.6)
+y2 <- b0 + b1*x2+b2*x2^2
+
+dat2 <- data.frame(x=x2,y=y2)
+
+ggplot(data=dat1) + geom_point(aes(x,y),size=3) + 
+  scale_x_continuous(labels = x1,breaks = x1) +
+  geom_line(data=dat2,aes(x,y)) + thm1 +
+  xlab("Nitrogen Level") + ylab("Yield (quintals/ha)")
+
+
+y3 <- b0 + b1*x1
+dat3 <- data.frame(x=x1,y=y3)
+
+ggplot(data=dat3) + geom_point(aes(x,y),size=3) + 
+  scale_x_continuous(labels = x1,breaks = x1) +
+  geom_line(aes(x,y)) + thm1 +
+  xlab("Nitrogen Level") + ylab("Yield (quintals/ha)")
+
+
+
+
+# y <- b0 + b1*x
+# 
+# plot(x,y)
+
+
+####### parameter preparation #########
+
+M <- 1000 ## simulation iterations
+
+paralist <- list(
+  Nitro  = seq(0,140,length=5),
+  nRep   = 4,
+  nRow   = 93,
+  b_0    = 65,
+  b_1    = 0.05,
+  b_2    = -0.0003,
+  sig_u0 = 5,
+  sig_u1 = 0.01,
+  sig_u2 = 0.0001,
+  rho_range = 0.15,
+  rho_row   = 0.5
+)
+lev    <- 2  # linear trend
+nRange <- 20
+nRow   <- paralist$nRow
+
+
+##### simulation study data generating functions #######
+SimuGenDat_Lin <- function(paras,covmat,eta){
+  
+  nitro  <- sample(paras$Nitro)
+  
+  nRep   <- paras$nRep
+  nRange <- nRep * length(nitro)
+  nRow   <- paras$nRow
+  N      <- nRange * nRow
+  
[…]

### 2024-08-23 RCode/OFEExptNewParaSimu2024Parallel.R

@@ -1,0 +1,2272 @@
+m0 <- function (mu, Sigma, tol = 1e-06) {
+  p <- length(mu)
+  if (!all(dim(Sigma) == c(p, p))) 
+    stop("incompatible arguments")
+  eS <- eigen(Sigma, symmetric = TRUE, EISPACK = TRUE)
+  ev <- eS$values
+  if (!all(ev >= -tol * abs(ev[1L]))) 
+    stop("'Sigma' is not positive definite")
+  list(eSv=eS$vector,ev=ev, dd=diag(sqrt(pmax(ev, 0)), p))
+}
+
+m1 <- function(n,mu,eL,fancy=FALSE) {
+  p <- length(mu)
+  X <- matrix(rnorm(p * n), n)
+  X <- drop(mu) + eL$eSv %*% eL$dd %*% t(X)
+  if (fancy) {
+    nm <- names(mu)
+    if (is.null(nm) && !is.null(dn <- dimnames(Sigma))) 
+      nm <- dn[[1L]]
+    dimnames(X) <- list(nm, NULL)
+    if (n == 1) 
+      drop(X)
+    else t(X)
+  } else t(X)
+}
+
+
+fastMN <- function(n,mu,sigma){
+  e <-  m0(mu,sigma)
+  x2 <- m1(n,mu,eL=e,fancy=TRUE)
+}
+
+mu <- rep(2,20)
+Sigma <- matrix(0.1,nrow=20,ncol=20)
+diag(Sigma) <- 4
+
+set.seed(1001)
+x1 <- mvrnorm(1000,mu=mu,Sigma=Sigma)
+set.seed(1001)
+e <- m0(mu,Sigma); 
+x2 <- m1(1000,mu=mu,eL=e,fancy=TRUE)
+identical(x1,x2)
+
+system.time(replicate(1000,mvrnorm(1000,mu=mu,Sigma=Sigma)))
+system.time({e <- m0(mu,Sigma); replicate(1000,m1(1000,mu=mu,eL=e))})
+system.time({e <- m0(mu,Sigma); replicate(1000,m1(1000,mu=mu,eL=e,fancy=FALSE))})
+
+
+
+
+paralist <- list(
+  Nitro  = seq(0,140,length=5),
+  nRep   = 3,
+  nRow   = 40,
+  b_0    = 65,
+  b_1    = 0.05,
+  b_2    = -0.0003,
+  sig_u0 = 5,
[…]

### 2024-08-23 RCode/OFEExptNewParaSimu2024Parallel_explore.R

@@ -1,0 +1,1805 @@
+rm(list = ls())
+library(asreml)
+library(ggplot2)
+library(tidyverse)
+
+thm1 <- theme_bw() + 
+  theme(axis.title = element_text(size=20),
+        axis.text = element_text(size=20),
+        legend.title = element_text(size=20),
+        legend.text = element_text(size=20),
+        legend.key.width = unit(1,"cm"),
+        legend.position = "top",
+        strip.text.x = element_text(size = 20),
+        strip.text.y = element_text(size=20))
+
+
+######### NS , eta = 1 ###############
+
+MSE_ns_LR5_PC  <-readRDS("Outcome/ExptNewPara/Simu1K2024/MSE_ns_LR5_PC2024.rds")
+MSE_ns_LR9_PC  <-readRDS("Outcome/ExptNewPara/Simu1K2024/MSE_ns_LR9_PC2024.rds")
+MSE_ns_LRbw_PC <-readRDS("Outcome/ExptNewPara/Simu1K2024/MSE_ns_LRbw_PC2024.rds")
+
+MSE_ns_LS5_PC  <-readRDS("Outcome/ExptNewPara/Simu1K2024/MSE_ns_LS5_PC2024.rds")
+MSE_ns_LS9_PC  <-readRDS("Outcome/ExptNewPara/Simu1K2024/MSE_ns_LS9_PC2024.rds")
+MSE_ns_LSbw_PC <-readRDS("Outcome/ExptNewPara/Simu1K2024/MSE_ns_LSbw_PC2024.rds")
+
+
+MSE_ns_LR5_sq  <- apply(MSE_ns_LR5_PC, c(1,2), function(a) mean(a^2))
+MSE_ns_LR9_sq  <- apply(MSE_ns_LR9_PC, c(1,2), function(a) mean(a^2))
+MSE_ns_LRbw_sq <- apply(MSE_ns_LRbw_PC, c(1,2), function(a) mean(a^2))
+
+MSE_ns_LS5_sq <- apply(MSE_ns_LS5_PC, c(1,2), function(a) mean(a^2))
+MSE_ns_LS9_sq <- apply(MSE_ns_LS9_PC, c(1,2), function(a) mean(a^2))
+MSE_ns_LSbw_sq <- apply(MSE_ns_LSbw_PC, c(1,2), function(a) mean(a^2))
+
+M <- 1000
+
+LinBeta0_ns <- data.frame(
[…]
